### 2019-08-27 PaperMagneticProfiles_JBSMSE.tex
Include basic draft and template.
The draft text was taken from the COBEM 2017 Paper.
The template was downloaded from the Journal of the Brazilian Society
of Mechanical Sciences and Engineering's website.

% LaTeX .tex example for the proceedings of
% COBEM 2017 - 24th International Congress of Mechanical Engineering
% December, 3-8, 2017, Curitiba, PR, Brazil
%
% Based on the template of the proceedings of COBEM2015 
% MODELO COBEM 2017

\documentclass[draft]{svjour3}

\usepackage{engsymbols}
\usepackage{magref}
\usepackage[utf8]{inputenc}
\usepackage{nicefrac}

\newcommand{\bmax}{\ensuremath{{B}\ped{max}}}
\newcommand{\bmin}{\ensuremath{{B}\ped{min}}}

\usepackage{mathptmx}
\journalname{Journal of the Brazilian Society of Mechanical Sciences and Engineering}

\usepackage{graphicx}
\usepackage{subfig}

\begin{document}

\title{Performance of Magnetic Refrigerators Operating with Different Magnetic Profiles}

\author{
Fábio P. Fortkamp \and
Gusttav B. Lang \and
Jaime A. Lozano \and
Jader R. Barbosa Jr.
}

\institute{
Fábio P. Fortkamp 
\at
POLO --- Research Laboratories for Emerging Technologies in Cooling and Thermophysics, Department of Mechanical Engineering, Federal University of Santa Catarina, Florianópolis, SC, 88040-900, Brazil, \email{fabio@polo.ufsc.br}
\and
Gusttav B. Lang \and
Jaime A. Lozano \and
Jader R. Barbosa Jr. \at POLO --- Research Laboratories for Emerging Technologies in Cooling and Thermophysics, Department of Mechanical Engineering, Federal University of Santa Catarina, Florianópolis, SC, 88040-900, Brazil}

\date{}

\maketitle

\begin{abstract}
 Magnetic refrigeration is a technology based on the concept of the active magnetic regenerator (AMR), which is a solid porous matrix of magnetocaloric material that undergoes temperature variations according to changes in the magnetization synchronized with oscillatory fluid flows. The magnetic field can be applied to the AMR in different profiles (waveforms). In this work, the performance of a magnetic refrigerator is evaluated in terms of two of the most common magnetic profiles: an instantaneous profile and a rectified cosine profile. The results show that the performance of an AMR operating with the instantaneous profile is consistently better than an AMR using the cosine profile with the same average high magnetic field and same minimum value, and that this improvement is higher for larger utilizations (ratio of solid to fluid thermal capacities). For an AMR frequency of \SI{1}{\hertz} and an utilization of 1.0, the cooling capacity of an AMR device operating with the instantaneous profile was \SI{196.3}{\percent} higher than the equivalent rectified cosine profile. The instantaneous profile was then analyzed in more detail, and it was concluded that using high values of magnetic field allows for smaller regenerators and lower mass flow rates to keep a desired level of cooling power.

\keywords{ magnetic refrigeration \and active magnetic regenerator \and numerical modeling \and magnetocaloric effect}
\end{abstract}

\section{INTRODUCTION}
\label{sec:introduction}

An active magnetic regenerator (AMR)  is a thermal regenerator composed of a solid porous matrix of magnetocaloric material, which changes its temperature according to the application of a varying magnetic field in synchronization with oscillatory fluid flows, due to the so-called magnetocaloric effect (MCE). Active magnetic regenerators are employed in magnetic refrigeration, a promising alternative to vapor compression systems due to its use of non-gaseous refrigerants and potentially higher  thermodynamic efficiency \cite{bib:trevizoli}. A magnetic refrigerator may contain multiple regenerator beds, in combination with rotary permanent magnets, to achieve higher levels of performance \cite{bib:trevizoli16_pump}.

The time variation of the magnetic field experienced by an AMR is known as the magnetic profile. The magnetic profile is directly related to the thermodynamic cycle that drives the magnetic refrigerator, and therefore has an important influence on its performance. AMRs can operate according to different thermodynamic cycles, but the most common is the Brayton AMR cycle, which has two isentropic processes of instantaneous magnetization and demagnetization of the magnetocaloric material and two isofield processes \cite{bib:kitanovski}, as shown in Fig.~\ref{fig:brayton}. In practice, it is difficult to generate  stepwise variations of the magnetic field (as required by  the Brayton cycle) using permanent magnets arrays (the apparently only viable solution for domestic magnetic refrigerators due to low cooling requirements and energy consumption). Most magnetic refrigerators developed so far operate with a more continuous magnetic profile, such as the rectified cosine profile \cite{bib:tura-rowe-amr,bib:arnold14_desig,bib:trevizoli15_desig_halbac}, which is easily generated with compact devices and capable of achieving high levels of magnetic field \cite{bib:trevizoli16_pump}, but at the cost of  too brief demagnetization periods.

\begin{figure}[!ht]
  \centering
%  \includegraphics[width=5cm]{brayton-kitanovski}
  \caption{Temperature-entropy diagram for the Brayton AMR cycle, as experienced by the magnetocaloric (MC)  material \cite{bib:kitanovski}. The applied magnetic field is denoted by $H$.}
  \label{fig:brayton}
\end{figure}

In Fig.~\ref{fig:cycles}, the instantaneous and rectified cosine waveforms evaluated in this work are shown in terms of the average applied magnetic field ($\average{B}$) that acts on the regenerator (vertical axis) for one AMR cycle parameterized in a time variable ($t$) ranging from 0 to the cycle period $\tau$ (horizontal axis).

\begin{figure}[!ht]
  \centering
  \includegraphics[width=7cm]{profiles.jpg}
  \caption{Instantaneous and rectified cosine magnetic profiles in terms of the average magnetic field over the regenerator for one AMR cycle as a function of time ($t$). }
  \label{fig:cycles}
\end{figure}

Besides the applied magnetic field variations shown in Fig.~\ref{fig:cycles}, an AMR cycle is also composed of two hydraulic processes: (i) cold blow, occurring after the magnetization, where cold fluid flows through the porous matrix to absorb energy from it and rejects heat to an external hot source, and (ii) hot blow, occurring after the demagnetization, where the magnetocaloric material is cooled down and removes heat from the fluid flowing, which then can absorb the thermal load from the cold source.

Many works on the analysis of  magnetic profiles used a ramp profile as  an approximation of the instantaneous profile with finite transition times between the magnetization levels, making it easier to generate the profiles with permanent magnets. The performance of an AMR subjected to a ramp profile with different parameters was performed by \cite{bib:bjoerk11_amr}, but the emphasis was on the synchronization with the fluid flow profile and the authors did not compare different magnetic profiles. The previously cited investigation by \cite{bib:kitanovski} implemented different cycles through a ramp profile and a modification of the rectified cosine (consisting only of linear variations), and concluded that, with the same operating parameters parameters (temperature span between heat source and heat sink, frequency, mass flow rate, regenerator geometry, maximum applied magnetic field), the Brayton cycle (realized by a ramp profile) results in the highest cooling capacities; the same profile could be used in Ericsson cycles, with the magnetization processes done isothermally instead of adiabatically, and the result is higher values of the coefficient of performance. A comparison of different magnetic profiles for an AMR device was also performed by \cite{bib:asme-mce}, and  the authors concluded that, for same levels of maximum and minimum magnetic field, the instantaneous profile results in higher cooling capacities for a given temperature span.

The present work extends these analyses and attempts to systematically compare the performance of a magnetic refrigerator operating with instantaneous and  rectified cosine profiles under different parameters, with the goal of selecting the best magnetic profile for certain requirements of cooling capacity of a target application. In comparison with the previously cited works, we analyze the effect of different regenerator geometries and different levels of the magnetic field and mass flow rate. In particular, in comparison with the work of \cite{bib:kitanovski}, where the authors studied different combinations of flow and magnetic profiles to yield various thermodynamic cycles, we fix the fluid flow profile to better investigate the effect of the magnetic profile, which is used in the design of magnetic circuits.

\section{NUMERICAL SIMULATIONS}
\label{sec:numer-simul}

Simulations were performed using a one-dimensional AMR mathematical model \cite{bib:asme-mce,bib:trevizoli16_perfor_model}. The simulated magnetic refrigerators are composed of multiple prismatic regenerators filled with gadolinium (Gd) spheres as the magnetocaloric solid matrix, with the parameters shown in Table~\ref{tab:params}. The fluid is a mixture of water and ethylene glycol, in the proportion of \SI{80}{\percent}-\SI{20}{\percent} in volume.

\begin{table}[!ht]
  \centering
  \caption{Geometric and operation parameters for the simulated AMR devices}
  \begin{tabular}{c|c}
\hline
    \textbf{Parameter}&\textbf{Value}\\
\hline
Regenerator height & \SI{20}{\mm}\\
Regenerator width & \SI{25}{\mm}\\
Regenerator length & \SI{100}{\mm}\\
Number of regenerators & \num{11} \\
Particle diameter & \SI{0.5}{\mm}\\
Hot source temperature & \SI{298}{\kelvin}\\
Cold source temperature & \SI{278}{\kelvin}\\
\hline
  \end{tabular}
  \label{tab:params}
\end{table}

The AMR model solves mass and energy conservation equations for the solid and the fluid domains in an active magnetic regenerator. In this work, regenerators were assumed to be adiabatic to the environment. All beds experience the same flow and magnetic profiles, as detailed in the following sections.

\subsection{Flow profile}
\label{sec:flow-profile}

The flow profile through a given bed, i.e. the mass flow rate as a function of time $\rate{m}\ped{f} (t)$, is assumed to be a square wave as that shown in Fig.~\ref{fig:mprofile}. The cold blow has a duration of $\tau\ped{CB}$ and the  hot blow a duration of $\tau\ped{HB}$, while the period of one AMR cycle is $\tau$. Limiting the blow times during each half-cycle to periods where the magnetic field is at its maximum and minimum can result in increased performance \cite{bib:nakashima17_avaliac}. In this work, the blows are supposed to be in balance, thus, $\tau\ped{CB} = \tau\ped{HB}$. An important parameter regarding the flow profiles can be defined, which is the blow fraction, $F\ped{B}$:

\begin{equation}
  \label{eq:1}
  F\ped{B} = \frac{\tau\ped{CB} + \tau\ped{HB}}{\tau}
\end{equation}

\begin{figure}[!ht]
  \centering
%  \includegraphics[width=7cm]{mprofile}
  \caption{Instantaneous flow profile used in the numerical simulations. "Positive" mass flow rate indicates flow in the direction from the cold to the hot source, and negative values represent the opposite direction. }
  \label{fig:mprofile}
\end{figure}

\subsection{Magnetic profile}
\label{sec:magnetic-profile}

The AMR mathematical model takes the magnetic profile as an input, and the profiles represented in Fig.~\ref{fig:cycles} were tested with different parameters. The mathematical definitions for the magnetic profiles over a cycle of period $\tau$ are as follows; the instantaneous profile (represented by the index ``I'') and the rectified cosine profile (represented by ``RC'') are defined solely in terms of the extrema values $\bmax$ and $\bmin$:

\begin{equation}
\average{B}\ped{I}(t)=
\begin{cases}
\average{B}\ped{max}, & 0 \le t < \nicefrac{\tau}{2} \\
\average{B}\ped{min}, & \nicefrac{\tau}{2} \le t < \tau\\
\end{cases}
\label{eq:4}
\end{equation}

\begin{equation}
\average{B}\ped{RC}(t) = \bmin + \left(\bmax - \bmin\right)  \left\lvert \cos\left( \frac{\pi}{\tau} \left( t - \frac{\tau}{4}\right)\right) \right\rvert
\label{eq:5}
\end{equation}

In this work, the average values of the magnetic field during each half-AMR cycle are considered for comparison between profiles. The average magnetic profile during the hot cycle ($0 \le t < \nicefrac{\tau}{2}$) is denoted $B\ped{h}$ and the average during the cold cycle  ($ \nicefrac{\tau}{2} \le t < \tau$) is denoted $B\ped{l}$.

\subsection{AMR operating parameters}
\label{sec:amr-oper-param}

Different numerical simulations were carried with different operating parameters such as: AMR cycle frequency ($f$), blow fraction ($F\ped{B}$) and utilization ($\Phi$) which is defined as:

\begin{equation}
\Phi = \frac{\rate{m}\ped{f,max}F\ped{B}\frac{\tau}{2}c_{p,\mathrm{f}}}{m\ped{s} c\ped{s}}
\label{eq:2}
\end{equation}

\noindent where $c_{p,\mathrm{f}}$ is the constant-pressure specific heat for the fluid, and $m\ped{s}$ and $c\ped{s}$ are the mass and specific heat of the solid phase in one bed.

\section{RESULTS AND DISCUSSIONS}
\label{sec:results-discussions}

\subsection{Comparison of the instantaneous and rectified cosine profiles}
\label{sec:comp-inst-cosine}

When comparing the magnetic profiles, the average magnetic field during the hot cycle is the same; this implies in a higher peak for the rectified cosine. For the cold cycle, there are two possible comparison methods:

\begin{enumerate}
\item The minimum values for both profiles is the same;
\item The average value for both profiles during the cold cycle is the same.
\end{enumerate}

As a reference, in all simulations  the minimum value for the rectified cosine was fixed at $\average{B}\ped{min,RC} = \SI{0.1}{\tesla}$. For the first comparison, the minimum value for the instantaneous value was kept at the same level ($\average{B}\ped{min,I} =  \average{B}\ped{min,RC}$), hence, the average low value for the RC profile was higher ($B\ped{l,RC} > B\ped{l,I}$). Although this does not seem a fair comparison, in practice it is feasible to generate a profile with a constant low-valued plateau for the magnetic field \cite{bib:insinga16_optim,bib:benedict16_desig}. For the other comparison method, the low level of the instantaneous profile was increased ($\average{B}\ped{min,I} >  \average{B}\ped{min,RC}$) to keep the average the same ($B\ped{l,RC} = B\ped{l,I}$). In addition, simulations were ran for various values of blow fraction and the optimal cases were selected; the rectified cosine profile can benefit from a smaller blow fraction because this can concentrate the flow during the periods of very high or low fields. In this section, all results show the resulting optimal case of the blow fraction for each profile (for the values tested): fluid flowing during the entire period for the instantaneous profile, and only during \SI{60}{\percent} of the period for the cosine profile.

Figure~\ref{fig:cos_ins} shows the cooling capacity attained by the device at a frequency of \SI{1}{\hertz} and different utilizations, for both comparison methods.  The horizontal axis shows the average value during the high field region. Notice how the results are conflicting; for Fig.~\ref{fig:comp_min}, the instantaneous profile almost always yields a higher performance, while for Fig.~\ref{fig:comp_avg} the rectified cosine profile generates higher cooling capacities. Since the average during the hot cycle (high field stage) is the same, the main difference is due to the low magnetic field levels. For the ``same minimum'' comparison, the instantaneous profile is capable of keeping the magnetic field at low levels for the whole half-cycle, which is beneficial for performance;  for $\Phi=1.0$ and $B\ped{h} = \SI{1.40}{\tesla}$, the cooling capacity for the instantaneous profile is $\SI{196.3}{\percent}$ higher than for the cosine profile.  As demonstrated by \cite{bib:asme-mce}, a higher average magnetic field during the low-field stage increases the solid temperature and consequently results in  warmer fluid entering the cold heat exchanger, representing a thermal loss. In the ``same-average'' comparison, the cosine profile is capable of achieving much lower levels (since its minimum value is fixed), therefore providing more cooling power. However, as explained before, it is possible to design near-instantaneous profiles with very low levels of the magnetic field.

\begin{figure}[!ht]
  \centering
%  \subfloat[Same minimum]{\includegraphics[width=8cm]{Qc_B_comp_f_1_same_minimum}\label{fig:comp_min}}
\,
%  \subfloat[Same average]{\includegraphics[width=8cm]{Qc_B_comp_f_1_same_low_average}\label{fig:comp_avg}}
\,
  \caption{Cooling capacity as a function of the  average high magnetic field, for different utilizations. “I”: instantaneous (blow fraction of \SI{100}{\percent}); “RC”: rectified cosine  (blow fraction of \SI{60}{\percent}), for both comparison methods.}
 \label{fig:cos_ins}
\end{figure}

The only exception in the ``same minimum'' comparison is seen for the lowest utilization of $\Phi = 0.2$, where the performance is slightly better for the RC profile. Since the blow fraction for the cosine is lower, the mass flow rate must be higher to yield the same utilization (cf. Eq.~\eqref{eq:2}), and this increases heat transfer rate, as previously explained ---  outweighing the effects of the magnetic field.

In general, the performance of the AMRs operating with the instantaneous magnetic profile yields better results. As can be seen on Fig.~\ref{fig:cos_ins}, an instantaneous profile with the lowest possible value of $\bmin$ and the highest possible value of $\bmax$, with a flow profile occupying the whole cycle with average values of utilization, results in the highest values of cooling capacity among all simulations, therefore, representing the ideal magnetic profile for an AMR.

\subsection{Analysis of the instantaneous profile}
\label{sec:deta-analys-inst}

As shown in the previous section, the instantaneous profile yields the highest values for cooling capacity. Therefore, in this section, a more detailed analysis of such profile has been carried out. Figure~\ref{fig:qc_phi_inst} shows the cooling capacity as function of utilization, for several levels of the maximum magnetic field for the instantaneous profile, for two different operating frequencies. Because of the conflicts between a low heat transfer rate for flow rates too low and a loss in regenerator effectiveness in flow rates too high, there are critical values of utilization that maximize cooling capacity, and this critical value grows with the level of magnetic field. With higher magnetic field, the increase in the MCE surpasses the loss of effectiveness, and one can go to higher flow rates without losing performance. It can also be seen in Fig.~\ref{fig:qc_phi_inst} that at higher frequencies, the values of cooling power are higher, and also the critical values of utilization are lower; however, this usually is achieved at the cost of higher power consumption in AMR devices at higher frequencies \cite{bib:lei15_study,NIKNIA2016601}.

\begin{figure}[!ht]
  \centering
\subfloat[$f = \SI{1}{\hertz}$]{\includegraphics[width=8cm]{Qc_Phi_inst_f_1_Hmin_005_FB_100}\label{fig:Qc_phi_inst_1}}
\,
  \subfloat[$f = \SI{2}{\hertz}$]{\includegraphics[width=8cm]{Qc_Phi_inst_f_2_Hmin_005_FB_100}\label{fig:Qc_phi_inst_2}}
  \caption{Cooling capacity as a function of utilization, for various values of the high magnetic field  of the instantaneous profile}
  \label{fig:qc_phi_inst}
\end{figure}

\begin{figure}[!ht]
  \centering
  \includegraphics[width=8cm]{Qc_H_inst_f_1_Phi_40}
  \caption{Cooling capacity as a function of  regenerator height (all other parameters from Table~\ref{tab:params} constant) for various values of the high magnetic field of the instantaneous profile}
\label{fig:Qc_H_inst}
\end{figure}

The parameters in Table~\ref{tab:params} were chosen from preliminary simulations, but they are not guaranteed to be the optimal choices. To understand the impact of regenerator geometry on the performance with the instantaneous profile, the regenerator height was varied in Fig.~\ref{fig:Qc_H_inst}, and all other parameters from Table.~\ref{tab:params} were kept fixed. As expected, higher magnetic fields allow for smaller regenerators (and hence more compact systems). For instance, to achieve a capacity of \SI{100}{\watt}, increasing the field from \num{1.0} to \SI{1.2}{\tesla} result in using regenerators \SI{36}{\percent} smaller.

\section{CONCLUSIONS}
\label{sec:conclusions}

A one-dimensional AMR numerical model was used to compare the performance of a magnetic refrigerator under different operating and geometric parameters and with the instantaneous and rectified cosine magnetic profiles. Most of the AMRs operating with an instantaneous magnetic profile have resulted in better performances than those with a cosine profile, except in cases of low utilization. Although the cosine profile reaches higher levels of the magnetic field, the instantaneous profile can keep the magnetization (and demagnetization) for a longer period, which is shown to be beneficial to performance. Further analysis of the instantaneous profile has shown that the use of the highest possible value of the maximum magnetic field allows for using smaller regenerators and lower utilization, without losing performance.

\begin{acknowledgements}
This work was supported by CNPq, Embraco and EMBRAPII Unit Polo/UFSC.  
\end{acknowledgements}

% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
\bibliographystyle{spphys}       % APS-like style for physics

\bibliography{thermo-ref/Thermo-Foam-Ref}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2019-08-27 loaddatasets.py
Change datasets to CSV format per journal requirements.

@@ -4,11 +4,11 @@
 import pandas as pd
 from pandas import DataFrame, Series
 
-INSTANTANEOUS_DATASET = "Instantaneous.txt"
-INSTANTANEOUS_DATASET_VARYING_HEIGHT = "Instantaneous-varH.txt"
-RAMP_DATASET = "Ramp.txt"
-RAMP_DATASET_VARYING_HEIGHT = "Ramp-varH.txt"
-RECTIFIED_COSINE_DATASET = "RectifiedCosine.txt"
+INSTANTANEOUS_DATASET = "Instantaneous.csv"
+INSTANTANEOUS_DATASET_VARYING_HEIGHT = "Instantaneous-varH.csv"
+RAMP_DATASET = "Ramp.csv"
+RAMP_DATASET_VARYING_HEIGHT = "Ramp-varH.csv"
+RECTIFIED_COSINE_DATASET = "RectifiedCosine.csv"
 
 
 # These dataset are formated as tab-separed values (TSV), with column names in the format:
@@ -19,11 +19,11 @@ RECTIFIED_COSINE_DATASET = "RectifiedCosine.txt"
 # 
 # We adopt the convention of naming these data sets as '<profile_identifier>df', where the profile identifier can be 'it' (instantaneous), 'rc' (rectified cosine) or 'rm' (ramp)
 
-itdf = pd.read_csv(INSTANTANEOUS_DATASET,sep="\s+")
-it_varH_df = pd.read_csv(INSTANTANEOUS_DATASET_VARYING_HEIGHT,sep="\s+")
-rcdf = pd.read_csv(RECTIFIED_COSINE_DATASET,sep="\s+")
-rmdf = pd.read_csv(RAMP_DATASET,sep="\s+")
-rm_varH_df = pd.read_csv(RAMP_DATASET_VARYING_HEIGHT,sep="\s+")
+itdf = pd.read_csv(INSTANTANEOUS_DATASET)
+it_varH_df = pd.read_csv(INSTANTANEOUS_DATASET_VARYING_HEIGHT)
+rcdf = pd.read_csv(RECTIFIED_COSINE_DATASET)
+rmdf = pd.read_csv(RAMP_DATASET)
+rm_varH_df = pd.read_csv(RAMP_DATASET_VARYING_HEIGHT)
 
 
 # The columns of interest can be nicely identified as:

### 2019-08-27 figures.py
Chane figures format to EPS per journal requirement.

@@ -5,7 +5,6 @@ import math
 import re
 import os.path
 from pathlib import Path
-import math
 
 import numpy as np
 import numpy.ma as ma
@@ -15,10 +14,11 @@ from scipy.interpolate import griddata
 from scipy.constants import mu_0
 from scipy.integrate import simps
 import matplotlib.pyplot as plt
+
 import loaddatasets as ld
 
 FIG_FILE_PATH = Path('.')
-PLOT_EXTENSION = ".pdf"
+PLOT_EXTENSION = ".eps"
 
 FIGSIZE_IN = (8,6)
 DPI = 800
@@ -52,7 +52,7 @@ plt.rc(
     'font', 
     size=MEDIUM_SIZE,
     family='serif',
-    serif='Palatino')          # controls default text sizes
+    serif='Helvetica')          # controls default text sizes
 plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
 plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
 plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels

### 2019-08-27 plotprofiles.py

@@ -1,7 +1,6 @@
 import numpy as np
 
 import matplotlib
-matplotlib.use("pdf")
 from matplotlib import patches
 import matplotlib.pyplot as plt
 
@@ -21,7 +20,7 @@ plt.rc(
     'font', 
     size=MEDIUM_SIZE,
     family='serif',
-    serif='Palatino')          # controls default text sizes
+    serif='Helvetica')          # controls default text sizes
 plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
 plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
 plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
@@ -159,7 +158,7 @@ def plot_all_profiles():
     profile_axes.text(0.99*tau/4,1.035*B_max,r'$\tau_\mathrm{M}$',
                       horizontalalignment='right')
 
-    profile_fig.savefig("profiles_all.pdf",dpi=800,bbox_inches="tight")
+    profile_fig.savefig("profiles_all.eps",dpi=800,bbox_inches="tight")
 
 def plot_it_and_rc_profiles():
     B_max= 1.0
@@ -201,7 +200,7 @@ def plot_it_and_rc_profiles():
 
     profile_axes.set_ylim(0,1.1*B_max)
 
-    profile_fig.savefig("profiles_it_and_rc",dpi=DPI,bbox_inches='tight')
+    profile_fig.savefig("profiles_it_and_rc.eps",dpi=DPI,bbox_inches='tight')
 
 def plot_it_and_rc_profiles_same_minimum():
 
@@ -244,7 +243,7 @@ def plot_it_and_rc_profiles_same_minimum():
     B_max = max(B_max_cos,B_max_ins)
     profile_axes.set_ylim(0,1.2*B_max)
 
-    profile_fig.savefig("profiles_it_and_rc_same_minimum.pdf",dpi=DPI,bbox_inches="tight")
+    profile_fig.savefig("profiles_it_and_rc_same_minimum.eps",dpi=DPI,bbox_inches="tight")
 
 def plot_it_and_rc_profiles_same_average():
     B_max_ins= 1.0
@@ -289,7 +288,7 @@ def plot_it_and_rc_profiles_same_average():
     B_max = max(B_max_cos,B_max_ins)
[…]

### 2019-08-28 figures.py
Improve figures.
- Fonts were adjusted
- Some plots were simplified in the number of lines
- Colors were adjusted
- The generator script was organized

@@ -20,15 +20,13 @@ import loaddatasets as ld
 FIG_FILE_PATH = Path('.')
 PLOT_EXTENSION = ".eps"
 
-FIGSIZE_IN = (8,6)
-DPI = 800
+FIGSIZE_IN = (7,5)
+DPI = 600
 
 # stolen from https://stackoverflow.com/questions/3899980/how-to-change-the-font-size-on-a-matplotlib-plot
-
-SMALL_SIZE = 16
+SMALL_SIZE = 14
 MEDIUM_SIZE = 20
-BIGGER_SIZE = 24
-
+BIGGER_SIZE = 22
 
 N_POINTS_LINEPLOT = 2000
 
@@ -52,7 +50,7 @@ plt.rc(
     'font', 
     size=MEDIUM_SIZE,
     family='serif',
-    serif='Helvetica')          # controls default text sizes
+    serif='Arial')          # controls default text sizes
 plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
 plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
 plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
@@ -85,7 +83,6 @@ def refine_list(original_list, factor):
         
     return np.linspace(min_value,max_value,math.ceil(n_refined))
 
-
 def refine_yticks(ax,factor):
     """
     Take an Axis object 'ax' and refine the y-ticks on it by 'factor'
@@ -115,7 +112,6 @@ def refine_xticks(ax,factor):
     """
 
     ax.set_xticks(refine_list(ax.get_xticks(),factor),minor=True)
-    
 
 def create_plot(xlabel="",
                      ylabel="",
@@ -166,10 +162,6 @@ def save_figure(fig,name):
                 dpi=DPI,
                 bbox_inches='tight')
 
-# In[3]:
-
-
-
 def filter_table_from_column(table,column,value):
     """
     Return a view into the 'table' DataFrame, selecting only the rows where
@@ -177,25 +169,6 @@ def filter_table_from_column(table,column,value):
     """
     
     return table[table[column] == value]
-
-# Fixed parameters
-
-FIXED_PARAMETERS = {
-    "D_p[m]": 0.5e-3,
-    "L[m]": 100e-3,
-    "W[m]": 25e-3,
-    "H[m]": 20e-3,
[…]

### 2019-08-29 figures.py
Set limit of pumping power limit for the cosine profile.

@@ -362,8 +362,8 @@ def plot_Wpump_Inst_vs_CCH(table_inst,table_cch,F_inst,F_CCH, figure_suffix=""):
             
 
                     
-            if (max(Wpump_vector_inst) > y_max):
-                y_max = max(Wpump_vector_inst)
+            if (max(Wpump_vector_cch) > y_max):
+                y_max = max(Wpump_vector_cch)
                     
         
         axis.set_ylim(0,y_max)     

### 2019-09-02 PaperMagneticProfiles_JBSMSE.tex
Develop draft of introduction.

@@
 \begin{abstract}
- Magnetic refrigeration is a technology based on the concept of the active magnetic regenerator (AMR), which is a solid porous matrix of magnetocaloric material that undergoes temperature variations according to changes in the magnetization synchronized with oscillatory fluid flows.
-The magnetic field can be applied to the AMR in different profiles (waveforms).
-In this work, the performance of a magnetic refrigerator is evaluated in terms of two of the most common magnetic profiles: an instantaneous profile and a rectified cosine profile.
-The results show that the performance of an AMR operating with the instantaneous profile is consistently better than an AMR using the cosine profile with the same average high magnetic field and same minimum value, and that this improvement is higher for larger utilizations (ratio of solid to fluid thermal capacities).
-For an AMR frequency of \SI{1}{\hertz} and an utilization of 1.0, the cooling capacity of an AMR device operating with the instantaneous profile was \SI{196.3}{\percent} higher than the equivalent rectified cosine profile.
-The instantaneous profile was then analyzed in more detail, and it was concluded that using high values of magnetic field allows for smaller regenerators and lower mass flow rates to keep a desired level of cooling power.
 
@@
 
-\section{INTRODUCTION}
+\section{Introduction}
 \label{sec:introduction}
@@
 A magnetic refrigerator may contain multiple regenerator beds, in combination with rotary permanent magnets, to achieve higher levels of performance \cite{bib:trevizoli16_pump}.
+Since the working fluid only has energy transport functions and does not change its phase, aqueous solutions with freezing and corrosion inhibitors are usually employed.
 
-The time variation of the magnetic field experienced by an AMR is known as the magnetic profile.
-The magnetic profile is directly related to the thermodynamic cycle that drives the magnetic refrigerator, and therefore has an important influence on its performance.
-AMRs can operate according to different thermodynamic cycles, but the most common is the Brayton AMR cycle, which has two isentropic processes of instantaneous magnetization and demagnetization of the magnetocaloric material and two isofield processes \cite{bib:kitanovski}, as shown in Fig.~\ref{fig:brayton}.
-In practice, it is difficult to generate  stepwise variations of the magnetic field (as required by  the Brayton cycle) using permanent magnets arrays (the apparently only viable solution for domestic magnetic refrigerators due to low cooling requirements and energy consumption).
-Most magnetic refrigerators developed so far operate with a more continuous magnetic profile, such as the rectified cosine profile \cite{bib:tura-rowe-amr,bib:arnold14_desig,bib:trevizoli15_desig_halbac}, which is easily generated with compact devices and capable of achieving high levels of magnetic field \cite{bib:trevizoli16_pump}, but at the cost of  too brief demagnetization periods.
+The dynamic nature of AMR systems are described by two characteristic waveforms:
+
+\begin{enumerate}
+\item The \emph{magnetic profile}, which describes the time variation of the magnetic field experienced by the regenerators;
+\item The \emph{fluid flow profile}, which describes the oscillatory flow rate though the regenerators
+\end{enumerate}
+
+Different combinations and arrangements of these waveforms yield different thermodynamic cycles through which an AMR system can operate.
+The most common cycle in the literature is the Brayton AMR cycle, which has two isentropic processes of instantaneous magnetization and demagnetization of the magnetocaloric material and two isofield processes \cite{bib:kitanovski}, as shown in Fig.~\ref{fig:brayton}.
+During magnetization, the solid material warms up due to the MCE; with a constant applied magnetic field, fluid flows, absorbing this energy and releasing it in the hot heat exchanger; the magnetic field is changed to a low level, cooling down the material; fluid from the hot source flows through the bed, releases its energy to the material, and the cold fluid can then absorb heat from the cold source.
 
@@
   \centering
-%  \includegraphics[width=5cm]{brayton-kitanovski}
+ %\includegraphics[width=5cm]{brayton-kitanovski}
   \caption{Temperature-entropy diagram for the Brayton AMR cycle, as experienced by the magnetocaloric (MC)  material \cite{bib:kitanovski}. The applied magnetic field is denoted by $H$.}
@@
 
-In Fig.~\ref{fig:cycles}, the instantaneous and rectified cosine waveforms evaluated in this work are shown in terms of the average applied magnetic field ($\average{B}$) that acts on the regenerator (vertical axis) for one AMR cycle parameterized in a time variable ($t$) ranging from 0 to the cycle period $\tau$ (horizontal axis).
+The performance of AMR-based magnetic refrigerators is directly related to their thermodynamic cycle, and hence to the magnetic and fluid flow profiles.
+With this motivation, there are multiple studies in the literature regarding these waveforms.
+In general, the fluid flow profile is more easily changed in experimental prototypes with modifications in the hydraulic system, and it can be optimized for a given magnetic profile for higher cooling capacity or coefficient of performance \cite{bib:teyber17_exper,bib:nakashima18-influen-exp,FORTKAMP2018}.
+The actual shape of waveform depends on the hydraulic system configuration; single- or two-regenerators systems usually employ piston pumps with sinusoidal fluid flow profiles, while more complex valving system yield trapezoidal fluid flow profiles, with periods of no flow (when fluid is by-passed from the regenerator), periods with a constant flow rate and ramp transitions between these two states.
+
+In room temperature magnetic refrigeration, the magnetic profile is generated by permanent magnets, representing the most expensive part of a magnetic refrigerator \cite{bib:bjoerk16_lifetime}, and hence considered fixed in AMR devices.
+Although the magnetic profile can be changed with motion control on the permanent magnets \cite{bib:benedict16_desig}, this is a topic yet to be better investigated, and most studies on the subject are numerical.
+The ideal Brayton cycle requires a instantaneous magnetic profile (square waveform), but in practice it is difficult to generate  stepwise variations of the magnetic field  using rotating permanent magnets arrays.
+Most magnetic refrigerators developed so far operate with a more continuous magnetic profile, such as the rectified cosine profile \cite{bib:tura-rowe-amr,bib:arnold14_desig,bib:trevizoli15_desig_halbac}, which is easily generated with compact devices and capable of achieving high levels of magnetic field \cite{bib:trevizoli16_pump}, but at the cost of  too brief demagnetization periods.
+
+Many works on the analysis of  magnetic profiles use a ramp profile as  an approximation of the instantaneous profile with finite transition times between the magnetization levels, making it easier to generate the profiles with permanent magnets.
+The performance of an AMR subjected to a ramp magnetic profile and a instantaneous fluid flow profile with different parameters has been investigate \cite{bib:bjoerk11_amr}, but the emphasis was on the synchronization with the fluid flow profile and the authors did not compare different magnetic profiles.
+A study that  implemented different cycles through a ramp profile and a modification of the rectified cosine (consisting only of linear variations) \cite{bib:kitanovski} concluded that, with the same operating parameters parameters (temperature span between heat source and heat sink, frequency, mass flow rate, regenerator geometry, maximum applied magnetic field), the Brayton cycle (realized by a ramp profile) results in the highest cooling capacities; the same profile could be used in Ericsson cycles, with the magnetization processes done isothermally instead of adiabatically, and the result is higher values of the coefficient of performance.
+The conclusion that the instantaneous magnetic profile results in higher cooling capacities for a given temperature span, compared to other waveforms is also presented in \cite{bib:asme-mce}
+
+In Fig.~\ref{fig:cycles}, the instantaneous and rectified cosine waveforms evaluated in this work are shown in terms of the average applied magnetic field (${B}$) that acts on the regenerator (vertical axis) for one AMR cycle parameterized in a time variable ($t$) ranging from 0 to the cycle period $\tau$ (horizontal axis).
 
@@
   \centering
-  \includegraphics[width=7cm]{profiles.jpg}
+  \includegraphics[width=7cm]{profiles_all.eps}
   \caption{Instantaneous and rectified cosine magnetic profiles in terms of the average magnetic field over the regenerator for one AMR cycle as a function of time ($t$). }
@@
 
-Besides the applied magnetic field variations shown in Fig.~\ref{fig:cycles}, an AMR cycle is also composed of two hydraulic processes: (i) cold blow, occurring after the magnetization, where cold fluid flows through the porous matrix to absorb energy from it and rejects heat to an external hot source, and (ii) hot blow, occurring after the demagnetization, where the magnetocaloric material is cooled down and removes heat from the fluid flowing, which then can absorb the thermal load from the cold source.
-
-Many works on the analysis of  magnetic profiles used a ramp profile as  an approximation of the instantaneous profile with finite transition times between the magnetization levels, making it easier to generate the profiles with permanent magnets.
-The performance of an AMR subjected to a ramp profile with different parameters was performed by \cite{bib:bjoerk11_amr}, but the emphasis was on the synchronization with the fluid flow profile and the authors did not compare different magnetic profiles.
-The previously cited investigation by \cite{bib:kitanovski} implemented different cycles through a ramp profile and a modification of the rectified cosine (consisting only of linear variations), and concluded that, with the same operating parameters parameters (temperature span between heat source and heat sink, frequency, mass flow rate, regenerator geometry, maximum applied magnetic field), the Brayton cycle (realized by a ramp profile) results in the highest cooling capacities; the same profile could be used in Ericsson cycles, with the magnetization processes done isothermally instead of adiabatically, and the result is higher values of the coefficient of performance.
-A comparison of different magnetic profiles for an AMR device was also performed by \cite{bib:asme-mce}, and  the authors concluded that, for same levels of maximum and minimum magnetic field, the instantaneous profile results in higher cooling capacities for a given temperature span.
-
-The present work extends these analyses and attempts to systematically compare the performance of a magnetic refrigerator operating with instantaneous and  rectified cosine profiles under different parameters, with the goal of selecting the best magnetic profile for certain requirements of cooling capacity of a target application.
+The present work extends these analyses and attempts to systematically compare the performance of a magnetic refrigerator operating with instantaneous, rectified cosine and ramp magnetic  profiles under different parameters, with the goal of selecting the best magnetic profile for certain requirements of cooling capacity of a target application.
 In comparison with the previously cited works, we analyze the effect of different regenerator geometries and different levels of the magnetic field and mass flow rate.
@@
 
-\bibliography{thermo-ref/Thermo-Foam-Ref}
+\bibliography{thermo-ref/Thermo-Foam-Ref,thermo-ref/thesis}
 

### 2019-09-09 PaperMagneticProfiles_JBSMSE.tex
Develop better draft of Introduction.

@@
 \usepackage{subfig}
+\usepackage{xcolor}
+\usepackage{nomencl}
+\usepackage{hyperref}
 
@@
 
-An active magnetic regenerator (AMR)  is a thermal regenerator composed of a solid porous matrix of magnetocaloric material, which changes its temperature according to the application of a varying magnetic field in synchronization with oscillatory fluid flows, due to the so-called magnetocaloric effect (MCE).
-Active magnetic regenerators are employed in magnetic refrigeration, a promising alternative to vapor compression systems due to its use of non-gaseous refrigerants and potentially higher  thermodynamic efficiency \cite{bib:trevizoli}.
-A magnetic refrigerator may contain multiple regenerator beds, in combination with rotary permanent magnets, to achieve higher levels of performance \cite{bib:trevizoli16_pump}.
-Since the working fluid only has energy transport functions and does not change its phase, aqueous solutions with freezing and corrosion inhibitors are usually employed.
+Mechanical vapor compression has been the dominant cooling technology for the past century \cite{bib:nik} but, despite its dominance, it still faces an increasing number of challenges related to the its environmental footprint.
+The large entropy generation associated with vapor compression processes makes this techonology constrained by low exergy efficiencies, in particular for compact systems \cite{KITANOVSKI2015288}.
+In addition, the phase-out of refrigerants \textcolor{black}{with} ozone depleting \textcolor{black}{and global warming potentials has} introduced the use of flammable substances, with their own set of risks for consumer applications \cite{bib:iir-flammable} and technologial challenges \cite{bib:lionte18-adapt}.
 
-The dynamic nature of AMR systems are described by two characteristic waveforms:
+The term \emph{caloric cooling} is \textcolor{black}{generally} applied to alternative cooling techonologies in which the cooling effect is generated by the response of a solid material to a physical \textcolor{black}{stimulus}.
+The absence of hazardous gases, compressors \textcolor{black}{and throttling devices} makes these technologies potentially more efficient, \textcolor{black}{scalable}, silent and environmentally friendly.
+Magnetic refrigeration (MR) is the most advanced of all caloric technologies \cite{KITANOVSKI2015288}; in particular, with the classes of magnetic refrigerants currently available, magnetocaloric refrigeration seems promising for applications in small temperature span (around \SI{20}{\kelvin}), such as winecoolers \textcolor{black}{and air conditioners} \cite{KITANOVSKI2015288}.
+
+\nomenclature[vm]{MR}{Magnetic (or Magnetocaloric) Refrigeration}
+
+In magnetic refrigeration, a \emph{magnetocaloric material} (MCM) \textcolor{black}{is subjected to a cyclical change of the applied} magnetic field, and its temperature \textcolor{black}{changes as a result} of the \emph{magnetocaloric effect} (MCE).
+The magnitude of the MCE  \textcolor{black}{depends} on  parameters \textcolor{black}{related to} characteristics of the material, magnetic field variation and temperature, and its maximal at the transition Curie temperature of the material.
+For a thorough introduction to the magnetocaloric effect and magnetocaloric materials, the reader is referred to \cite{bib:smith-magneto}.
+
+\nomenclature[vm]{MCM}{Magnetocaloric Material}
+
+For operating conditions typical of a low-temperature span magnetic refrigerator, the MCE is typically \textcolor{black}{on} the order of \num{2}-\SI{5}{\kelvin}.
+\textcolor{black}{T}o amplify this \textcolor{black}{temperature change}, heat regeneration is usually employed \cite{bib:kitanovski}.
+Active magnetic regenerators (AMR) are thermal devices where the magnetocaloric material constitutes a solid matrix through which flows an aqueous heat transfer fluid, and is cyclically magnetized and demagnetized to activate the magnetocaloric effect.
+\textcolor{black}{A regenerator is essentially a cascade of infinitesimal ``layers'' of MCM that are activated simultaneously} to build up a temperature profile \textcolor{black}{along its length}.
+These layers can be made of the same material, yielding an homogeneous regenerator; however, given the  dependence  of the MCE with temperature, it is an interesting strategy to build \emph{multilayer} regenerators, where each layer is composed of a different material \textcolor{black}{that} will work around its \textcolor{black}{own} Curie temperature, maximizing the magnetocaloric effect of each portion.
+
+\nomenclature[vm]{AMR}{Active Magnetic Regenerator}
+
+The five main subsystems in an AMR-based magnetic refrigerator can be identified as follows \cite{bib:jaime,bib:trevizoli16_pump}:
 
 \begin{enumerate}
-\item The \emph{magnetic profile}, which describes the time variation of the magnetic field experienced by the regenerators;
-\item The \emph{fluid flow profile}, which describes the oscillatory flow rate though the regenerators
+\item magnetic circuit; \label{item:1}
+\item active magnetic regenerator; \label{item:2}
+\item flow management system; \label{item:3}
+\item control system; \label{item:4}
+\item transmission system; \label{item:5}
+\item heat exchangers and cabinet. \label{item:6a}
 \end{enumerate}
 
-Different combinations and arrangements of these waveforms yield different thermodynamic cycles through which an AMR system can operate.
-The most common cycle in the literature is the Brayton AMR cycle, which has two isentropic processes of instantaneous magnetization and demagnetization of the magnetocaloric material and two isofield processes \cite{bib:kitanovski}, as shown in Fig.~\ref{fig:brayton}.
-During magnetization, the solid material warms up due to the MCE; with a constant applied magnetic field, fluid flows, absorbing this energy and releasing it in the hot heat exchanger; the magnetic field is changed to a low level, cooling down the material; fluid from the hot source flows through the bed, releases its energy to the material, and the cold fluid can then absorb heat from the cold source.
+The magnetic circuit generates oscillating magnetic fields that activate the MCE \textcolor{black}{in} the active magnetic regenerators.
+As previously explained, the regenerators are composed of magnetocaloric porous media, and the flow management system provides the alternating fluid flow through the beds.
+The control system \textcolor{black}{serves} the purpose of synchronizing the fluid flow regime with the magnetic field variations.
+Finally, the heat exchangers are responsible for transferring the cooling effect from the AMR to the refrigerated cabinet and the rejected heat to the surroundings.
+
+Magnetic refrigerators can operate according to different thermodynamic cycles, but the stages are roughly as follows.
+The magnetic circuit magnetizes the MCM, increasing its temperature due to the MCE.
+During the so-called \emph{cold blow}, cold fluid from the cold source flows through the warm bed and absorbs its energy, releasing it to the external heat exchanger.
+On the return of the fluid, the solid is demagnetized and cooled down, and in the \emph{hot blow} the fluid relases energy to the bed, decreasing its temperature so it can absorb the thermal load at the cold source.
+The cycle then repeats; different cycles can be configured by different durations and synchronization steps between these two \emph{characteristic waveforms}:
+
+\begin{enumerate}
+\item The \emph{magnetic profile}, which describes the oscillating magnetic field over one regenerator;
+\item The \emph{fluid flow profile}, which describes the time-variation of flow rate through one bed.
+\end{enumerate}
+
+Among the challenges cited in the literature for further improvement of magnetic refrigerators, two can be highlighted \cite{bib:eriksen16_activ}:
+
+\begin{enumerate}
+\item Better use of AMR and magnetic circuit models during the design process, to identify optimal geometric and operating parameter;
+\item Better study of losses that are present in a magnetic cooling device.
+\end{enumerate}
+
+\textcolor{black}{In} other words, these challenges arise due to \emph{interactions} between different subsystems \textcolor{black}of a magnetic refrigerator.
+In these context, the focus on the aforementioned waveforms is a suitable approach for optimizing the performance of magnetic refrigerators, as these profiles represent interactions between systems.
+As it will be seen, mathematical models for AMRs take these waveforms as input, and they are generated by models for other components.
+
+Fluid flow profiles are more easily investigated with experimental methods, since they can be altered with modifications in the fluid flow system.
+In particular, the \emph{duration} of blows have been extensively investigated \cite{bib:teyber17_exper,bib:nakashima18-influen-exp,FORTKAMP2018}, and the literature shows that the cooling capacity of magnetic refrigerators can be increased by focusing fluid flows during periods where the magnetic field is at its extrema values.
+
+In this work, we focus on magnetic profiles, which are less studied in the literature.
+The studied waveforms are depicted in \autoref{fig:profiles}, identified by the transitions between states.
+The instantaneous profile represents step-like changes between high and low levels of the magnetic field, while the ramp profile has linear variations between these states.
+The rectified cosine profile is a common waveform found in the literature that has a continuous variation of the applied magnetic field.
 
@@
   \centering
- %\includegraphics[width=5cm]{brayton-kitanovski}
-  \caption{Temperature-entropy diagram for the Brayton AMR cycle, as experienced by the magnetocaloric (MC)  material \cite{bib:kitanovski}. The applied magnetic field is denoted by $H$.}
+  \includegraphics[width=8cm]{profiles_all}
+  \caption{Magnetic profiles studied in this paper}
+  \label{fig:profiles}
+\end{figure}
+
+The instantaneous magnetic profile is characteristic of the Brayton AMR cycle, where the magnetization and demagnetization steps must be done adiabatically, as shown in \autoref{fig:brayton}; compared to other common cycles such as the Ericsson, the Brayton cycle results in the highest cooling capacities for the same operating  parameters \cite{bib:kitanovski}, at the expense of lower coefficient of performance.
+
+\begin{figure}[!ht]
+  \centering
+
+  \caption{Brayton AMR cycle}
   \label{fig:brayton}
@@
 
-The performance of AMR-based magnetic refrigerators is directly related to their thermodynamic cycle, and hence to the magnetic and fluid flow profiles.
-With this motivation, there are multiple studies in the literature regarding these waveforms.
-In general, the fluid flow profile is more easily changed in experimental prototypes with modifications in the hydraulic system, and it can be optimized for a given magnetic profile for higher cooling capacity or coefficient of performance \cite{bib:teyber17_exper,bib:nakashima18-influen-exp,FORTKAMP2018}.
-The actual shape of waveform depends on the hydraulic system configuration; single- or two-regenerators systems usually employ piston pumps with sinusoidal fluid flow profiles, while more complex valving system yield trapezoidal fluid flow profiles, with periods of no flow (when fluid is by-passed from the regenerator), periods with a constant flow rate and ramp transitions between these two states.
-
-In room temperature magnetic refrigeration, the magnetic profile is generated by permanent magnets, representing the most expensive part of a magnetic refrigerator \cite{bib:bjoerk16_lifetime}, and hence considered fixed in AMR devices.
-Although the magnetic profile can be changed with motion control on the permanent magnets \cite{bib:benedict16_desig}, this is a topic yet to be better investigated, and most studies on the subject are numerical.
-The ideal Brayton cycle requires a instantaneous magnetic profile (square waveform), but in practice it is difficult to generate  stepwise variations of the magnetic field  using rotating permanent magnets arrays.
-Most magnetic refrigerators developed so far operate with a more continuous magnetic profile, such as the rectified cosine profile \cite{bib:tura-rowe-amr,bib:arnold14_desig,bib:trevizoli15_desig_halbac}, which is easily generated with compact devices and capable of achieving high levels of magnetic field \cite{bib:trevizoli16_pump}, but at the cost of  too brief demagnetization periods.
-
-Many works on the analysis of  magnetic profiles use a ramp profile as  an approximation of the instantaneous profile with finite transition times between the magnetization levels, making it easier to generate the profiles with permanent magnets.
-The performance of an AMR subjected to a ramp magnetic profile and a instantaneous fluid flow profile with different parameters has been investigate \cite{bib:bjoerk11_amr}, but the emphasis was on the synchronization with the fluid flow profile and the authors did not compare different magnetic profiles.
-A study that  implemented different cycles through a ramp profile and a modification of the rectified cosine (consisting only of linear variations) \cite{bib:kitanovski} concluded that, with the same operating parameters parameters (temperature span between heat source and heat sink, frequency, mass flow rate, regenerator geometry, maximum applied magnetic field), the Brayton cycle (realized by a ramp profile) results in the highest cooling capacities; the same profile could be used in Ericsson cycles, with the magnetization processes done isothermally instead of adiabatically, and the result is higher values of the coefficient of performance.
-The conclusion that the instantaneous magnetic profile results in higher cooling capacities for a given temperature span, compared to other waveforms is also presented in \cite{bib:asme-mce}
-
-In Fig.~\ref{fig:cycles}, the instantaneous and rectified cosine waveforms evaluated in this work are shown in terms of the average applied magnetic field (${B}$) that acts on the regenerator (vertical axis) for one AMR cycle parameterized in a time variable ($t$) ranging from 0 to the cycle period $\tau$ (horizontal axis).
+ In practice, the ramp profile is a more feasible realization with finite transition times, and its synchronization with the fluid flow profile can yield different performance levels \cite{TUSEK20111507}.
+In particular, the plateaus of magnetic field should be centered with the blow durations \cite{bib:bjoerk11_amr}.
+\autoref{fig:sync} shows the syncronization schema between the magnetic and fluid flow profiles, showing the ramp magnetic profile as an example.
 
@@
   \centering
-  \includegraphics[width=7cm]{profiles_all.eps}
-  \caption{Instantaneous and rectified cosine magnetic profiles in terms of the average magnetic field over the regenerator for one AMR cycle as a function of time ($t$). }
-  \label{fig:cycles}
+  \includegraphics[width=8cm]{profiles_rm_and_flow_instantaneous}
+  \caption{Ramp magnetic profile (solid lines) and instantaneous fluid flow profile (dashed lines)}
+  \label{fig:sync}
 \end{figure}
 
-The present work extends these analyses and attempts to systematically compare the performance of a magnetic refrigerator operating with instantaneous, rectified cosine and ramp magnetic  profiles under different parameters, with the goal of selecting the best magnetic profile for certain requirements of cooling capacity of a target application.
-In comparison with the previously cited works, we analyze the effect of different regenerator geometries and different levels of the magnetic field and mass flow rate.
-In particular, in comparison with the work of \cite{bib:kitanovski}, where the authors studied different combinations of flow and magnetic profiles to yield various thermodynamic cycles, we fix the fluid flow profile to better investigate the effect of the magnetic profile, which is used in the design of magnetic circuits.
+This paper uses the AMR model developed by \cite{bib:trevizoli16_perfor_model}, and the same authors had studied magnetic profiles waveforms in an earlier work \cite{bib:asme-mce}.
+However, their amplitudes was not varied, nor were they investigated with different geometries.
+
+The present works combines the gaps from the above cited papers in investigating the performance of a magnetic refrigerator under different magnetic profile waveforms.
+These waveforms are mathematically modeled, and the cooling capacity and coefficient of performance are calculated based on the profiles parameters, while also investigated how the AMR geometry affect the performance in combinations with the magnetic profile.
+The fluid flow profile is assumed fixed in shape, although its parameters are also variied.
+The emulate constraints on an operating point of actual magnetic refrigeration devices, the temperature span is set fixed, and hence few comments are made on second-law efficiency.
 

### 2019-09-10 PaperMagneticProfiles_JBSMSE.tex
Update title. 
Develop section on AMR model.

@@
 \newcommand{\bmin}{\ensuremath{{B}\ped{min}}}
+\newcommand{\mrate}{\rate{m}}
 
@@
 
-\title{Performance of Magnetic Refrigerators Operating with Different Magnetic Profiles}
+\title{Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators}
 
@@
 
-\section{NUMERICAL SIMULATIONS}
-\label{sec:numer-simul}
+\section{Materials and methods}
+\label{sec:materials-methods}
+
+In this work, we perform numerical simulations of a previously developed AMR model, varying the profile and geometric parameters.
+We also couple a model for calculating  the power comsumption of a proposed valve system, a topic understudied in the literature.
+With this, we can evaluate the influence of the profile on cooling capacity and coefficient of performance.
+
+\subsection{AMR model}
+\label{sec:amr-model}
+
+\subsubsection{Governing equations}
+\label{sec:governing-equations}
 
 Simulations were performed using a one-dimensional AMR mathematical model \cite{bib:asme-mce,bib:trevizoli16_perfor_model}.
-The simulated magnetic refrigerators are composed of multiple prismatic regenerators filled with gadolinium (Gd) spheres as the magnetocaloric solid matrix, with the parameters shown in Table~\ref{tab:params}.
-The fluid is a mixture of water and ethylene glycol, in the proportion of \SI{80}{\percent}-\SI{20}{\percent} in volume.
+Here we will show a summarized version focusing on the governing equations.
+This model solves momentum and energy balance equations for the solid and fluid phases, represented by indices 's' and 'f', respectively.
+The model geometry is depicted in \autoref{fig:amrmodel}, and assumes regenerators composed of monodisperse packed spheres with porosity $\varepsilon$.
 
-\begin{table}[!ht]
+\nomenclature[is]{s}{solid phase}
+\nomenclature[if]{f}{fluid phase}
+
+\begin{figure}[!ht]
   \centering
-  \caption{Geometric and operation parameters for the simulated AMR devices}
-  \begin{tabular}{c|c}
-\hline
-    \textbf{Parameter}&\textbf{Value}\\
-\hline
-Regenerator height & \SI{20}{\mm}\\
-Regenerator width & \SI{25}{\mm}\\
-Regenerator length & \SI{100}{\mm}\\
-Number of regenerators & \num{11} \\
-Particle diameter & \SI{0.5}{\mm}\\
-Hot source temperature & \SI{298}{\kelvin}\\
-Cold source temperature & \SI{278}{\kelvin}\\
-\hline
-  \end{tabular}
-  \label{tab:params}
-\end{table}
+  \includegraphics[width=8cm]{reg3d}
+  \caption{AMR model geometry}
+  \label{fig:amrmodel}
+\end{figure}
 
-The AMR model solves mass and energy conservation equations for the solid and the fluid domains in an active magnetic regenerator.
-In this work, regenerators were assumed to be adiabatic to the environment.
-All beds experience the same flow and magnetic profiles, as detailed in the following sections.
+The momentum equation for the fluid domain is:
+
+\begin{equation}
+\label{eq:75}
+  \frac{\rho\ped{f}}{\varepsilon} \diffp{V_z}{t}= -\diffp{P}{z} - \frac{\mu\ped{f}}{K} V_z - \frac{c\ped{E} \rho\ped{f}}{K^{1/2}} \left| V_z\right| V_z 
+\end{equation}
+
+\nomenclature[ak]{$K$}{permeability of the porous medium [\si{\meter\square}]}
+\nomenclature[ac]{$c\ped{E}$}{Ergun constant of the porous medium}
+\nomenclature[ar]{$\rho$}{density [\si{\kg\per\cubic\meter}]}
+\nomenclature[be]{$\varepsilon$}{porosity}
+\nomenclature[av]{$V$}{velocity [\si{\meter\per\second}]}
+\nomenclature[ap]{$P$}{pressure [\si{\pascal}]}
+\nomenclature[bu]{$\mu$}{dynamic viscosity [\si{\pascal\second}]}
+
+\noindent and is solved for the time-dependent uniform fluid velocity through the bed.
+
+The energy equation for the fluid phase can be written as:
+
+\begin{equation}
+\label{eq:78}
+\begin{split}
+  \rho\ped{f} c_{p,\mathrm{f}} \left(\varepsilon \diffp{T\ped{f}}{t} + V_z\diffp{T\ped{f}}{z}\right) = & -\hheat\ped{sf} \beta \left(T\ped{f} - T\ped{s}\right) \\
+& + \left|V_z\diffp{p}{z}\bigg|_f \right| \\
+& + \varepsilon\left(k\ped{f}\ap{eff}  +\rho\ped{f} c_{p,\mathrm{f}} D\ped{ld}\right)\diffp[2]{T\ped{f}}{z} \\
+& + \rate{q}\ped{csg}  
+\end{split}
+\end{equation}
+
+\nomenclature[at]{$T$}{temperature [\si{\kelvin}]}
+\nomenclature[at]{$t$}{time [\si{\second}]}
+\nomenclature[az]{$z$}{axial coordinate [\si{\meter}]}
+
+\nomenclature[aq]{$\rate{q}\ped{csg}$}{volumetric casing losses in the AMR model [\si{\watt\per\cubic\meter}]}
+\nomenclature[ic]{csg}{regenerator casing}
+\nomenclature[ah]{$\hheat$}{heat transfer coefficient [\si{\watt\per\meter\squared\per\kelvin}]}
+\nomenclature[aa]{$A\ped{sf}$}{contact surface area between solid and fluid phases in the regenerator [\si{\meter^2}]}
+\nomenclature[is]{sf}{relative to the heat transfer between solid and fluid phases in the regenerator}
+\nomenclature[azb]{$\beta$}{surface area density [\si{\squared\meter\per\cubic\meter}]}
+\nomenclature[ak]{$k\ap{eff}$}{effective thermal conductivity [\si{\watt\per\meter\per\kelvin}]}
+\nomenclature[ad]{$D\ped{ld}$}{dispersion term in the AMR model [\si{\meter\square\per\second}]}
+\nomenclature[af]{$f$}{cycle frequency [\si{\hertz}]}
+\nomenclature[azf]{$\Phi$}{utilization}
+\nomenclature[am]{$m$}{mass [\si{\kg}]}
+
+\nomenclature[azt]{$\tau$}{time period [\si{\second}]}
+\nomenclature[ac]{$c$}{specific heat [\si{\joule\per\kg\per\kelvin}]}
+
+\noindent while the energy equation for the solid phase is written as:
+
+\begin{equation}
+\label{eq:88}
+  \rho\ped{s} c\ped{s}(1 - \varepsilon)\diffp{T\ped{s}}{t} = \hheat\ped{sf}\beta(T\ped{f}-T\ped{s}) + (1-\varepsilon)k\ped{s}\ap{eff}\diffp[2]{T\ped{s}}{z}
+\end{equation}
+
+Initial and boundary conditions, solution methods, convergence analyses, and closure relations for the porous media terms are described in \cite{bib:trevizoli16_perfor_model}.
+This AMR model solves the above equations for one regenerator operating between given sources temperatures, during one full cycle (hot and cold blows and  magnetization and demagnetization periods), given specified operating conditions (to be discussed later).
+
+The casing heat transfer term $\rate{q}\ped{csg}$ in \autoref{eq:78} is calculated solving the heat conduction in the regenerators casing \cite{bib:trevizoli16_perfor_model}, and can be neglected to simplify some analyses.
+More details are provided in \autoref{sec:results-discussions}.
+
+\subsubsection{How the fluid flow profile is used}
+\label{sec:how-fluid-flow}
+
+The pressure gradient in \autoref{eq:75}is modeled as:
+
+\begin{equation}
+\label{eq:76}
+-\diffp{P}{z} = \rho\ped{f} A\ped{t} g(t)
+\end{equation}
+
+\noindent where \(g(t)\) is a dimensionless function that expresses the mathematical waveform of the pressure gradient, and  \(A\ped{t}\) is its amplitude,  adjusted in a convergence loop; the mass flow rate calculated from the Darcy velocity from \autoref{eq:75} is compared with the input value of mass flow rate until these values converge.
+The waveform $g(t)$ represents the fluid flow profile used.
+
+\nomenclature[ag]{$g(t)$}{dimensional waveform of the pressure gradient term in the fluid momentum equation}
+\nomenclature[aA]{$A\ped{t}$}{amplitude of the pressure gradient waveform in the fluid momentum equation [\si{\meter\per\second\square}]}
+
+\subsubsection{How the magnetic profile is used}
+\label{sec:how-magnetic-profile}
+
+The magnetic profile is modeled by a waveform of magnetic field strength $H$ applied perpendicular to the regenerators, as shown in \autoref{fig:amrmodel}.
+The magnetic field is assumed uniform throughout the beds.
+The applied field is corrected from demagnetization effects to yield the effective field inside the regenerators:
+
+\begin{equation}
+  \label{eq:6}
+  H\ap{eff} = H - N\ped{D} M
+\end{equation}
+
+\nomenclature[am]{$M$}{magnetization field [\si{\ampere\per\meter}]}
+\nomenclature[an]{$N\ped{D}$}{demagnetization tensor}
+
+\noindent where $M$ is the magnetization field of the material, and $N\ped{D}$ is a demagnetization factor.
+
+The magnetocaloric effect is implemented in the so-called discrete approach \cite{bib:nielsen11_review}; every time the magnetic field changes, based on the input magnetic profile, the solid temperature is calculated according to:
+
+\begin{equation}
+  \label{eq:89}
+  T\ped{s}(t + \Delta{}t) = T\ped{s}(t) + \dtad \left(T\ped{s}(t),H\ap{eff}(t),H\ap{eff}\left(t + \Delta{}t\right)\right)
+\end{equation}
+
+\nomenclature[ct]{$\dtad$}{adiabatic temperature variation [\si{\kelvin}]}
+
+\noindent where the adiabatic temperature variation $\dtad$ is calculated from \textcolor{black}{tabulated} experimental \textcolor{black}{data} for magnetocaloric materials as function of temperature and effective field.
+\cite{bib:trevizoli16_perfor_model}.
+
+\subsubsection{Evaluation of solid and fluid properties}
+\label{sec:eval-solid-fluid}
+
+The fluid properties are considered constant in the momentum equation to decouple the solution \textcolor{black}{procedures to determine} the velocity and temperature fields.
+The properties are computed at the average temperature between the hot and cold sources temperatures, and are evaluated from interpolated tables exported from the EES software \cite{bib:klein13-ees}.
+In all simulations shown in this work, the heat transfer fluid is a mixture of water/ethylene-glycol with concentration \num{80}/\SI{20}{\percent} vol.
+For the energy equations, the fluid properties are also calculated from tabulated data, but the temperature dependence is considered.
+
+n this chapter, all simulations use gadolinium or its allows as the magnetocaloric material.
+Gadolinium is a benchmark material with a Curie temperature of \SI{290}{\kelvin}.
+\textcolor{black}{For simplicity, the solid} density is assumed constant at $\rho\ped{s} = \SI{7900}{\kg\per\cubic\meter}$ and the solid \textcolor{black}{thermal} conductivity is set to $k\ped{s} = \SI{10.5}{\watt\per\meter\per\kelvin}$.
+The specific heat \textcolor{black}{capacity} of \ce{Gd} is calculated as a function of temperature and magnetic field based on experimental \textcolor{black}{data}, using a bi-linear interpolation scheme; more details on the experimental dataset \textcolor{black}{are available} in \cite{bib:trevizoli16_perfor_model}.
+
+In this work, both single- and multilayer regenerators are considered.
+For the multilayer simulations, alloys of gadolinium and yttrium are used in the form \ce{Gd_{1-x}Y_x}, where $x$ is the yttrium fraction.
+\textcolor{black}{This fraction} decreases the Curie temperature  \textcolor{black}{of the} alloy relative to that of pure gadolinium.
+Due to the lack of experimental  \textcolor{black}{data on the magnetocaloric properties of} \ce{Gd_{1-x}Y_x} alloys at the time \textcolor{black}{this analysis was made}, a simpler approach was used \textcolor{black}{in which} the properties of alloys with {a} low yttrium fraction are \textcolor{black}{identical to those} of pure gadolinium, except for the Curie temperature \textcolor{black}{(which is shifted to lower values)}.
+
+\subsubsection{Performance metrics}
+\label{sec:performance-metrics}
+
+The AMR model considers only one bed and assumes $N\ped{r}$ identical beds experience the same cycle, multiplyind the performance metrics below by this factor
+
+\nomenclature{an}{$N\ped{r}$}{number of regenerators}
+
+The cooling capacity is calculated as \cite{bib:trevizoli16_perfor_model}:
+
+\begin{equation}
+\label{eq:99}
+\qc = N\ped{r}\frac{1}{\tau} \int_{\tau\ped{HB}} \mrate\ped{f}(t) c_{p,\mathrm{f}} \left( T\ped{C} -T\ped{f,CE} \right) \diffd{t}
+\end{equation}
+
+\noindent where $\tau$ is the cycle period, and $\tau\ped{HB}$ is the duration of the hot blow, during which the cold end temperature is compared to the cold source temperature.
+
+\nomenclature[vh]{HB}{hot blow}
+\nomenclature[vc]{CE}{cold end}
+\nomenclature[am]{$\mrate\ped{f}$}{mass flow rate [\si{\kg\per\second}]}
+\nomenclature[vc]{C}{cold source}
+\nomenclature[vc]{H}{hot source}
+
+The magnetic power to operate the AMR cycle is modeled as the ideal Carnot power, ignoring most thermal irreversibilities:
+
+\begin{equation}
+\label{eq:100}
+\wmag = \qc \frac{T\ped{H} - \tc}{\tc}
+\end{equation}
+
+\noindent while the fluid friction irreversibility is accounted for in the calculation of the pumping power:
+
+\begin{equation}
+\label{eq:103}
+\wpump = N\ped{r}\frac{1}{\tau}\int_0^{\tau}\frac{\rate{m}\ped{f}}{\rho\ped{f}} \Delta P \diffd{t}
+\end{equation}
+
+\noindent where $\Delta P$ is the total pressure drop through the regenerator.
+
+\nomenclature[awm]{$\wpump$}{pumping power [\si{\watt}]}
+\nomenclature[awm]{$\wmag$}{magnetic power [\si{\watt}]}
+\nomenclature[ap]{$\Delta P$}{pressure drop across one region [\si{\pascal}]}
 
@@
 
-\section{RESULTS AND DISCUSSIONS}
+\section{Results and Discussions}
 \label{sec:results-discussions}
+
+The simulated magnetic refrigerators are composed of multiple prismatic regenerators filled with gadolinium (Gd) spheres as the magnetocaloric solid matrix, with the parameters shown in Table~\ref{tab:params}.
+The fluid is a mixture of water and ethylene glycol, in the proportion of \SI{80}{\percent}-\SI{20}{\percent} in volume.
+
+\begin{table}[!ht]
+  \centering
+  \caption{Geometric and operation parameters for the simulated AMR devices}
+  \begin{tabular}{c|c}
+\hline
+    \textbf{Parameter}&\textbf{Value}\\
+\hline
+Regenerator height & \SI{20}{\mm}\\
+Regenerator width & \SI{25}{\mm}\\
+Regenerator length & \SI{100}{\mm}\\
+Number of regenerators & \num{11} \\
+Particle diameter & \SI{0.5}{\mm}\\
+Hot source temperature & \SI{298}{\kelvin}\\
+Cold source temperature & \SI{278}{\kelvin}\\
+\hline
+  \end{tabular}
+  \label{tab:params}
+\end{table}
 

### 2019-09-11 PaperMagneticProfiles_JBSMSE.tex
Develop section on hydraulic system  model.

@@
 \newcommand{\mrate}{\rate{m}}
+\newcommand{\wvalven}{\w\ped{valve,n}}
+\newcommand{\wrelayn}{\w\ped{relay,n}}
 
@@
 
-\subsection{Flow profile}
-\label{sec:flow-profile}
+\subsection{Hydraulic system  and fluid flow profile model}
+\label{sec:hydr-syst-model}
 
-The flow profile through a given bed, i.e.
-the mass flow rate as a function of time $\rate{m}\ped{f} (t)$, is assumed to be a square wave as that shown in Fig.~\ref{fig:mprofile}.
-The cold blow has a duration of $\tau\ped{CB}$ and the  hot blow a duration of $\tau\ped{HB}$, while the period of one AMR cycle is $\tau$.
-Limiting the blow times during each half-cycle to periods where the magnetic field is at its maximum and minimum can result in increased performance \cite{bib:nakashima17_avaliac}.
-In this work, the blows are supposed to be in balance, thus, $\tau\ped{CB} = \tau\ped{HB}$.
-An important parameter regarding the flow profiles can be defined, which is the blow fraction, $F\ped{B}$:
-
-\begin{equation}
-  \label{eq:1}
-  F\ped{B} = \frac{\tau\ped{CB} + \tau\ped{HB}}{\tau}
-\end{equation}
+The canonical fluid flow profile considered in this work \textcolor{black}{ is the square wave or \emph{instantaneous profile}}, because of the instantaneous change in flow rate, as shown in \autoref{fig:mprofile}.
 
@@
   \centering
-%  \includegraphics[width=7cm]{mprofile}
-  \caption{Instantaneous flow profile used in the numerical simulations.
-"Positive" mass flow rate indicates flow in the direction from the cold to the hot source, and negative values represent the opposite direction.
-}
+  \includegraphics[width=8cm]{mprofile}
+  \caption{Instantaneous fluid flow profile}
   \label{fig:mprofile}
@@
 
-\subsection{Magnetic profile}
-\label{sec:magnetic-profile}
+The \textcolor{black}{instantaneous mass flow rate}, \(\rate{m}\ped{f}(t)\), is defined over a cycle with \textcolor{black}{a} period \(\tau\), and represents the fluid flow \textcolor{black}{through} a given regenerator bed.
+The so-called \emph{hot cycle}, \textcolor{black}{during which} the MCM is magnetized, occupies the \textcolor{black}{time interval} \(0 \le t < \nicefrac{\tau}{2}\), while the \emph{cold cycle}
+lies \textcolor{black}{between} \(\nicefrac{\tau}{2} \le t \le \tau\). The flow profile oscillates between two plateaus of equal magnitude
+\(\rate{m}\ped{f,max}\) \textcolor{black}{and} opposite directions, \textcolor{black}{which} are centered in each half-cycle. During the hot cycle, the cold
+blow period is \(\tau\ped{CB}\), and during the cold cycle the hot blow period is \(\tau\ped{HB}\). If the flow is balanced, then \(\tau\ped{CB} = \tau\ped{HB}\).
 
-The AMR mathematical model takes the magnetic profile as an input, and the profiles represented in Fig.~\ref{fig:cycles} were tested with different parameters.
-The mathematical definitions for the magnetic profiles over a cycle of period $\tau$ are as follows; the instantaneous profile (represented by the index ``I'') and the rectified cosine profile (represented by ``RC'') are defined solely in terms of the extrema values $\bmax$ and $\bmin$:
+During each half cycle, there are periods \textcolor{black}{without}  fluid flow, defined as:
 
 \begin{equation}
-\average{B}\ped{I}(t)=
-\begin{cases}
-\average{B}\ped{max}, & 0 \le t < \nicefrac{\tau}{2} \\
-\average{B}\ped{min}, & \nicefrac{\tau}{2} \le t < \tau\\
-\end{cases}
-\label{eq:4}
+\label{eq:48}
+\tau\ped{0,HC} = \frac{\nicefrac{\tau}{2} - \tau\ped{CB}}{2}
 \end{equation}
@@
 \begin{equation}
-\average{B}\ped{RC}(t) = \bmin + \left(\bmax - \bmin\right)  \left\lvert \cos\left( \frac{\pi}{\tau} \left( t - \frac{\tau}{4}\right)\right) \right\rvert
-\label{eq:5}
+\label{eq:49}
+\tau\ped{0,CC} = \frac{\nicefrac{\tau}{2} - \tau\ped{HB}}{2}
 \end{equation}
 
-In this work, the average values of the magnetic field during each half-AMR cycle are considered for comparison between profiles.
-The average magnetic profile during the hot cycle ($0 \le t < \nicefrac{\tau}{2}$) is denoted $B\ped{h}$ and the average during the cold cycle  ($ \nicefrac{\tau}{2} \le t < \tau$) is denoted $B\ped{l}$.
+where HC and CC stand for hot \textcolor{black}{cycle} and cold cycle, respectively.
 
-\subsection{AMR operating parameters}
-\label{sec:amr-oper-param}
+\nomenclature[vh]{HC}{hot cycle}
+\nomenclature[vc]{CC}{cold cycle}
 
-Different numerical simulations were carried with different operating parameters such as: AMR cycle frequency ($f$), blow fraction ($F\ped{B}$) and utilization ($\Phi$) which is defined as:
+The profile can be mathematically defined as:
 
 \begin{equation}
-\Phi = \frac{\rate{m}\ped{f,max}F\ped{B}\frac{\tau}{2}c_{p,\mathrm{f}}}{m\ped{s} c\ped{s}}
-\label{eq:2}
+\rate{m}\ped{f}(t)=
+\begin{cases}
+0, & 0 \le t < \tau\ped{0,HC} \\
+\rate{m}\ped{f,max}, & \tau\ped{0,HC} \le t \le \nicefrac{\tau}{2} - \tau\ped{0,HC} \\
+0, & \nicefrac{\tau}{2} - \tau\ped{0,HC} < t < \nicefrac{\tau}{2} + \tau\ped{0,CC} \\
+-\rate{m}\ped{f,max}, & \nicefrac{\tau}{2} + \tau\ped{0,CC} \le t \le \tau - \tau\ped{0,CC} \\
+0, &  \tau - \tau\ped{0,CC} <  t < \tau \\
+\end{cases}
+\label{eq:50}
 \end{equation}
 
-\noindent where $c_{p,\mathrm{f}}$ is the constant-pressure specific heat for the fluid, and $m\ped{s}$ and $c\ped{s}$ are the mass and specific heat of the solid phase in one bed.
+When the blows have different time durations, the AMR cycle is considered unbalanced, and this \textcolor{black}{is known to have} a negative effect on performance \cite{bib:eriksen16_effec,bib:nakashima18-influen-exp}.
+In this work, the blows are always balanced, hence the blow fraction, the ratio of blow durations to cycle period \cite{bib:nakashima18-influen-exp}, can be evaluated as:
+
+\begin{equation}
+\label{eq:59}
+F\ped{B} = \frac{2\tau\ped{B}}{\tau}
+\end{equation}
+
+\noindent where $\tau\ped{B}$ is the duration of one blow.
+
+\nomenclature[azt]{$\tau\ped{B}$}{blow duration [\si{\second}]}
+
+The hydraulic system to modulate this fluid flow through different regenerators at different time instants is composed of a pump and a set of electronic valves which can be precisely controlled to yield the desired blow durations.
+The electrical power consumed by the valve array is computed separately from other work contributions.
+An application of electronic valves in AMR devices has been presented by \cite{bib:nakashima18-perfor-asses-solen-valves-flow}.
+
+Due to evolving developments in our group, two types of valves are considered, as will be elaborated in \autoref{sec:results-discussions}.
+
+The first approach, called \emph{Type B valves}, uses the  model \textcolor{black}{of} \cite{bib:cardoso16_trans}, assuming that the individual consumption of each valve is independent of frequency and blow fraction.
+The valve power  $\wvalve$ can be computed as:
+
+\begin{equation}
+  \label{eq:58}
+  \wvalve = N\ped{v}F\ped{B}\left(\wvalven + \frac{1}{2}\wrelayn\right)
+\end{equation}
+
+\noindent where $N\ped{v}$ is the number of valves, $\wvalven$ is the measured average nominal power for one normally-closed electronic valve and $\wrelayn$ is the nominal power for one controlling relay.
+The factor $\nicefrac{1}{2}$ is due to two valves being controlled by one relay.
+
+\nomenclature[an]{$N\ped{v}$}{number of valves}
+\nomenclature[aw]{$\wvalve$}{valve power [\si{\watt}]}
+\nomenclature[aw]{$\wvalven$}{nominal power comsumption of one valve [\si{\watt}]}
+\nomenclature[aw]{$\wrelayn$}{nominal power comsumption of one relay [\si{\watt}]}
+
+In the second approach, \emph{Type A} valves are used, with lower nominal power but that depends on frequency and blow fraction. For these valves, the valve power was experimentally correlated as:
+
+\begin{equation}
+  \label{eq:198}
+  \wvalve\,[\si{\watt}]= N\ped{v}\left(0.927 f\,[\si{\hertz}] + 1.023 F\ped{B} + 0.226 f\,[\si{\hertz}] F\ped{B} - 0.037\right)
+\end{equation}
+
+Equation~\eqref{eq:198} was correlated for blow fractions of \num{50} and \SI{100}{\percent} and for frequencies in the range \textcolor{black}{of} \num{0.2}--\SI{1.6}{\hertz}, with an uncertainty \textcolor{black}{on} the order of \SI{0.4}{\watt} for a single valve.
+The use of different valve types will be discussed among the presented results.
+
+Indepedent of the valve type used, it is also assumed that this valve system can produce the fluid flow profile \textcolor{black}{shown in} \autoref{fig:mprofile}, where the displaced fluid mass during one blow in one regenerator bed is $\rate{m}\ped{f,max} F\ped{B} \nicefrac{\tau}{2}$.
+
+The \emph{utilization factor} can then be calculated as:
+
+\begin{equation}
+  \label{eq:110}
+  \Phi = \frac{\rate{m}\ped{f,max} F\ped{B} c\ped{s}}{2 f m\ped{s} c\ped{s}}
+\end{equation}
+
+\nomenclature[bf]{$\Phi$}{utilization factor}
+
+\textcolor{black}{For an even number of poles in the magnetic circuit}, it may be advantageous to employ an odd number of regenerator beds to  \textcolor{black}{break the symmetry between the magnetic circuit and the beds, thus avoiding positions of equilibrium between magnetic forces which result in torque oscillations} \cite{bib:eriksen}.
+\textcolor{black}{Additionally}, in general, two valves per regenerator  may be necessary (one at each end), to independently control  the hot and cold blows for each bed and correct flow \textcolor{black}{imbalance}; thus, in all results in this work, the number of valves is \textcolor{black}{calculated as}:
+
+\begin{equation}
+  \label{eq:111}
+  N\ped{v} = 2 N\ped{r}
+\end{equation}
 

### 2019-09-11 PaperMagneticProfiles_JBSMSE.tex
Add section on COP.
Add section on definition of the magnetic profiles.

@@
 
+\subsection{Calculation of the coefficient of performance}
+\label{sec:calc-coeff-perf}
+
+The coefficient of performance \textcolor{black}{takes} the cooling capacity as \textcolor{black}{the main} output \textcolor{black}{parameter from} the AMR model, \textcolor{black}{in addition to} all previously cited power contributions:
+
+\begin{equation}
+  \label{eq:112}
+  \cop = \frac{\qc}{\wpump + \wmag + \wvalve}
+\end{equation}
+
+\subsection{Definition of magnetic profiles}
+\label{sec:defin-magn-prof}
+
+The magnetic profiles considered in this work were shown in \autoref{fig:profiles}; here their mathematical definitions are presented.
+The profiles are presented in terms of the flux density $B = \mu_0 H$, where $\mu_0$ is the permeability of free space; the magnetic field $H$ is used in the evaluation of the magnetocaloric effect (cf.
+\autoref{sec:how-magnetic-profile}).
+
+The instantaneous profile (represented by the subscript ``IT'') and the rectified cosine profile (represented by ``RC'') are defined solely in terms of the \textcolor{black}{(extreme)} values $B\ped{min}$ and $B\ped{min}$:
+
+\nomenclature[vi]{IT}{instantaneous magnetic profile}
+\nomenclature[vr]{RC}{rectified cosine magnetic profile}
+
+\begin{equation}
+{B}\ped{IT}\,(t)=
+\begin{cases}
+{B}\ped{max}, & 0 \le t < \nicefrac{\tau}{2} \\
+{B}\ped{min}, & \nicefrac{\tau}{2} \le t < \tau\\
+\end{cases}
+\label{eq:199}
+\end{equation}
+
+\begin{equation}
+{B}\ped{RC}\,(t) = B\ped{min} + \left(B\ped{max} - B\ped{min}\right)  \left\lvert \cos\left( \frac{\pi}{\tau} \left( t - \frac{\tau}{4}\right)\right) \right\rvert
+\label{eq:200}
+\end{equation}
+
+As previously discussed, a suitable approximation of the instantaneous profile is the \textcolor{black}{\emph{magnetic ramp profile}, shown} in \autoref{fig:ramp}.
+The so-called \emph{hot cycle}, \textcolor{black}{during which} the MCM is magnetized, occupies the range \(0 \le t < \nicefrac{\tau}{2}\), while the \emph{cold cycle} lies in the range \(\nicefrac{\tau}{2} \le t < \tau\).
+The magnetic profile oscillates  between a low value \({B}\ped{min}\) and a high value \({B}\ped{max}\), and \textcolor{black}{remains} at each plateau for a period of \(\tau\ped{M}\).
+The plateaus are balanced and centered at each half-cycle.
+
+\begin{figure}[!ht]
+  \centering
+  \includegraphics[width=7cm]{profile_rm}
+  \caption{\textcolor{black}{Magnetic ramp}  profile}
+  \label{fig:ramp}
+\end{figure}
+
+The \emph{ramp period} \(\tau\ped{R}\) \textcolor{black}{is} defined as:
+
+\begin{equation}
+\label{eq:201}
+\tau\ped{R} = \frac{1}{4}\left(\tau - 2 \tau\ped{M}\right)
+\end{equation}
+
+\noindent such that there are four ramp periods in one full cycle. The ramp rate, \(\theta\ped{R}\), is:
+
+\begin{equation}
+\label{eq:202}
+\tan \theta\ped{R} = \frac{\left({B}\ped{max} - {B}\ped{min}\right)}{2\tau\ped{R}}
+\end{equation}
+
+\nomenclature[azt]{$\tau\ped{R}$}{ramp period in the \textcolor{black}{magnetic} ramp profile [\si{\second}]}
+\nomenclature[azt]{$\tau\ped{M}$}{magnetization period in the \textcolor{black}{magnetic} ramp  profile [\si{\second}]}
+\nomenclature[azo]{$\theta\ped{R}$}{ramp rate in the \textcolor{black}{magnetic} ramp profile}
+
+The magnetization fraction, \(F\ped{M}\), is the fraction of the cycle \textcolor{black}{during which} the magnetocaloric material is \textcolor{black}{subjected to a} constant magnetic field:
+
+\begin{equation}
+\label{eq:204}
+F\ped{M} = \frac{2\tau\ped{M}}{\tau}
+\end{equation}
+
+\nomenclature[af]{$F\ped{M}$}{magnetization fraction}
+
+The ramp profile (``RM'') can be mathematically defined as:
+
+\begin{equation}
+{B}\ped{RM}(t)=
+\begin{cases}
+\nicefrac{\left({B}\ped{max} + {B}\ped{min}\right)}{2} + t \tan \theta\ped{R} , & 0 \le t < \tau\ped{R} \\
+{B}\ped{max}, & \tau\ped{R} \le t < \nicefrac{\tau}{2} - \tau\ped{R}\\
+{B}\ped{max} - \left(t - \left(\nicefrac{\tau}{2} - \tau\ped{R}\right)\right) \tan \theta\ped{R} , & \nicefrac{\tau}{2} - \tau\ped{R} \le t < \nicefrac{\tau}{2} + \tau\ped{R} \\
+{B}\ped{min}, & \nicefrac{\tau}{2} + \tau\ped{R} \le t < \tau - \tau\ped{R}\\
+{B}\ped{min} + \left(t - \left(\tau - \tau\ped{R}\right)\right) \tan \theta\ped{R} , & \tau - \tau\ped{R} \le t \le \tau \\
+\end{cases}
+\label{eq:203}
+\end{equation}
+
+\nomenclature[vr]{RM}{rectified cosine magnetic profile}
+
+Additionally, the average values of the magnetic field during each half-AMR cycle are considered for comparison between profiles.
+The average magnetic profile during the hot cycle ($0 \le t < \nicefrac{\tau}{2}$) is denoted $\average{B}\ped{high}$ and the average during the cold cycle  ($ \nicefrac{\tau}{2} \le t < \tau$) is denoted $\average{B}\ped{low}$.
+For the instantaneous waveform, these average values are identical to the extrema values.
+
 \section{Results and Discussions}

### 2019-09-11 PaperMagneticProfiles_JBSMSE.tex
Include text of comparison of instantaneous and rectified cosine waveforms.

@@
 
-The simulated magnetic refrigerators are composed of multiple prismatic regenerators filled with gadolinium (Gd) spheres as the magnetocaloric solid matrix, with the parameters shown in Table~\ref{tab:params}.
-The fluid is a mixture of water and ethylene glycol, in the proportion of \SI{80}{\percent}-\SI{20}{\percent} in volume.
+The analysis of magnetic profiles was performed in two different stages in the research of our group, as discussed below.
+
+\subsection{Comparison of instantaneous and rectified cosine profiles using a simplified model}
+\label{sec:comp-cosine-inst}
+
+In the first stage, the instantaneous and rectified cosine profiles are compared in the AMR model, considering monolayer regenerators without casing losses, and using Type B valves.
+The parameters used in all simulations are presented in \autoref{tab:params-cobem}.
 
@@
   \centering
-  \caption{Geometric and operation parameters for the simulated AMR devices}
+  \caption{AMR parameters kept fixed in the simulations with different magnetic profiles}
   \begin{tabular}{c|c}
 \hline
-    \textbf{Parameter}&\textbf{Value}\\
+\textbf{Parameter} & \textbf{Value}\\
 \hline
-Regenerator height & \SI{20}{\mm}\\
-Regenerator width & \SI{25}{\mm}\\
-Regenerator length & \SI{100}{\mm}\\
-Number of regenerators & \num{11} \\
-Particle diameter & \SI{0.5}{\mm}\\
-Hot source temperature & \SI{298}{\kelvin}\\
-Cold source temperature & \SI{278}{\kelvin}\\
+   $D\ped{p}$ & \SI{0.5}{\mm}\\
+$H\ped{r}$ & \SI{20}{\mm}\\
+$W\ped{r}$ & \SI{25}{\mm}\\
+$L\ped{r}$ & \SI{100}{\mm}\\
+$N\ped{r}$ & 11 \\
+$N\ped{v}$ & 22 \\
+$T\ped{H}$ & \SI{298}{\kelvin}\\
+$\tc$ & \SI{278}{\kelvin}\\
+$\w\ped{NV}$ & \SI{4}{\watt}\\
+$\w\ped{R}$ & \SI{0.36}{\watt}\\
 \hline
   \end{tabular}
-  \label{tab:params}
+
+  \label{tab:params-cobem}
 \end{table}
 
-\subsection{Comparison of the instantaneous and rectified cosine profiles}
-\label{sec:comp-inst-cosine}
-
-When comparing the magnetic profiles, the average magnetic field during the hot cycle is the same; this implies in a higher peak for the rectified cosine.
-For the cold cycle, there are two possible comparison methods:
+When comparing the \textcolor{black}{performances resulting from the application of the different} magnetic profiles, the average magnetic field during the hot cycle \textcolor{black}{will be considered} the same; this implies a higher peak for the rectified cosine.
+For the cold cycle, two comparison methods are considered, as shown in \autoref{fig:comparison-methods-profiles}:
 
@@
 
-As a reference, in all simulations  the minimum value for the rectified cosine was fixed at $\average{B}\ped{min,RC} = \SI{0.1}{\tesla}$.
-For the first comparison, the minimum value for the instantaneous value was kept at the same level ($\average{B}\ped{min,I} =  \average{B}\ped{min,RC}$), hence, the average low value for the RC profile was higher ($B\ped{l,RC} > B\ped{l,I}$).
-Although this does not seem a fair comparison, in practice it is feasible to generate a profile with a constant low-valued plateau for the magnetic field \cite{bib:insinga16_optim,bib:benedict16_desig}.
-For the other comparison method, the low level of the instantaneous profile was increased ($\average{B}\ped{min,I} >  \average{B}\ped{min,RC}$) to keep the average the same ($B\ped{l,RC} = B\ped{l,I}$).
-In addition, simulations were ran for various values of blow fraction and the optimal cases were selected; the rectified cosine profile can benefit from a smaller blow fraction because this can concentrate the flow during the periods of very high or low fields.
-In this section, all results show the resulting optimal case of the blow fraction for each profile (for the values tested): fluid flowing during the entire period for the instantaneous profile, and only during \SI{60}{\percent} of the period for the cosine profile.
+\textcolor{black}{For} reference, in all simulations,  the minimum value for the rectified cosine was fixed at ${B}\ped{min,RC} = \SI{0.1}{\tesla}$.
+\textcolor{black}{In} the first comparison, the minimum value for the instantaneous \textcolor{black}{waveform} was kept at the same level (${B}\ped{min,IT} =  {B}\ped{min,RC}$); hence, the average low value for the RC profile was higher ($\average{B}\ped{low,RC} > \average{B}\ped{low,IT}$).
+This represents common design scenarios: a constant low-valued plateau for the magnetic field for instantaneous-like magnetic profiles \cite{bib:insinga16_optim,bib:benedict16_desig}, or a low peak for the rectified cosine profile \cite{bib:trevizoli15_desig_halbac}.
+For the other comparison method, the low level of the instantaneous profile was increased (${B}\ped{min,IT} >  {B}\ped{min,RC}$) \textcolor{black}{in order} to keep the \textcolor{black}{same} average ($\average{B}\ped{low,RC} = \average{B}\ped{low,IT}$).
+
+\begin{figure}[!ht]
+  \centering
+  \subfloat[Same minimum]{\includegraphics[width=8cm]{profiles_it_and_rc_same_minimum}\label{fig:profiles_inst_cos_same_minimum}}
+\quad
+  \subfloat[Same average]{\includegraphics[width=8cm]{profiles_it_and_rc_same_average}\label{fig:profiles_inst_cos_same_average}}
+  \caption{Comparison methods for the instantaneous and rectified cosine profiles }
+  \label{fig:comparison-methods-profiles}
+\end{figure}
+
+In addition, simulations were \textcolor{black}{carried out} for various values of blow fraction; the rectified cosine profile can benefit from a smaller blow fraction because this can concentrate the flow during the periods of very high or low fields.
+In this section, all results use the critical value of blow fraction that maximized the cooling capacity: fluid flowing during the entire period for the instantaneous profile, and only during \SI{60}{\percent}  of the period (the smallest blow fraction tested) for the cosine profile; this latter case is shown in \autoref{fig:cos-inst-60}.
+
+\begin{figure}[!ht]
+  \centering
+  \includegraphics[width=7cm]{profiles_rc_and_flow_instantaneous}
+  \caption{Rectified cosine magnetic profile and the instantaneous flow profile with blow fraction of \SI{60}{\percent}}
+  \label{fig:cos-inst-60}
+\end{figure}
 
@@
 The horizontal axis shows the average value during the high field region.
-Notice how the results are conflicting; for Fig.~\ref{fig:comp_min}, the instantaneous profile almost always yields a higher performance, while for Fig.~\ref{fig:comp_avg} the rectified cosine profile generates higher cooling capacities.
-Since the average during the hot cycle (high field stage) is the same, the main difference is due to the low magnetic field levels.
-For the ``same minimum'' comparison, the instantaneous profile is capable of keeping the magnetic field at low levels for the whole half-cycle, which is beneficial for performance;  for $\Phi=1.0$ and $B\ped{h} = \SI{1.40}{\tesla}$, the cooling capacity for the instantaneous profile is $\SI{196.3}{\percent}$ higher than for the cosine profile.
+\textcolor{black}{For} Fig.~\ref{fig:comp_min}, the instantaneous profile almost always yields a higher performance, while for Fig.~\ref{fig:comp_avg} the rectified cosine profile generates higher cooling capacities.
+Since the average \textcolor{black}{field} during the hot cycle (high field stage) is the same, the main difference is due to the low magnetic field levels.
+For the ``same minimum'' comparison, the instantaneous profile is capable of keeping the magnetic field at low levels for the whole half-cycle, which is beneficial for performance;  for $\Phi=1.0$ and $\average{B}\ped{high} = \SI{1.40}{\tesla}$, the cooling capacity for the instantaneous profile is $\SI{196.3}{\percent}$ higher than for the cosine profile.
 As demonstrated by \cite{bib:asme-mce}, a higher average magnetic field during the low-field stage increases the solid temperature and consequently results in  warmer fluid entering the cold heat exchanger, representing a thermal loss.
 In the ``same-average'' comparison, the cosine profile is capable of achieving much lower levels (since its minimum value is fixed), therefore providing more cooling power.
-However, as explained before, it is possible to design near-instantaneous profiles with very low levels of the magnetic field.
+However, as explained before, this \textcolor{black}{analysis serves mainly the purpose of illustrating the influence of low magnetic field variation, by looking at two hypothetical scenarios.
+More} complex \textcolor{black}{magnetic circuit}  geometries \textcolor{black}{are} required to generate the instantaneous magnetic profile \textcolor{black}{with a} low \textcolor{black}{magnetic field} close to 0.
 
@@
   \centering
-%  \subfloat[Same minimum]{\includegraphics[width=8cm]{Qc_B_comp_f_1_same_minimum}\label{fig:comp_min}}
+  \subfloat[Same minimum]{\includegraphics[width=8cm]{Qc_B_comp_f_1_same_minimum}\label{fig:comp_min}}
 \,
@@
   \caption{Cooling capacity as a function of the  average high magnetic field, for different utilizations.
-“I”: instantaneous (blow fraction of \SI{100}{\percent}); “RC”: rectified cosine  (blow fraction of \SI{60}{\percent}), for both comparison methods.}
+\textcolor{black}{``IT''}: instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}), for both comparison methods.}
  \label{fig:cos_ins}
@@
 The only exception in the ``same minimum'' comparison is seen for the lowest utilization of $\Phi = 0.2$, where the performance is slightly better for the RC profile.
-Since the blow fraction for the cosine is lower, the mass flow rate must be higher to yield the same utilization (cf.
-Eq.~\eqref{eq:2}), and this increases heat transfer rate, as previously explained ---  outweighing the effects of the magnetic field.
+Since the blow fraction for the cosine is lower, the mass flow rate \textcolor{black}{is} higher \textcolor{black}{in the latter for} the same utilization (cf.
+Eq.~\eqref{eq:200}).
+\textcolor{black}{This} increases \textcolor{black}{the} heat transfer rate, as previously explained ---  outweighing the effects of the magnetic field.
 
-In general, the performance of the AMRs operating with the instantaneous magnetic profile yields better results.
-As can be seen on Fig.~\ref{fig:cos_ins}, an instantaneous profile with the lowest possible value of $\bmin$ and the highest possible value of $\bmax$, with a flow profile occupying the whole cycle with average values of utilization, results in the highest values of cooling capacity among all simulations, therefore, representing the ideal magnetic profile for an AMR.
+The same analysis, but in terms of the coeficient of performance, is shown in \autoref{fig:cos_ins_cop}.
+For the ``same average'' analysis, the $\cop$ results show the same trends as the cooling capacity.
+However, for the \textcolor{black}{somewhat} more realistic analysis where the minimum of both profiles are the same, the rectified cosine profile yields better results for small values of utilization.
+This is due to \textcolor{black}{a} lower pumping power, as the mass flow rate for the cosine profile is slightly higher, but also flows for a shorter period of time.
+\textcolor{black}{Since} in this region the cooling capacity for the RC profile can be close to or higher than the \textcolor{black}{IT} profile (cf.
+Fig.~\autoref{fig:comp_min}), the coefficient of performance becomes higher for the rectified cosine profile.
 
-\subsection{Analysis of the instantaneous profile}
+\begin{figure}[!ht]
+  \centering
+  \subfloat[Same minimum]{\includegraphics[width=7cm]{COP_B_comp_f_1_same_minimum}\label{fig:comp_min_cop}}
+\,
+%  \subfloat[Same average]{\includegraphics[width=7cm]{COP_B_comp_f_1_same_low_average}\label{fig:comp_avg_cop}}
+\,
+  \caption{Coefficient of performance as a function of the  average high magnetic field, for different utilizations.
+\textcolor{black}{``IT''}: instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}), for both comparison methods.}
+ \label{fig:cos_ins_cop}
+\end{figure}
+
+In general, considering the goal of achieving target requirements for the cooling capacity, AMRs operating with the instantaneous magnetic profile \textcolor{black}{generate} better \textcolor{black}{performance} results.
+As can be seen \textcolor{black}{in} Fig.~\ref{fig:cos_ins}, an instantaneous profile with the lowest possible value of $B\ped{min}$ and the highest possible value of $B\ped{max}$, with a flow profile occupying the whole cycle with average values of utilization, results in the highest values of cooling capacity among all simulations.
+
+The rectified cosine profile, found in compact systems using Halbach arrays, can \textcolor{black}{surely} benefit from reducing the blow fraction, both in terms of cooling capacity and temperature span.
+However, for the typical parameters \textcolor{black}{evaluated} in this Thesis, even if the blow fraction is optimized for the ``RC'' profile, the ``IT'' profile still yields better results.
+
+\subsubsection{Analysis of the instantaneous profile}
 \label{sec:deta-analys-inst}
 
-As shown in the previous section, the instantaneous profile yields the highest values for cooling capacity.
-Therefore, in this section, a more detailed analysis of such profile has been carried out.
-Figure~\ref{fig:qc_phi_inst} shows the cooling capacity as function of utilization, for several levels of the maximum magnetic field for the instantaneous profile, for two different operating frequencies.
-Because of the conflicts between a low heat transfer rate for flow rates too low and a loss in regenerator effectiveness in flow rates too high, there are critical values of utilization that maximize cooling capacity, and this critical value grows with the level of magnetic field.
-With higher magnetic field, the increase in the MCE surpasses the loss of effectiveness, and one can go to higher flow rates without losing performance.
-It can also be seen in Fig.~\ref{fig:qc_phi_inst} that at higher frequencies, the values of cooling power are higher, and also the critical values of utilization are lower; however, this usually is achieved at the cost of higher power consumption in AMR devices at higher frequencies \cite{bib:lei15_study,NIKNIA2016601}.
+As shown in the previous section, the instantaneous profile \textcolor{black}{generally} yields the highest values \textcolor{black}{of} cooling capacity.
+Therefore, in this section, a more detailed analysis of \textcolor{black}{this} profile has been carried out, \textcolor{black}{where the} maximum field in \autoref{fig:cobem-profiles} \textcolor{black}{is} varied, while the minimum value is kept at \SI{0.05}{\tesla}.
+Figure~\ref{fig:qc_phi_inst} shows the cooling capacity as a function of \textcolor{black}{the} utilization, for several levels of the maximum magnetic field \textcolor{black}{and} two different operating frequencies.
+Because of the conflict between a low heat transfer rate for flow rates \textcolor{black}{that are} too low and losses in regenerator effectiveness in flow rates \textcolor{black}{that are} too high, there are critical values of utilization that maximize \textcolor{black}{the} cooling capacity, and this critical values increases with the magnetic field.
+\textcolor{black}{For} higher magnetic fields, the increase in the MCE surpasses the loss of effectiveness, and one can go to higher flow rates without losing performance.
+It can also be seen in Fig.~\ref{fig:qc_phi_inst} that at  higher frequencies the values of cooling power are higher, and also the critical values of utilization are lower; however, this \textcolor{black}{is} usually achieved at the \textcolor{black}{expense} of \textcolor{black}{a} higher power consumption in AMR devices at higher frequencies \cite{bib:lei15_study,NIKNIA2016601}.
 
@@
   \subfloat[$f = \SI{2}{\hertz}$]{\includegraphics[width=8cm]{Qc_Phi_inst_f_2_Hmin_005_FB_100}\label{fig:Qc_phi_inst_2}}
-  \caption{Cooling capacity as a function of utilization, for various values of the high magnetic field  of the instantaneous profile}
+  \caption{Cooling capacity as a function of utilization, for various values of the high magnetic field  \textcolor{black}{for} the instantaneous profile}
   \label{fig:qc_phi_inst}
@@
   \centering
-  \includegraphics[width=8cm]{Qc_H_inst_f_1_Phi_40}
-  \caption{Cooling capacity as a function of  regenerator height (all other parameters from Table~\ref{tab:params} constant) for various values of the high magnetic field of the instantaneous profile}
+  \subfloat[Cooling capacity]{\includegraphics[width=9cm]{Qc_H_inst_f_1_Phi_40}\label{fig:Qc_H_inst_f_1_Phi_40}}
+\quad
+  \subfloat[Coefficient of performance]{\includegraphics[width=9cm]{COP_H_inst_f_1_Phi_40}\label{fig:COP_H_inst_f_1_Phi_40}}
+  \caption{Performance metrics as a function of \textcolor{black}{the} regenerator height (all other parameters \textcolor{black}{were set as in} Table~\ref{tab:params-cobem}, \textcolor{black}{for}  utilization factor of 0.4) for various values of the high magnetic field of the instantaneous profile}
 \label{fig:Qc_H_inst}
@@
 
-The parameters in Table~\ref{tab:params} were chosen from preliminary simulations, but they are not guaranteed to be the optimal choices.
-To understand the impact of regenerator geometry on the performance with the instantaneous profile, the regenerator height was varied in Fig.~\ref{fig:Qc_H_inst}, and all other parameters from Table.~\ref{tab:params} were kept fixed.
-As expected, higher magnetic fields allow for smaller regenerators (and hence more compact systems).
-For instance, to achieve a capacity of \SI{100}{\watt}, increasing the field from \num{1.0} to \SI{1.2}{\tesla} result in using regenerators \SI{36}{\percent} smaller.
-
-\section{CONCLUSIONS}
-\label{sec:conclusions}
-
-A one-dimensional AMR numerical model was used to compare the performance of a magnetic refrigerator under different operating and geometric parameters and with the instantaneous and rectified cosine magnetic profiles.
-Most of the AMRs operating with an instantaneous magnetic profile have resulted in better performances than those with a cosine profile, except in cases of low utilization.
-Although the cosine profile reaches higher levels of the magnetic field, the instantaneous profile can keep the magnetization (and demagnetization) for a longer period, which is shown to be beneficial to performance.
-Further analysis of the instantaneous profile has shown that the use of the highest possible value of the maximum magnetic field allows for using smaller regenerators and lower utilization, without losing performance.
+The parameters in \autoref{tab:params-cobem} were chosen from preliminary simulations, \textcolor{black}{so} they are not  optimal.
+To understand the impact of \textcolor{black}{the} regenerator geometry on the performance with the instantaneous profile, the regenerator height was varied in Fig.~\ref{fig:Qc_H_inst}, and all other parameters from \autoref{tab:params-cobem} were kept fixed and with $\phi=0.4$.
+As expected, higher magnetic fields allow for smaller regenerators (hence more compact systems) to achieve a \textcolor{black}{desired} cooling capacity.
+For instance, to achieve a capacity of \SI{100}{\watt}, increasing the field from \num{1.0} to \SI{1.2}{\tesla} \textcolor{black}{results} in regenerators \textcolor{black}{that are} \SI{36}{\percent} smaller.
+Comparing results \textcolor{black}{for} cooling capacity and coefficient of performance, the trends are largely the same, as the former is more sensitive to variations in the magnetic field and regenerator height than the components of power.
 

### 2019-09-11 PaperMagneticProfiles_JBSMSE.tex
Include section on ramp profile analysis.

@@
 \usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
 \usepackage{nicefrac}
@@
 
+\subsection{In-depth analysis of the  magnetic \textcolor{black}{ramp} profile}
+\label{sec:performance-an-amr-1}
+
+Based on the better performance of the instantaneous profile, the ramp profile is assumed as a suitable target profile for the design of magnetic refrigerators, and will be analyzed in this section.
+
+Moving towards a more realistic model, casing losses are included, using the model from \cite{bib:trevizoli16_perfor_model}.
+The bed is enclosed in a solid casing of thickness $h\ped{csg}$, and two air layers of thickness $h\ped{air}$ separate \textcolor{black}{the AMR and its casing} from the inner and outer \textcolor{black}{magnet} cylinders.
+
+\begin{figure}[!ht]
+  \centering
+  \includegraphics[width=7cm]{amr-casing}
+  \caption{Model for the casing losses in regenerators}
+  \label{fig:amr-casing}
+\end{figure}
+
+\nomenclature[ia]{air}{air layer between magnets and regenerators}
+\nomenclature[ic]{csg}{regenerator casing}
+
+Preliminary analyses \textcolor{black}{carried out by} \cite{bib:peixer17-perfor-amrs} using the losses model described in \autoref{sec:model-casing-loss} showed that a stainless steel casing \textcolor{black}{with a} thickness \textcolor{black}{of} $h\ped{csg} = \SI{0.5}{\mm}$ is thick enough to ensure mechanical integrity and easy manufacturing, while being thin enough to accommodate the material \textcolor{black}{with a low} thermal conductivity.
+
+In addition, \textcolor{black}{in the present study}, an air gap clearance thickness was set at $h\ped{air} = \SI{1}{\mm}$.
+This value \textcolor{black}{gave rise to a} peak in cooling capacity due to the compromise between minimizing losses and maximizing the magnetocaloric mass.
+
+The simulations in this section also use multilayer regenerators.
+A summary of all parameters adopted in this section, including the Curie temperatures and volumetric fractions (relative to the length of the bed) of each layer is presented in \autoref{tab:params-ramp}.
+
+\begin{table}[!ht]
+  \centering
+  \begin{tabular}{c|c}
+\hline
+    \textbf{Parameter} & \textbf{Value} \\
+\hline
+$R\ped{o}$ & \SI{40}{\mm} \\
+$W\ped{r}$ & \SI{30}{\mm} \\
+$L\ped{r}$ & \SI{85}{\mm} \\
+$N\ped{r}$ & \num{8} \\
+$N\ped{v}$ & \num{16} \\
+$f$ & \SI{1}{\hertz} \\
+$\th$ & \SI{305.5}{\kelvin} = \SI{32.5}{\celsius} \\
+$\tc$ & \SI{270.5}{\kelvin} = \SI{-2.5}{\celsius} \\
+$D\ped{p}$ & \SI{350}{\micro\meter} \\
+$h\ped{csg}$ & \SI{0.5}{\mm} \\
+$h\ped{air}$ & \SI{1}{\mm} \\
+Casing material & Stainless steel \\
+Number of layers & \num{3} \\
+Curie temperatures of each layer & \num{273}, \num{283}, \SI{290}{\kelvin} \\ 
+Length fractions of each layer & \num{20}, \num{20}, \SI{60}{\percent}\\
+\hline
+  \end{tabular}
+  \caption{Fixed parameters for the AMR simulations used in this chapter}
+  \label{tab:params-ramp}
+\end{table}
+
+\subsubsection{Synchronization between \textcolor{black}{the} fluid flow and magnetic profiles}
+\label{sec:synchr-betw-fluid}
+
+A central point of this Thesis is \textcolor{black}{related to} the importance of two characteristic waveforms, the fluid flow and magnetic profiles, \textcolor{black}{and how they affect} the performance of a magnetic refrigerator.
+Several works have independently investigated the synchronization between these profiles \cite{bib:bjoerk11_amr,bib:nakashima17-exper}.
+Here, \textcolor{black}{the} focus is  on the parameterization of these waveforms and \textcolor{black}{the} characerization of an AMR system with these parameters, in particular the blow fraction (cf.
+\autoref{sec:inst-fluid-flow}) and the magnetization fraction (cf.
+\autoref{sec:ramp-magn-prof}).
+Figure~\ref{fig:ramp-inst} shows the two profiles that will be used in this section.
+
+\begin{figure}[!ht]
+  \centering
+  \includegraphics[width=7cm]{profiles_rm_and_flow_instantaneous}
+  \caption{Comparison between the magnetic \textcolor{black}{ramp} profile (solid line) and the instantaneous fluid flow profile (dashed line)}
+  \label{fig:ramp-inst}
+\end{figure}
+
+Regarding the magnetic profile, the \textcolor{black}{magnitude of the} high value will be varied to investigate the performance of the AMR system, while the minimum will be kept at $\bmin = \SI{0.05}{\tesla}$.
+Ideally, this value \textcolor{black}{should be nil}, but it is \textcolor{black}{difficult} to achieve complete flux insulation in the low field region, so \textcolor{black}{a finite value of the} minimum field is \textcolor{black}{adopted}.
+
+\subsubsection{Performance curves for varying blow and magnetization fractions}
+\label{sec:perf-curv-vary}
+
+Figure~\ref{fig:Qc_COP_curves_phi40} shows the cooling capacity and coefficient of performance of the AMR system for a fixed utilization factor of \num{0.4} and for a magnetic profile with \textcolor{black}{a} maximum at \SI{1.3}{\tesla}, for \textcolor{black}{variable} blow and magnetization fractions.
+\textcolor{black}{To facilitate the analysis, the} results are plotted in terms of the ratio $\nicefrac{F\ped{M}}{F\ped{B}}$, with curves for different \textcolor{black}{values of} $F\ped{B}$.
+It is clear \textcolor{black}{that both the cooling capacity and the coefficient of performance exhibit a peak at} $F\ped{M} = F\ped{B}$.
+Moreover,  \textcolor{black}{to the right of the peak, i.e., for higher values of $F\ped{M}$, the}  reduction \textcolor{black}{of} both \textcolor{black}{performance} metrics \textcolor{black}{is} slower, meaning it is better to have a magnetization plateau wider than the fluid flow plateau, thus confirming the conclusions \textcolor{black}{of} \autoref{cha:exper-invest-fluid}.
+
+The reduction in performance for $F\ped{M} > F\ped{B}$ \textcolor{black}{can be explained by an increase in} heat leakage through the casing, as the solid begins to lose energy to the environment \textcolor{black}{when} the fluid is not flowing.
+For $F\ped{M} < F\ped{B}$, the effect \textcolor{black}{discussed in} \autoref{sec:results-discussions} is present: the fluid begins to flow when the solid is not totally warmed up, losing effectiveness.
+
+\begin{figure}[!ht]
+  \centering
+  \subfloat[Cooling capacity]{\includegraphics[width=5cm]{Qc_FM_ramp_f_1_Phi_40_35K_1300mT}\label{fig:Qc_FM_ramp_f_1_Phi_40_35K_1.3T}}
+\quad
+ \subfloat[Coefficient of performance]{\includegraphics[width=5cm]{COP_FM_ramp_f_1_Phi_40_35K_1300mT}\label{fig:COP_FM_ramp_f_1_Phi_40_35K_1.3T}}
+  \caption{Performance of the AMR system for various blow and magnetization fractions, utilization of 0.4 and and high magnetic field of \SI{1.3}{\tesla}}
+  \label{fig:Qc_COP_curves_phi40}
+\end{figure}
+
+The influence of \textcolor{black}{the} utilization is demonstrated in \autoref{fig:Qc_curves_ramp_phi}, where the cooling capacity \textcolor{black}{is} plotted for different utilization factors.
+For increasing $\Phi$ in this range, not only do the overall values of cooling capacity increase, but also the importance of choosing the blow fraction becomes clearer.
+In \textcolor{black}{these ranges} of utilization and blow fraction,  the cooling capacity increases because the higher transfer rate associated with higher flow rates \textcolor{black}{dominates} over the loss of regenerator effectiveness.
+
+\begin{figure}[!ht]
+  \centering
+  \subfloat[$\Phi = \num{0.2}$]{\includegraphics[width=5cm]{Qc_FM_ramp_f_1_Phi_20_35K_1300mT}\label{fig:Qc_FM_ramp_f_1_Phi_20_35K_1.3T}}
+\quad
+ \subfloat[$\Phi = \num{
+0.5}$]{\includegraphics[width=5cm]{Qc_FM_ramp_f_1_Phi_50_35K_1300mT}\label{fig:COP_FM_ramp_f_1_Phi_50_35K_1.3T}}
+  \caption{Influence of utilization on the cooling capacity of the AMR system for  various blow and magnetization fractions, with high magnetic field of \SI{1.3}{\tesla}}
+  \label{fig:Qc_curves_ramp_phi}
+\end{figure}
+
+The \textcolor{black}{above} results can be \textcolor{black}{evaluated from} another point of view with \autoref{fig:COP_maps_ramp_FM}, where the coefficient of performance is plotted as contour levels.
+This type of map is useful because, since $\bmin$ and $\tau$ are fixed, each point in this graph completely characterizes a magnetic \textcolor{black}{ramp} profile, and each subplot with fixed $\Phi$ and $F\ped{B}$ characterizes the fluid flow profile.
+As expected, the performance increases for the higher values both $\bmax$ and $F\ped{M}$, where the  magnetic \textcolor{black}{ramp} profile tends to the instantaneous magnetic profile with a large amplitude.
+Confirming the previous trends, the results are less sensitive to the magnetization fraction when $F\ped{M} \ge F\ped{B}$.
+
+\begin{figure}[!ht]
+  \centering
+  \subfloat[$\Phi = 0.2, F\ped{B} = \SI{60}{\percent}$]{\includegraphics[width=5cm]{COP_ramp_map_f_1_Phi_20_FB_60_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_20_FB_70_35K_Valv_ASCO}}
+\quad
+ \subfloat[$\Phi= 0.2, F\ped{B} = \SI{90}{\percent}$]{\includegraphics[width=5cm]{COP_ramp_map_f_1_Phi_20_FB_90_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_20_FB_90_35K_Valv_ASCO}} \\
+  \subfloat[$\Phi = 0.4, F\ped{B} = \SI{60}{\percent}$]{\includegraphics[width=5cm]{COP_ramp_map_f_1_Phi_40_FB_60_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_60_FB_90_35K_Valv_ASCO}}
+\quad
+ \subfloat[$\Phi = 0.4, F\ped{B} = \SI{90}{\percent}$]{\includegraphics[width=5cm]{COP_ramp_map_f_1_Phi_40_FB_90_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_40_FB_90_35K_Valv_ASCO}}
+  \caption{Influence of utilization and blow fraction on the coefficient of performance of the AMR system for varying high magnetic field and magnetization fraction}
+  \label{fig:COP_maps_ramp_FM}
+\end{figure}
+
+\subsubsection{Geometric analysis of the regenerators using the ramp magnetic profile}
+\label{sec:geom-analys-regen}
+
+\textcolor{black}{All} previous results assumed a fixed regenerator geometry, with the goal of identifying the optimal fluid and magnetic profile parameters.
+\textcolor{black}{It became clear that the} magnetization fraction should be as large as possible, but that makes it more difficult to design a magnetic circuit \textcolor{black}{based on} permanent magnets.
+The value of $F\ped{M} = \SI{70}{\percent}$ is then chosen as a compromise, with \textcolor{black}{a corresponding} $F\ped{B} = F\ped{M}$.
+The mean value of \textcolor{black}{the} utilization factor of $\Phi = 0.4$ is also chosen as reference in the next results.
+
+In this section, the \textcolor{black}{effect of the} regenerator height is \textcolor{black}{evaluated.
+The results will complement those for the} air gap height that will be shown in \autoref{cha:design-optim-magn} concerning the design of the magnetic circuit.
+The importance of the air gap height as a coupling \textcolor{black}{parameter} between the geometric design of the regenerators and the magnetic circuit was explored using a simplified model in \autoref{sec:performance-an-amr} and using the instantaneous magnetic profile in \autoref{sec:deta-analys-inst}.
+The results \textcolor{black}{to be} shown \textcolor{black}{here} use the magnetic \textcolor{black}{ramp} profile \textcolor{black}{studied in depth in} this present chapter.
+
+Figure~\ref{fig:qc-cop-eta-amr-height} shows the cooling capacity, coefficient of performance and second-law efficiency for varying magnetic field and regenerator height.
+\textcolor{black}{As} expected, larger regenerators can \textcolor{black}{produce} the desired performance with lower magnetic fields.
+It can also be seen that this configuration for an AMR system can achieve values of $\etasec$ compatible with conventional vapor compression systems \cite{HERMES20081341,NEGRAO20113051}, although these numerical results do not include mechanical losses.
+
+\begin{figure}[!ht]
+  \centering
+\subfloat[Cooling capacity (solid lines) and coefficient of performance (dashed lines)]{  \includegraphics[width=5cm]{Qc_COP_combined_H_regW30}\label{fig:Qc_COP_Hreg}}
+\,
+\subfloat[Second-law efficiency]{\includegraphics[width=5cm]{eta_H_regW30}\label{fig:eta_Hreg}}
+  \caption{Performance of the AMR with varying regenerator height and high magnetic field, with fixed $F\ped{M} = F\ped{B} = \SI{70}{\percent}$ and $\Phi = 0.4$}
+  \label{fig:qc-cop-eta-amr-height}
+\end{figure}
+
 \begin{acknowledgements}

### 2019-09-11 PaperMagneticProfiles_JBSMSE.tex
Add first draft of conclusions.

@@
 
+\section{Final considerations}
+\label{sec:final-considerations}
+
+To the authors' knowledge, this is the first study where magnetic profiles for AMR model are mathematically modeled and the model parameters are changed in a systematic way.
+
+The instantaneous profile yields higher cooling capacity, even by
+reducing the blow fraction on rectified cosine, up to levels achieved by pumping and valving systems, mainly restricted by valve opening times
+
+The ramp profile is a feasible approximation for the instantaneous
+profile, and can be optimized for increasing cooling capacity.
+In particular, by synchronizing the plateau durations between fluid
+and magnetic profiles.
+
 \begin{acknowledgements}

### 2019-09-17 PaperMagneticProfiles_JBSMSE.tex
Add acknowledgements.
Compile manuscript to referee mode (bigger spacing and pictures).
Improve author's affiliations and addresses

@@
-% LaTeX .tex example for the proceedings of
-% COBEM 2017 - 24th International Congress of Mechanical Engineering
-% December, 3-8, 2017, Curitiba, PR, Brazil
-%
-% Based on the template of the proceedings of COBEM2015 
-% MODELO COBEM 2017
-
-\documentclass[draft]{svjour3}
+\documentclass[referee]{svjour3}
 
@@
 \institute{
-Fábio P. Fortkamp 
-\at
-POLO --- Research Laboratories for Emerging Technologies in Cooling and Thermophysics, Department of Mechanical Engineering, Federal University of Santa Catarina, Florianópolis, SC, 88040-900, Brazil, \email{fabio@polo.ufsc.br}
-\and
+Fábio P. Fortkamp \\
+\email{fabio@polo.ufsc.br} \\
 Gusttav B. Lang \and
 Jaime A. Lozano \and
-Jader R.
-Barbosa Jr.
-\at POLO --- Research Laboratories for Emerging Technologies in Cooling and Thermophysics, Department of Mechanical Engineering, Federal University of Santa Catarina, Florianópolis, SC, 88040-900, Brazil}
+Jader R. Barbosa Jr.
+\at
+POLO --- Research Laboratories for Emerging Technologies in Cooling and Thermophysics, Department of Mechanical Engineering, Federal University of Santa Catarina, Florianópolis, SC, 88040-900, Brazil}
 
@@
 \begin{acknowledgements}
-This work was supported by CNPq, Embraco and EMBRAPII Unit Polo/UFSC.  
+The authors duly acknowledge the financial support from CNPq (Grant no. 443696/2014-4), Capes (PTI program, Process no. 88887.194773/2018-00), Embraco and the EMBRAPII Unit Polo/UFSC.
 \end{acknowledgements}

### 2019-09-17 PaperMagneticProfiles_JBSMSE.tex
Create running title.
Draft abstract.

@@
 
+\titlerunning{Analysis of magnetic field waveforms}
 \maketitle
@@
 \begin{abstract}
+Magnetic cooling is an alternative to vapor compression with no use of hazarduous gases.
+The refrigerant is a solid material which reacts to oscillations in magnetic field with changes in temperature.
+In active magnetic regenerators, this magnetocaloric material and its effect are coupled with an oscillating fluid flow to yield a thermodynamic cooling cycle between cold and hot source temperatures.
+The literature is abundant with studies on the influence of the fluid flow waveform on magnetic refrigeration devices, but the influence of the magnetic field waveform is less investigated.
+In this work, we simulate a previously developed active magnetic regenerator numerical model with different mathematically-defined waveforms, and determine which operating parameters yield the highest values for cooling capacity and coefficient of performance.
+Results show that the highests performance levels are achieved when the magnetic field is kept constant for the same duration of the fluid flow through the magnetized material, and that the transition times between high and low levels of the magnetic field should be as fast as possible.
 

### 2019-09-17 PaperMagneticProfiles_JBSMSE.tex
Edit introduction.
Several paragraphs were cut for brevity.

@@
 Mechanical vapor compression has been the dominant cooling technology for the past century \cite{bib:nik} but, despite its dominance, it still faces an increasing number of challenges related to the its environmental footprint.
-The large entropy generation associated with vapor compression processes makes this techonology constrained by low exergy efficiencies, in particular for compact systems \cite{KITANOVSKI2015288}.
-In addition, the phase-out of refrigerants \textcolor{black}{with} ozone depleting \textcolor{black}{and global warming potentials has} introduced the use of flammable substances, with their own set of risks for consumer applications \cite{bib:iir-flammable} and technologial challenges \cite{bib:lionte18-adapt}.
+In particular, the phase-out of refrigerants \textcolor{black}{with} ozone depleting \textcolor{black}{and global warming potentials has} introduced the use of flammable substances, with their own set of risks for consumer applications \cite{bib:iir-flammable} and technological challenges \cite{bib:lionte18-adapt}.
 
-The term \emph{caloric cooling} is \textcolor{black}{generally} applied to alternative cooling techonologies in which the cooling effect is generated by the response of a solid material to a physical \textcolor{black}{stimulus}.
-The absence of hazardous gases, compressors \textcolor{black}{and throttling devices} makes these technologies potentially more efficient, \textcolor{black}{scalable}, silent and environmentally friendly.
-Magnetic refrigeration (MR) is the most advanced of all caloric technologies \cite{KITANOVSKI2015288}; in particular, with the classes of magnetic refrigerants currently available, magnetocaloric refrigeration seems promising for applications in small temperature span (around \SI{20}{\kelvin}), such as winecoolers \textcolor{black}{and air conditioners} \cite{KITANOVSKI2015288}.
+Magnetic refrigeration (MR) is an advanced cooling technology with no use of hazarduous gases, where a \emph{magnetocaloric material} (MCM) \textcolor{black}{is subjected to a cyclical change of the applied} magnetic field, and its temperature \textcolor{black}{changes as a result} of the \emph{magnetocaloric effect} (MCE).
+The magnitude of the MCE  \textcolor{black}{depends} on  material parameters, magnetic field variation and temperature, and its maximal at the Curie temperature of the material.
+For a thorough introduction to the magnetocaloric effect and magnetocaloric materials, the reader is referred to \cite{bib:smith-magneto}.
 
 \nomenclature[vm]{MR}{Magnetic (or Magnetocaloric) Refrigeration}
-
-In magnetic refrigeration, a \emph{magnetocaloric material} (MCM) \textcolor{black}{is subjected to a cyclical change of the applied} magnetic field, and its temperature \textcolor{black}{changes as a result} of the \emph{magnetocaloric effect} (MCE).
-The magnitude of the MCE  \textcolor{black}{depends} on  parameters \textcolor{black}{related to} characteristics of the material, magnetic field variation and temperature, and its maximal at the transition Curie temperature of the material.
-For a thorough introduction to the magnetocaloric effect and magnetocaloric materials, the reader is referred to \cite{bib:smith-magneto}.
-
 \nomenclature[vm]{MCM}{Magnetocaloric Material}
+\nomenclature[vm]{MCE}{Magnetocaloric Effect}
 
@@
 \textcolor{black}{T}o amplify this \textcolor{black}{temperature change}, heat regeneration is usually employed \cite{bib:kitanovski}.
-Active magnetic regenerators (AMR) are thermal devices where the magnetocaloric material constitutes a solid matrix through which flows an aqueous heat transfer fluid, and is cyclically magnetized and demagnetized to activate the magnetocaloric effect.
-\textcolor{black}{A regenerator is essentially a cascade of infinitesimal ``layers'' of MCM that are activated simultaneously} to build up a temperature profile \textcolor{black}{along its length}.
+Active magnetic regenerators (AMR) are thermal devices where the magnetocaloric material constitutes a solid matrix through which flows an aqueous heat transfer fluid, and which is cyclically magnetized and demagnetized to activate the magnetocaloric effect.
+\textcolor{black}{Such a regenerator is essentially a cascade of infinitesimal ``layers'' of MCM that are activated simultaneously} to build up a temperature profile \textcolor{black}{along its length}.
 These layers can be made of the same material, yielding an homogeneous regenerator; however, given the  dependence  of the MCE with temperature, it is an interesting strategy to build \emph{multilayer} regenerators, where each layer is composed of a different material \textcolor{black}{that} will work around its \textcolor{black}{own} Curie temperature, maximizing the magnetocaloric effect of each portion.
@@
 \nomenclature[vm]{AMR}{Active Magnetic Regenerator}
-
-The five main subsystems in an AMR-based magnetic refrigerator can be identified as follows \cite{bib:jaime,bib:trevizoli16_pump}:
-
-\begin{enumerate}
-\item magnetic circuit; \label{item:1}
-\item active magnetic regenerator; \label{item:2}
-\item flow management system; \label{item:3}
-\item control system; \label{item:4}
-\item transmission system; \label{item:5}
-\item heat exchangers and cabinet. \label{item:6a}
-\end{enumerate}
-
-The magnetic circuit generates oscillating magnetic fields that activate the MCE \textcolor{black}{in} the active magnetic regenerators.
-As previously explained, the regenerators are composed of magnetocaloric porous media, and the flow management system provides the alternating fluid flow through the beds.
-The control system \textcolor{black}{serves} the purpose of synchronizing the fluid flow regime with the magnetic field variations.
-Finally, the heat exchangers are responsible for transferring the cooling effect from the AMR to the refrigerated cabinet and the rejected heat to the surroundings.
 
@@
 
-Among the challenges cited in the literature for further improvement of magnetic refrigerators, two can be highlighted \cite{bib:eriksen16_activ}:
-
-\begin{enumerate}
-\item Better use of AMR and magnetic circuit models during the design process, to identify optimal geometric and operating parameter;
-\item Better study of losses that are present in a magnetic cooling device.
-\end{enumerate}
-
-\textcolor{black}{In} other words, these challenges arise due to \emph{interactions} between different subsystems \textcolor{black}of a magnetic refrigerator.
-In these context, the focus on the aforementioned waveforms is a suitable approach for optimizing the performance of magnetic refrigerators, as these profiles represent interactions between systems.
-As it will be seen, mathematical models for AMRs take these waveforms as input, and they are generated by models for other components.
-
 Fluid flow profiles are more easily investigated with experimental methods, since they can be altered with modifications in the fluid flow system.
@@
 In this work, we focus on magnetic profiles, which are less studied in the literature.
-The studied waveforms are depicted in \autoref{fig:profiles}, identified by the transitions between states.
-The instantaneous profile represents step-like changes between high and low levels of the magnetic field, while the ramp profile has linear variations between these states.
-The rectified cosine profile is a common waveform found in the literature that has a continuous variation of the applied magnetic field.
-
-\begin{figure}[!ht]
-  \centering
-  \includegraphics[width=8cm]{profiles_all}
-  \caption{Magnetic profiles studied in this paper}
-  \label{fig:profiles}
-\end{figure}
-
-The instantaneous magnetic profile is characteristic of the Brayton AMR cycle, where the magnetization and demagnetization steps must be done adiabatically, as shown in \autoref{fig:brayton}; compared to other common cycles such as the Ericsson, the Brayton cycle results in the highest cooling capacities for the same operating  parameters \cite{bib:kitanovski}, at the expense of lower coefficient of performance.
-
-\begin{figure}[!ht]
-  \centering
-
-  \caption{Brayton AMR cycle}
-  \label{fig:brayton}
-\end{figure}
-
- In practice, the ramp profile is a more feasible realization with finite transition times, and its synchronization with the fluid flow profile can yield different performance levels \cite{TUSEK20111507}.
-In particular, the plateaus of magnetic field should be centered with the blow durations \cite{bib:bjoerk11_amr}.
-\autoref{fig:sync} shows the syncronization schema between the magnetic and fluid flow profiles, showing the ramp magnetic profile as an example.
-
-\begin{figure}[!ht]
-  \centering
-  \includegraphics[width=8cm]{profiles_rm_and_flow_instantaneous}
-  \caption{Ramp magnetic profile (solid lines) and instantaneous fluid flow profile (dashed lines)}
-  \label{fig:sync}
-\end{figure}
-
+These waveforms are usually investigated in terms of their synchronization with the fluid flow profile \cite{TUSEK20111507,bib:bjoerk11_amr}.
 This paper uses the AMR model developed by \cite{bib:trevizoli16_perfor_model}, and the same authors had studied magnetic profiles waveforms in an earlier work \cite{bib:asme-mce}.
@@
 
-The present works combines the gaps from the above cited papers in investigating the performance of a magnetic refrigerator under different magnetic profile waveforms.
+The present work combines the gaps from the above cited papers in investigating the performance of a magnetic refrigerator under different magnetic profile waveforms.
 These waveforms are mathematically modeled, and the cooling capacity and coefficient of performance are calculated based on the profiles parameters, while also investigated how the AMR geometry affect the performance in combinations with the magnetic profile.
-The fluid flow profile is assumed fixed in shape, although its parameters are also variied.
-The emulate constraints on an operating point of actual magnetic refrigeration devices, the temperature span is set fixed, and hence few comments are made on second-law efficiency.
+The fluid flow profile is assumed fixed in shape, although its parameters are also varied.
+To emulate constraints on an operating point of actual magnetic refrigeration devices, the temperature span is set fixed, and hence few comments are made on second-law efficiency.
 

### 2019-09-17 PaperMagneticProfiles_JBSMSE.tex
Create list of symbols.
Edit AMR model section.
The main edit was to combine explanations on the
magnetic and fluid profiles into a more cohesive section.

@@
 \usepackage{hyperref}
+
+\makenomenclature
+
+\renewcommand{\nomgroup}[1]{%
+\ifthenelse{\equal{#1}{A}}%
+    {\item[\textbf{Variables}]}%
+{\ifthenelse{\equal{#1}{B}}%
+{\item[\textbf{Greek symbols}]}%
+    {\ifthenelse{\equal{#1}{I}}%
+        {\item[\textbf{Subscripts and Superscripts}]}%
+        {\ifthenelse{\equal{#1}{V}}%
+            {\item[\textbf{Abbreviations}]}%
+                {}%
+        }
+    }
+}}
+
+% \nomenclature[a ]{}{...} produces a regular symbol
+% \nomenclature[b ]{}{...} produces a greek symbol
+% \nomenclature[i ]{}{...} produces a subscript
+% \nomenclature[v ]{}{...} produces an abbreviation
+% The letter after a,i, v or c can control the ordering (e.g. for placing greek letter at the end
+\renewcommand{\nomname}{List of symbols}%
 
@@
 \end{abstract}
+
+\printnomenclature
 
@@
 
-In this work, we perform numerical simulations of a previously developed AMR model, varying the profile and geometric parameters.
-We also couple a model for calculating  the power comsumption of a proposed valve system, a topic understudied in the literature.
-With this, we can evaluate the influence of the profile on cooling capacity and coefficient of performance.
+As previuosly explained, we perform numerical simulations of a previously developed AMR model, varying the profile-specific and geometric parameters.
+We also couple a model for calculating  the power comsumption of a proposed fluid management system, a topic understudied in the literature.
+The output of this integrated model are cooling capacity, power contributions and the coefficient of performance (COP).
+
+\nomenclature[ac]{COP}{coefficient of performance}
 
@@
 
-Simulations were performed using a one-dimensional AMR mathematical model \cite{bib:asme-mce,bib:trevizoli16_perfor_model}.
+Simulations were performed using a one-dimensional AMR mathematical model, implemented using the Finite Volumes Method \cite{bib:trevizoli16_perfor_model}.
 Here we will show a summarized version focusing on the governing equations.
-This model solves momentum and energy balance equations for the solid and fluid phases, represented by indices 's' and 'f', respectively.
+This model solves momentum and energy balance equations for the solid and fluid phases, represented by indices `s' and `f', respectively.
 The model geometry is depicted in \autoref{fig:amrmodel}, and assumes regenerators composed of monodisperse packed spheres with porosity $\varepsilon$.
@@
 \nomenclature[ac]{$c\ped{E}$}{Ergun constant of the porous medium}
-\nomenclature[ar]{$\rho$}{density [\si{\kg\per\cubic\meter}]}
+\nomenclature[br]{$\rho$}{density [\si{\kg\per\cubic\meter}]}
 \nomenclature[be]{$\varepsilon$}{porosity}
@@
 
-\noindent and is solved for the time-dependent uniform fluid velocity through the bed.
+\noindent and is solved for the time-dependent uniform fluid velocity $V_z$ through the bed.
 
@@
   \rho\ped{f} c_{p,\mathrm{f}} \left(\varepsilon \diffp{T\ped{f}}{t} + V_z\diffp{T\ped{f}}{z}\right) = & -\hheat\ped{sf} \beta \left(T\ped{f} - T\ped{s}\right) \\
-& + \left|V_z\diffp{p}{z}\bigg|_f \right| \\
+& + \left|V_z\diffp{P}{z}\bigg|_f \right| \\
 & + \varepsilon\left(k\ped{f}\ap{eff}  +\rho\ped{f} c_{p,\mathrm{f}} D\ped{ld}\right)\diffp[2]{T\ped{f}}{z} \\
@@
 \nomenclature[is]{sf}{relative to the heat transfer between solid and fluid phases in the regenerator}
-\nomenclature[azb]{$\beta$}{surface area density [\si{\squared\meter\per\cubic\meter}]}
+\nomenclature[bb]{$\beta$}{surface area density [\si{\squared\meter\per\cubic\meter}]}
 \nomenclature[ak]{$k\ap{eff}$}{effective thermal conductivity [\si{\watt\per\meter\per\kelvin}]}
@@
 \nomenclature[af]{$f$}{cycle frequency [\si{\hertz}]}
-\nomenclature[azf]{$\Phi$}{utilization}
+\nomenclature[bf]{$\Phi$}{utilization}
 \nomenclature[am]{$m$}{mass [\si{\kg}]}
 
-\nomenclature[azt]{$\tau$}{time period [\si{\second}]}
+\nomenclature[bt]{$\tau$}{time period [\si{\second}]}
 \nomenclature[ac]{$c$}{specific heat [\si{\joule\per\kg\per\kelvin}]}
@@
 Initial and boundary conditions, solution methods, convergence analyses, and closure relations for the porous media terms are described in \cite{bib:trevizoli16_perfor_model}.
-This AMR model solves the above equations for one regenerator operating between given sources temperatures, during one full cycle (hot and cold blows and  magnetization and demagnetization periods), given specified operating conditions (to be discussed later).
+This AMR model solves the above equations for one regenerator operating between given sources temperatures (assuming ideal heat exchangers in contact with the thermal reservoirs), during one full cycle (hot and cold blows and  magnetization and demagnetization periods), given specified operating conditions (to be discussed later).
 
@@
 
-The pressure gradient in \autoref{eq:75}is modeled as:
+The pressure gradient in \autoref{eq:75} is modeled as:
 
@@
 \nomenclature[aA]{$A\ped{t}$}{amplitude of the pressure gradient waveform in the fluid momentum equation [\si{\meter\per\second\square}]}
-
-\subsubsection{How the magnetic profile is used}
-\label{sec:how-magnetic-profile}
-
-The magnetic profile is modeled by a waveform of magnetic field strength $H$ applied perpendicular to the regenerators, as shown in \autoref{fig:amrmodel}.
-The magnetic field is assumed uniform throughout the beds.
-The applied field is corrected from demagnetization effects to yield the effective field inside the regenerators:
-
-\begin{equation}
-  \label{eq:6}
-  H\ap{eff} = H - N\ped{D} M
-\end{equation}
-
-\nomenclature[am]{$M$}{magnetization field [\si{\ampere\per\meter}]}
-\nomenclature[an]{$N\ped{D}$}{demagnetization tensor}
-
-\noindent where $M$ is the magnetization field of the material, and $N\ped{D}$ is a demagnetization factor.
-
-The magnetocaloric effect is implemented in the so-called discrete approach \cite{bib:nielsen11_review}; every time the magnetic field changes, based on the input magnetic profile, the solid temperature is calculated according to:
-
-\begin{equation}
-  \label{eq:89}
-  T\ped{s}(t + \Delta{}t) = T\ped{s}(t) + \dtad \left(T\ped{s}(t),H\ap{eff}(t),H\ap{eff}\left(t + \Delta{}t\right)\right)
-\end{equation}
-
-\nomenclature[ct]{$\dtad$}{adiabatic temperature variation [\si{\kelvin}]}
-
-\noindent where the adiabatic temperature variation $\dtad$ is calculated from \textcolor{black}{tabulated} experimental \textcolor{black}{data} for magnetocaloric materials as function of temperature and effective field.
-\cite{bib:trevizoli16_perfor_model}.
-
-\subsubsection{Evaluation of solid and fluid properties}
-\label{sec:eval-solid-fluid}
-
-The fluid properties are considered constant in the momentum equation to decouple the solution \textcolor{black}{procedures to determine} the velocity and temperature fields.
-The properties are computed at the average temperature between the hot and cold sources temperatures, and are evaluated from interpolated tables exported from the EES software \cite{bib:klein13-ees}.
-In all simulations shown in this work, the heat transfer fluid is a mixture of water/ethylene-glycol with concentration \num{80}/\SI{20}{\percent} vol.
-For the energy equations, the fluid properties are also calculated from tabulated data, but the temperature dependence is considered.
-
-n this chapter, all simulations use gadolinium or its allows as the magnetocaloric material.
-Gadolinium is a benchmark material with a Curie temperature of \SI{290}{\kelvin}.
-\textcolor{black}{For simplicity, the solid} density is assumed constant at $\rho\ped{s} = \SI{7900}{\kg\per\cubic\meter}$ and the solid \textcolor{black}{thermal} conductivity is set to $k\ped{s} = \SI{10.5}{\watt\per\meter\per\kelvin}$.
-The specific heat \textcolor{black}{capacity} of \ce{Gd} is calculated as a function of temperature and magnetic field based on experimental \textcolor{black}{data}, using a bi-linear interpolation scheme; more details on the experimental dataset \textcolor{black}{are available} in \cite{bib:trevizoli16_perfor_model}.
-
-In this work, both single- and multilayer regenerators are considered.
-For the multilayer simulations, alloys of gadolinium and yttrium are used in the form \ce{Gd_{1-x}Y_x}, where $x$ is the yttrium fraction.
-\textcolor{black}{This fraction} decreases the Curie temperature  \textcolor{black}{of the} alloy relative to that of pure gadolinium.
-Due to the lack of experimental  \textcolor{black}{data on the magnetocaloric properties of} \ce{Gd_{1-x}Y_x} alloys at the time \textcolor{black}{this analysis was made}, a simpler approach was used \textcolor{black}{in which} the properties of alloys with {a} low yttrium fraction are \textcolor{black}{identical to those} of pure gadolinium, except for the Curie temperature \textcolor{black}{(which is shifted to lower values)}.
-
-\subsubsection{Performance metrics}
-\label{sec:performance-metrics}
-
-The AMR model considers only one bed and assumes $N\ped{r}$ identical beds experience the same cycle, multiplyind the performance metrics below by this factor
-
-\nomenclature{an}{$N\ped{r}$}{number of regenerators}
-
-The cooling capacity is calculated as \cite{bib:trevizoli16_perfor_model}:
-
-\begin{equation}
-\label{eq:99}
-\qc = N\ped{r}\frac{1}{\tau} \int_{\tau\ped{HB}} \mrate\ped{f}(t) c_{p,\mathrm{f}} \left( T\ped{C} -T\ped{f,CE} \right) \diffd{t}
-\end{equation}
-
-\noindent where $\tau$ is the cycle period, and $\tau\ped{HB}$ is the duration of the hot blow, during which the cold end temperature is compared to the cold source temperature.
-
-\nomenclature[vh]{HB}{hot blow}
-\nomenclature[vc]{CE}{cold end}
-\nomenclature[am]{$\mrate\ped{f}$}{mass flow rate [\si{\kg\per\second}]}
-\nomenclature[vc]{C}{cold source}
-\nomenclature[vc]{H}{hot source}
-
-The magnetic power to operate the AMR cycle is modeled as the ideal Carnot power, ignoring most thermal irreversibilities:
-
-\begin{equation}
-\label{eq:100}
-\wmag = \qc \frac{T\ped{H} - \tc}{\tc}
-\end{equation}
-
-\noindent while the fluid friction irreversibility is accounted for in the calculation of the pumping power:
-
-\begin{equation}
-\label{eq:103}
-\wpump = N\ped{r}\frac{1}{\tau}\int_0^{\tau}\frac{\rate{m}\ped{f}}{\rho\ped{f}} \Delta P \diffd{t}
-\end{equation}
-
-\noindent where $\Delta P$ is the total pressure drop through the regenerator.
-
-\nomenclature[awm]{$\wpump$}{pumping power [\si{\watt}]}
-\nomenclature[awm]{$\wmag$}{magnetic power [\si{\watt}]}
-\nomenclature[ap]{$\Delta P$}{pressure drop across one region [\si{\pascal}]}
-
-\subsection{Hydraulic system  and fluid flow profile model}
-\label{sec:hydr-syst-model}
 
@@
 
-\nomenclature[azt]{$\tau\ped{B}$}{blow duration [\si{\second}]}
+\nomenclature[bt]{$\tau\ped{B}$}{blow duration [\si{\second}]}
+
+\subsubsection{How the magnetic profile is used}
+\label{sec:how-magnetic-profile}
+
+The magnetic profile is modeled by a waveform of magnetic field strength $H(t)$ applied perpendicular to the regenerators, as shown in \autoref{fig:amrmodel}.
+The magnetic field is assumed uniform throughout the beds.
+The applied field is corrected from demagnetization effects to yield the effective field inside the regenerators:
+
+\begin{equation}
+  \label{eq:6}
+  H\ap{eff} = H - N\ped{D} M
+\end{equation}
+
+\nomenclature[am]{$M$}{magnetization field [\si{\ampere\per\meter}]}
+\nomenclature[an]{$N\ped{D}$}{demagnetization tensor}
+
+\noindent where $M$ is the magnetization field of the material, and $N\ped{D}$ is a demagnetization factor.
+
+The magnetocaloric effect is implemented in the so-called discrete approach \cite{bib:nielsen11_review}; every time the magnetic field changes, based on the input magnetic profile, the solid temperature is calculated according to:
+
+\begin{equation}
+  \label{eq:89}
+  T\ped{s}(t + \Delta{}t) = T\ped{s}(t) + \dtad \left(T\ped{s}(t),H\ap{eff}(t),H\ap{eff}\left(t + \Delta{}t\right)\right)
+\end{equation}
+
+\nomenclature[bt]{$\dtad$}{adiabatic temperature variation [\si{\kelvin}]}
+
+\noindent where the adiabatic temperature variation $\dtad$, a standard measure of the MCE, is calculated from \textcolor{black}{tabulated} experimental \textcolor{black}{data} for magnetocaloric materials as function of temperature and effective field.
+\cite{bib:trevizoli16_perfor_model}.
+
+The magnetic profiles considered in this work are presented in terms of the flux density $B = \mu_0 H$, where $\mu_0$ is the permeability of free space; the magnetic field $H$ is used in the evaluation of the magnetocaloric effect (cf.
+Sec.~\ref{sec:how-magnetic-profile}).
+
+The instantaneous profile (represented by the subscript ``IT'') and the rectified cosine profile (represented by ``RC'') are defined solely in terms of the \textcolor{black}{extreme} values $B\ped{min}$ and $B\ped{min}$, and are shown in \autoref{fig:itrc}.
+
+\nomenclature[vi]{IT}{instantaneous magnetic profile}
+\nomenclature[vr]{RC}{rectified cosine magnetic profile}
+
+\begin{equation}
+{B}\ped{IT}\,(t)=
+\begin{cases}
+{B}\ped{max}, & 0 \le t < \nicefrac{\tau}{2} \\
+{B}\ped{min}, & \nicefrac{\tau}{2} \le t < \tau\\
+\end{cases}
+\label{eq:199}
+\end{equation}
+
+\begin{equation}
+{B}\ped{RC}\,(t) = B\ped{min} + \left(B\ped{max} - B\ped{min}\right)  \left\lvert \cos\left( \frac{\pi}{\tau} \left( t - \frac{\tau}{4}\right)\right) \right\rvert
+\label{eq:200}
+\end{equation}
+
+\begin{figure}[!ht]
+  \centering
+  \includegraphics[width=8cm]{profiles_it_and_rc}
+  \caption{Instantaneous ("IT") and rectified cosine ("RC") magnetic profiles}
+  \label{fig:itrc}
+\end{figure}
+
+A suitable approximation of the instantaneous profile is the \textcolor{black}{\emph{magnetic ramp profile}, shown} in \autoref{fig:ramp}, with finite transition times between the levels of constant magnetization.
+The magnetic profile oscillates  between a low value \({B}\ped{min}\) and a high value \({B}\ped{max}\), and \textcolor{black}{remains} at each plateau for a period of \(\tau\ped{M}\).
+The plateaus are balanced and centered at each half-cycle.
+
+\begin{figure}[!ht]
+  \centering
+  \includegraphics[width=7cm]{profile_rm}
+  \caption{\textcolor{black}{Magnetic ramp}  profile}
+  \label{fig:ramp}
+\end{figure}
+
+The \emph{ramp period} \(\tau\ped{R}\) \textcolor{black}{is} defined as:
+
+\begin{equation}
+\label{eq:201}
+\tau\ped{R} = \frac{1}{4}\left(\tau - 2 \tau\ped{M}\right)
+\end{equation}
+
+\noindent such that there are four ramp periods in one full cycle. The ramp rate, \(\theta\ped{R}\), is:
+
+\begin{equation}
+\label{eq:202}
+\tan \theta\ped{R} = \frac{\left({B}\ped{max} - {B}\ped{min}\right)}{2\tau\ped{R}}
+\end{equation}
+
+\nomenclature[azt]{$\tau\ped{R}$}{ramp period in the \textcolor{black}{magnetic} ramp profile [\si{\second}]}
+\nomenclature[azt]{$\tau\ped{M}$}{magnetization period in the \textcolor{black}{magnetic} ramp  profile [\si{\second}]}
+\nomenclature[azo]{$\theta\ped{R}$}{ramp rate in the \textcolor{black}{magnetic} ramp profile}
+
+The magnetization fraction, \(F\ped{M}\), is the fraction of the cycle \textcolor{black}{during which} the magnetocaloric material is \textcolor{black}{subjected to a} constant magnetic field:
+
+\begin{equation}
+\label{eq:204}
+F\ped{M} = \frac{2\tau\ped{M}}{\tau}
+\end{equation}
+
+\nomenclature[af]{$F\ped{M}$}{magnetization fraction}
+
+The ramp profile (``RM'') can be mathematically defined as:
+
+\begin{equation}
+{B}\ped{RM}(t)=
+\begin{cases}
+\nicefrac{\left({B}\ped{max} + {B}\ped{min}\right)}{2} + t \tan \theta\ped{R} , & 0 \le t < \tau\ped{R} \\
+{B}\ped{max}, & \tau\ped{R} \le t < \nicefrac{\tau}{2} - \tau\ped{R}\\
+{B}\ped{max} - \left(t - \left(\nicefrac{\tau}{2} - \tau\ped{R}\right)\right) \tan \theta\ped{R} , & \nicefrac{\tau}{2} - \tau\ped{R} \le t < \nicefrac{\tau}{2} + \tau\ped{R} \\
+{B}\ped{min}, & \nicefrac{\tau}{2} + \tau\ped{R} \le t < \tau - \tau\ped{R}\\
+{B}\ped{min} + \left(t - \left(\tau - \tau\ped{R}\right)\right) \tan \theta\ped{R} , & \tau - \tau\ped{R} \le t \le \tau \\
+\end{cases}
+\label{eq:203}
+\end{equation}
+
+\nomenclature[vr]{RM}{rectified cosine magnetic profile}
+
+Additionally, the average values of the magnetic field during each half-AMR cycle are considered for comparison between profiles.
+The average magnetic profile during the hot cycle ($0 \le t < \nicefrac{\tau}{2}$) is denoted $\average{B}\ped{high}$ and the average during the cold cycle  ($ \nicefrac{\tau}{2} \le t < \tau$) is denoted $\average{B}\ped{low}$.
+For the instantaneous waveform, these average values are identical to the extrema values.
+
+\subsubsection{Evaluation of solid and fluid properties}
+\label{sec:eval-solid-fluid}
+
+The fluid properties are considered constant in the momentum equation to decouple the solution \textcolor{black}{procedures to determine} the velocity and temperature fields.
+The properties are computed at the average temperature between the hot and cold sources temperatures, and are evaluated from interpolated tables exported from the EES software \cite{bib:klein13-ees}.
+In all simulations shown in this work, the heat transfer fluid is a mixture of water/ethylene-glycol with concentration \num{80}/\SI{20}{\percent} vol.
+For the energy equations, the fluid properties are also calculated from tabulated data, but the temperature dependence is considered.
+
+In this work, both single- and multilayer regenerators are considered.
+Single-layer regenerators are composed of gadolinium,  a benchmark material with a Curie temperature of \SI{290}{\kelvin}.
+\textcolor{black}{For simplicity, the solid} density is assumed constant at $\rho\ped{s} = \SI{7900}{\kg\per\cubic\meter}$ and the solid \textcolor{black}{thermal} conductivity is set to $k\ped{s} = \SI{10.5}{\watt\per\meter\per\kelvin}$.
+The specific heat \textcolor{black}{capacity} of \ce{Gd} is calculated as a function of temperature and magnetic field based on experimental \textcolor{black}{data}, using a bi-linear interpolation scheme; more details on the experimental dataset \textcolor{black}{are available} in \cite{bib:trevizoli16_perfor_model}.
+
+For the multilayer simulations, alloys of gadolinium and yttrium are used in the form \ce{Gd_{1-x}Y_x}, where $x$ is the yttrium fraction.
+\textcolor{black}{This fraction} decreases the Curie temperature  \textcolor{black}{of the} alloy relative to that of pure gadolinium.
+Due to the lack of experimental  \textcolor{black}{data on the magnetocaloric properties of} \ce{Gd_{1-x}Y_x} alloys at the time \textcolor{black}{this analysis was made}, a simpler approach was used \textcolor{black}{in which} the properties of alloys with {a} low yttrium fraction are \textcolor{black}{identical to those} of pure gadolinium, except for the Curie temperature \textcolor{black}{(which is shifted to lower values)}.
+
+\subsubsection{Performance metrics}
+\label{sec:performance-metrics}
+
+The AMR model considers only one bed and assumes $N\ped{r}$ identical beds experience the same cycle, multiplying the performance metrics below by this factor.
+
+\nomenclature[an]{$N\ped{r}$}{number of regenerators}
+
+The cooling capacity is calculated as \cite{bib:trevizoli16_perfor_model}:
+
+\begin{equation}
+\label{eq:99}
+\qc = N\ped{r}\frac{1}{\tau} \int_{\tau\ped{HB}} \mrate\ped{f}(t) c_{p,\mathrm{f}} \left( T\ped{C} -T\ped{f,CE} \right) \diffd{t}
+\end{equation}
+
+\nomenclature[vh]{HB}{hot blow}
+\nomenclature[vc]{CE}{cold end}
+\nomenclature[am]{$\mrate\ped{f}$}{mass flow rate [\si{\kg\per\second}]}
+\nomenclature[vc]{C}{cold source}
+\nomenclature[vc]{H}{hot source}
+
+The magnetic power to operate the AMR cycle is modeled as the ideal Carnot power, ignoring most thermal irreversibilities:
+
+\begin{equation}
+\label{eq:100}
+\wmag = \qc \frac{T\ped{H} - \tc}{\tc}
+\end{equation}
+
+\noindent while the fluid friction irreversibility is accounted for in the calculation of the pumping power:
+
+\begin{equation}
+\label{eq:103}
+\wpump = N\ped{r}\frac{1}{\tau}\int_0^{\tau}\frac{\rate{m}\ped{f}}{\rho\ped{f}} \Delta P \diffd{t}
+\end{equation}
+
+\noindent where $\Delta P$ is the total pressure drop through the regenerator.
+
+\nomenclature[awm]{$\wpump$}{pumping power [\si{\watt}]}
+\nomenclature[awm]{$\wmag$}{magnetic power [\si{\watt}]}
+\nomenclature[ap]{$\Delta P$}{pressure drop across one region [\si{\pascal}]}
+
+\subsection{Hydraulic system  and fluid flow profile model}
+\label{sec:hydr-syst-model}
 
@@
 \end{equation}
-
-\subsection{Definition of magnetic profiles}
-\label{sec:defin-magn-prof}
-
-The magnetic profiles considered in this work were shown in \autoref{fig:profiles}; here their mathematical definitions are presented.
-The profiles are presented in terms of the flux density $B = \mu_0 H$, where $\mu_0$ is the permeability of free space; the magnetic field $H$ is used in the evaluation of the magnetocaloric effect (cf.
-\autoref{sec:how-magnetic-profile}).
-
-The instantaneous profile (represented by the subscript ``IT'') and the rectified cosine profile (represented by ``RC'') are defined solely in terms of the \textcolor{black}{(extreme)} values $B\ped{min}$ and $B\ped{min}$:
-
-\nomenclature[vi]{IT}{instantaneous magnetic profile}
-\nomenclature[vr]{RC}{rectified cosine magnetic profile}
-
-\begin{equation}
-{B}\ped{IT}\,(t)=
-\begin{cases}
-{B}\ped{max}, & 0 \le t < \nicefrac{\tau}{2} \\
-{B}\ped{min}, & \nicefrac{\tau}{2} \le t < \tau\\
-\end{cases}
-\label{eq:199}
-\end{equation}
-
-\begin{equation}
-{B}\ped{RC}\,(t) = B\ped{min} + \left(B\ped{max} - B\ped{min}\right)  \left\lvert \cos\left( \frac{\pi}{\tau} \left( t - \frac{\tau}{4}\right)\right) \right\rvert
-\label{eq:200}
-\end{equation}
-
-As previously discussed, a suitable approximation of the instantaneous profile is the \textcolor{black}{\emph{magnetic ramp profile}, shown} in \autoref{fig:ramp}.
-The so-called \emph{hot cycle}, \textcolor{black}{during which} the MCM is magnetized, occupies the range \(0 \le t < \nicefrac{\tau}{2}\), while the \emph{cold cycle} lies in the range \(\nicefrac{\tau}{2} \le t < \tau\).
-The magnetic profile oscillates  between a low value \({B}\ped{min}\) and a high value \({B}\ped{max}\), and \textcolor{black}{remains} at each plateau for a period of \(\tau\ped{M}\).
-The plateaus are balanced and centered at each half-cycle.
-
-\begin{figure}[!ht]
-  \centering
-  \includegraphics[width=7cm]{profile_rm}
-  \caption{\textcolor{black}{Magnetic ramp}  profile}
-  \label{fig:ramp}
-\end{figure}
-
-The \emph{ramp period} \(\tau\ped{R}\) \textcolor{black}{is} defined as:
-
-\begin{equation}
-\label{eq:201}
-\tau\ped{R} = \frac{1}{4}\left(\tau - 2 \tau\ped{M}\right)
-\end{equation}
-
-\noindent such that there are four ramp periods in one full cycle. The ramp rate, \(\theta\ped{R}\), is:
-
-\begin{equation}
-\label{eq:202}
-\tan \theta\ped{R} = \frac{\left({B}\ped{max} - {B}\ped{min}\right)}{2\tau\ped{R}}
-\end{equation}
-
-\nomenclature[azt]{$\tau\ped{R}$}{ramp period in the \textcolor{black}{magnetic} ramp profile [\si{\second}]}
-\nomenclature[azt]{$\tau\ped{M}$}{magnetization period in the \textcolor{black}{magnetic} ramp  profile [\si{\second}]}
-\nomenclature[azo]{$\theta\ped{R}$}{ramp rate in the \textcolor{black}{magnetic} ramp profile}
-
-The magnetization fraction, \(F\ped{M}\), is the fraction of the cycle \textcolor{black}{during which} the magnetocaloric material is \textcolor{black}{subjected to a} constant magnetic field:
-
-\begin{equation}
-\label{eq:204}
-F\ped{M} = \frac{2\tau\ped{M}}{\tau}
-\end{equation}
-
-\nomenclature[af]{$F\ped{M}$}{magnetization fraction}
-
-The ramp profile (``RM'') can be mathematically defined as:
-
-\begin{equation}
-{B}\ped{RM}(t)=
-\begin{cases}
-\nicefrac{\left({B}\ped{max} + {B}\ped{min}\right)}{2} + t \tan \theta\ped{R} , & 0 \le t < \tau\ped{R} \\
-{B}\ped{max}, & \tau\ped{R} \le t < \nicefrac{\tau}{2} - \tau\ped{R}\\
-{B}\ped{max} - \left(t - \left(\nicefrac{\tau}{2} - \tau\ped{R}\right)\right) \tan \theta\ped{R} , & \nicefrac{\tau}{2} - \tau\ped{R} \le t < \nicefrac{\tau}{2} + \tau\ped{R} \\
-{B}\ped{min}, & \nicefrac{\tau}{2} + \tau\ped{R} \le t < \tau - \tau\ped{R}\\
-{B}\ped{min} + \left(t - \left(\tau - \tau\ped{R}\right)\right) \tan \theta\ped{R} , & \tau - \tau\ped{R} \le t \le \tau \\
-\end{cases}
-\label{eq:203}
-\end{equation}
-
-\nomenclature[vr]{RM}{rectified cosine magnetic profile}
-
-Additionally, the average values of the magnetic field during each half-AMR cycle are considered for comparison between profiles.
-The average magnetic profile during the hot cycle ($0 \le t < \nicefrac{\tau}{2}$) is denoted $\average{B}\ped{high}$ and the average during the cold cycle  ($ \nicefrac{\tau}{2} \le t < \tau$) is denoted $\average{B}\ped{low}$.
-For the instantaneous waveform, these average values are identical to the extrema values.
 

### 2019-09-17 PaperMagneticProfiles_JBSMSE.tex
Edit section on valve system.

@@
 
-The hydraulic system to modulate this fluid flow through different regenerators at different time instants is composed of a pump and a set of electronic valves which can be precisely controlled to yield the desired blow durations.
+The hydraulic system to modulate the fluid flow through different regenerators at different time instants is composed of a pump and a set of electronic valves which can be precisely controlled to yield the desired blow durations.
 The electrical power consumed by the valve array is computed separately from other work contributions.
@@
 
-In the second approach, \emph{Type A} valves are used, with lower nominal power but that depends on frequency and blow fraction. For these valves, the valve power was experimentally correlated as:
+In the second approach, \emph{Type A} valves are used, with  nominal power lower in magnitude but which depends on frequency and blow fraction.
+For these valves, the valve power was experimentally correlated as:
 
@@
 Indepedent of the valve type used, it is also assumed that this valve system can produce the fluid flow profile \textcolor{black}{shown in} \autoref{fig:mprofile}, where the displaced fluid mass during one blow in one regenerator bed is $\rate{m}\ped{f,max} F\ped{B} \nicefrac{\tau}{2}$.
-
 The \emph{utilization factor} can then be calculated as:
@@
 \nomenclature[bf]{$\Phi$}{utilization factor}
-
-\textcolor{black}{For an even number of poles in the magnetic circuit}, it may be advantageous to employ an odd number of regenerator beds to  \textcolor{black}{break the symmetry between the magnetic circuit and the beds, thus avoiding positions of equilibrium between magnetic forces which result in torque oscillations} \cite{bib:eriksen}.
-\textcolor{black}{Additionally}, in general, two valves per regenerator  may be necessary (one at each end), to independently control  the hot and cold blows for each bed and correct flow \textcolor{black}{imbalance}; thus, in all results in this work, the number of valves is \textcolor{black}{calculated as}:
+\noindent and in all results shown in this work, the number of valves is \textcolor{black}{calculated as}:
 

### 2019-09-17 PaperMagneticProfiles_JBSMSE.tex
Edit section on results of IT x RC.
In particular, the "same average" comparison was removed.

@@
 When comparing the \textcolor{black}{performances resulting from the application of the different} magnetic profiles, the average magnetic field during the hot cycle \textcolor{black}{will be considered} the same; this implies a higher peak for the rectified cosine.
-For the cold cycle, two comparison methods are considered, as shown in \autoref{fig:comparison-methods-profiles}:
-
-\begin{enumerate}
-\item The minimum values for both profiles is the same;
-\item The average value for both profiles during the cold cycle is the same.
-\end{enumerate}
-
-\textcolor{black}{For} reference, in all simulations,  the minimum value for the rectified cosine was fixed at ${B}\ped{min,RC} = \SI{0.1}{\tesla}$.
-\textcolor{black}{In} the first comparison, the minimum value for the instantaneous \textcolor{black}{waveform} was kept at the same level (${B}\ped{min,IT} =  {B}\ped{min,RC}$); hence, the average low value for the RC profile was higher ($\average{B}\ped{low,RC} > \average{B}\ped{low,IT}$).
-This represents common design scenarios: a constant low-valued plateau for the magnetic field for instantaneous-like magnetic profiles \cite{bib:insinga16_optim,bib:benedict16_desig}, or a low peak for the rectified cosine profile \cite{bib:trevizoli15_desig_halbac}.
-For the other comparison method, the low level of the instantaneous profile was increased (${B}\ped{min,IT} >  {B}\ped{min,RC}$) \textcolor{black}{in order} to keep the \textcolor{black}{same} average ($\average{B}\ped{low,RC} = \average{B}\ped{low,IT}$).
+For the cold cycle,  the minimum values for both profiles is the same, as shown in \autoref{fig:comparison-methods-profiles}.
+\textcolor{black}{For} reference, in all simulations,  the minimum value for the rectified cosine was fixed at ${B}\ped{min} = \SI{0.1}{\tesla}$.
 
@@
   \centering
-  \subfloat[Same minimum]{\includegraphics[width=8cm]{profiles_it_and_rc_same_minimum}\label{fig:profiles_inst_cos_same_minimum}}
-\quad
-  \subfloat[Same average]{\includegraphics[width=8cm]{profiles_it_and_rc_same_average}\label{fig:profiles_inst_cos_same_average}}
-  \caption{Comparison methods for the instantaneous and rectified cosine profiles }
+\includegraphics[width=8cm]{profiles_it_and_rc_same_minimum}
+  \caption{Configuration of average and extrema values of the instantaneous and rectified cosine profiles }
   \label{fig:comparison-methods-profiles}
@@
 
-In addition, simulations were \textcolor{black}{carried out} for various values of blow fraction; the rectified cosine profile can benefit from a smaller blow fraction because this can concentrate the flow during the periods of very high or low fields.
+Simulations were \textcolor{black}{carried out} for various values of blow fraction; the rectified cosine profile can benefit from a smaller blow fraction because this can concentrate the flow during the periods of very high or low fields.
 In this section, all results use the critical value of blow fraction that maximized the cooling capacity: fluid flowing during the entire period for the instantaneous profile, and only during \SI{60}{\percent}  of the period (the smallest blow fraction tested) for the cosine profile; this latter case is shown in \autoref{fig:cos-inst-60}.
@@
 
-Figure~\ref{fig:cos_ins} shows the cooling capacity attained by the device at a frequency of \SI{1}{\hertz} and different utilizations, for both comparison methods.
+Figure~\ref{fig:cos_ins} shows the cooling capacity attained by the device at a frequency of \SI{1}{\hertz} and different utilizations.
 The horizontal axis shows the average value during the high field region.
-\textcolor{black}{For} Fig.~\ref{fig:comp_min}, the instantaneous profile almost always yields a higher performance, while for Fig.~\ref{fig:comp_avg} the rectified cosine profile generates higher cooling capacities.
-Since the average \textcolor{black}{field} during the hot cycle (high field stage) is the same, the main difference is due to the low magnetic field levels.
-For the ``same minimum'' comparison, the instantaneous profile is capable of keeping the magnetic field at low levels for the whole half-cycle, which is beneficial for performance;  for $\Phi=1.0$ and $\average{B}\ped{high} = \SI{1.40}{\tesla}$, the cooling capacity for the instantaneous profile is $\SI{196.3}{\percent}$ higher than for the cosine profile.
+The instantaneous profile almost always yields a higher performance, and cince the average \textcolor{black}{field} during the hot cycle (high field stage) is the same, the main difference is due to the low magnetic field levels.
+For the ``same minimum'' comparison, the instantaneous profile is capable of keeping the magnetic field at low levels for the whole half-cycle, which is beneficial for performance;  for $\Phi=1.0$ and $B\ped{high} = \SI{1.40}{\tesla}$, the cooling capacity for the instantaneous profile is $\SI{196.3}{\percent}$ higher than for the cosine profile.
 As demonstrated by \cite{bib:asme-mce}, a higher average magnetic field during the low-field stage increases the solid temperature and consequently results in  warmer fluid entering the cold heat exchanger, representing a thermal loss.
-In the ``same-average'' comparison, the cosine profile is capable of achieving much lower levels (since its minimum value is fixed), therefore providing more cooling power.
-However, as explained before, this \textcolor{black}{analysis serves mainly the purpose of illustrating the influence of low magnetic field variation, by looking at two hypothetical scenarios.
-More} complex \textcolor{black}{magnetic circuit}  geometries \textcolor{black}{are} required to generate the instantaneous magnetic profile \textcolor{black}{with a} low \textcolor{black}{magnetic field} close to 0.
 
@@
   \centering
-  \subfloat[Same minimum]{\includegraphics[width=8cm]{Qc_B_comp_f_1_same_minimum}\label{fig:comp_min}}
-\,
-%  \subfloat[Same average]{\includegraphics[width=8cm]{Qc_B_comp_f_1_same_low_average}\label{fig:comp_avg}}
-\,
+\includegraphics[width=8cm]{Qc_B_comp_f_1_same_minimum}
   \caption{Cooling capacity as a function of the  average high magnetic field, for different utilizations.
-\textcolor{black}{``IT''}: instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}), for both comparison methods.}
+\textcolor{black}{``IT''}: instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}).}
  \label{fig:cos_ins}
@@
 
-The only exception in the ``same minimum'' comparison is seen for the lowest utilization of $\Phi = 0.2$, where the performance is slightly better for the RC profile.
+The only exception in this comparison  is seen for the lowest utilization of $\Phi = 0.2$, where the performance is slightly better for the RC profile.
 Since the blow fraction for the cosine is lower, the mass flow rate \textcolor{black}{is} higher \textcolor{black}{in the latter for} the same utilization (cf.
@@
 
-The same analysis, but in terms of the coeficient of performance, is shown in \autoref{fig:cos_ins_cop}.
-For the ``same average'' analysis, the $\cop$ results show the same trends as the cooling capacity.
-However, for the \textcolor{black}{somewhat} more realistic analysis where the minimum of both profiles are the same, the rectified cosine profile yields better results for small values of utilization.
+The same analysis, but in terms of the coeficient of performance, is shown in \autoref{fig:cos_ins_cop}, with the same trends as for the cooling capacity; however, in this case  the rectified cosine profile yields better results for small to medium values of utilization.
 This is due to \textcolor{black}{a} lower pumping power, as the mass flow rate for the cosine profile is slightly higher, but also flows for a shorter period of time.
@@
   \centering
-  \subfloat[Same minimum]{\includegraphics[width=7cm]{COP_B_comp_f_1_same_minimum}\label{fig:comp_min_cop}}
-\,
-%  \subfloat[Same average]{\includegraphics[width=7cm]{COP_B_comp_f_1_same_low_average}\label{fig:comp_avg_cop}}
-\,
+\includegraphics[width=7cm]{COP_B_comp_f_1_same_minimum}
   \caption{Coefficient of performance as a function of the  average high magnetic field, for different utilizations.
-\textcolor{black}{``IT''}: instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}), for both comparison methods.}
+\textcolor{black}{``IT''}: instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}).}
  \label{fig:cos_ins_cop}
@@
 As shown in the previous section, the instantaneous profile \textcolor{black}{generally} yields the highest values \textcolor{black}{of} cooling capacity.
-Therefore, in this section, a more detailed analysis of \textcolor{black}{this} profile has been carried out, \textcolor{black}{where the} maximum field in \autoref{fig:cobem-profiles} \textcolor{black}{is} varied, while the minimum value is kept at \SI{0.05}{\tesla}.
+Therefore, in this section, a more detailed analysis of \textcolor{black}{this} profile has been carried out, \textcolor{black}{where the} maximum field  \textcolor{black}{is} varied, while the minimum value is kept at \SI{0.05}{\tesla}.
 Figure~\ref{fig:qc_phi_inst} shows the cooling capacity as a function of \textcolor{black}{the} utilization, for several levels of the maximum magnetic field \textcolor{black}{and} two different operating frequencies.
-Because of the conflict between a low heat transfer rate for flow rates \textcolor{black}{that are} too low and losses in regenerator effectiveness in flow rates \textcolor{black}{that are} too high, there are critical values of utilization that maximize \textcolor{black}{the} cooling capacity, and this critical values increases with the magnetic field.
+Because of the conflict between a low heat transfer rate for flow rates \textcolor{black}{that are} too low and losses in regenerator effectiveness in flow rates \textcolor{black}{that are} too high, there are critical values of utilization that maximize \textcolor{black}{the} cooling capacity, and this critical values increase with the magnetic field.
 \textcolor{black}{For} higher magnetic fields, the increase in the MCE surpasses the loss of effectiveness, and one can go to higher flow rates without losing performance.
@@
 
-The parameters in \autoref{tab:params-cobem} were chosen from preliminary simulations, \textcolor{black}{so} they are not  optimal.
+The geometric parameters in \autoref{tab:params-cobem} were chosen from preliminary simulations, \textcolor{black}{so} they are not  optimal.
 To understand the impact of \textcolor{black}{the} regenerator geometry on the performance with the instantaneous profile, the regenerator height was varied in Fig.~\ref{fig:Qc_H_inst}, and all other parameters from \autoref{tab:params-cobem} were kept fixed and with $\phi=0.4$.

### 2019-09-17 PaperMagneticProfiles_JBSMSE.tex
Edit section in ramp results.

@@
 
-Based on the better performance of the instantaneous profile, the ramp profile is assumed as a suitable target profile for the design of magnetic refrigerators, and will be analyzed in this section.
+Based on the better performance of the instantaneous profile, the ramp profile is assumed as a suitable target profile for the design of magnetic refrigerators, and will be analyzed in this section, representing the second stage in the analysis of magnetic profiles.
 
 Moving towards a more realistic model, casing losses are included, using the model from \cite{bib:trevizoli16_perfor_model}.
-The bed is enclosed in a solid casing of thickness $h\ped{csg}$, and two air layers of thickness $h\ped{air}$ separate \textcolor{black}{the AMR and its casing} from the inner and outer \textcolor{black}{magnet} cylinders.
+The bed is enclosed in a solid casing of thickness $h\ped{csg}$, and two air layers of thickness $h\ped{air}$ separate \textcolor{black}{the AMR and its casing} from the inner and outer \textcolor{black}{magnet} cylinders, as shown in \autoref{fig:amr-casing}.
+These magnetic cylinders can be designed to yield the desired magnetic profiles, as will be shown in future studies by our group.
 
@@
 \nomenclature[ia]{air}{air layer between magnets and regenerators}
-\nomenclature[ic]{csg}{regenerator casing}
 
-Preliminary analyses \textcolor{black}{carried out by} \cite{bib:peixer17-perfor-amrs} using the losses model described in \autoref{sec:model-casing-loss} showed that a stainless steel casing \textcolor{black}{with a} thickness \textcolor{black}{of} $h\ped{csg} = \SI{0.5}{\mm}$ is thick enough to ensure mechanical integrity and easy manufacturing, while being thin enough to accommodate the material \textcolor{black}{with a low} thermal conductivity.
+Preliminary analyses \textcolor{black}{carried out by} \cite{bib:peixer17-perfor-amrs} showed that a stainless steel casing \textcolor{black}{with a} thickness \textcolor{black}{of} $h\ped{csg} = \SI{0.5}{\mm}$ is thick enough to ensure mechanical integrity and easy manufacturing, while being thin enough to accommodate the material \textcolor{black}{with a low} thermal conductivity.
 
@@
 $f$ & \SI{1}{\hertz} \\
-$\th$ & \SI{305.5}{\kelvin} = \SI{32.5}{\celsius} \\
+$T\ped{H}$ & \SI{305.5}{\kelvin} = \SI{32.5}{\celsius} \\
 $\tc$ & \SI{270.5}{\kelvin} = \SI{-2.5}{\celsius} \\
@@
 
-\subsubsection{Synchronization between \textcolor{black}{the} fluid flow and magnetic profiles}
-\label{sec:synchr-betw-fluid}
-
-A central point of this Thesis is \textcolor{black}{related to} the importance of two characteristic waveforms, the fluid flow and magnetic profiles, \textcolor{black}{and how they affect} the performance of a magnetic refrigerator.
-Several works have independently investigated the synchronization between these profiles \cite{bib:bjoerk11_amr,bib:nakashima17-exper}.
-Here, \textcolor{black}{the} focus is  on the parameterization of these waveforms and \textcolor{black}{the} characerization of an AMR system with these parameters, in particular the blow fraction (cf.
-\autoref{sec:inst-fluid-flow}) and the magnetization fraction (cf.
-\autoref{sec:ramp-magn-prof}).
-Figure~\ref{fig:ramp-inst} shows the two profiles that will be used in this section.
+ Figure~\ref{fig:ramp-inst} shows the two profiles that will be used in this section and how they are synchronized.
+Regarding the magnetic profile, the \textcolor{black}{magnitude of the} high value will be varied to investigate the performance of the AMR system, while the minimum will be kept at $\bmin = \SI{0.05}{\tesla}$.
 
@@
 
-Regarding the magnetic profile, the \textcolor{black}{magnitude of the} high value will be varied to investigate the performance of the AMR system, while the minimum will be kept at $\bmin = \SI{0.05}{\tesla}$.
-Ideally, this value \textcolor{black}{should be nil}, but it is \textcolor{black}{difficult} to achieve complete flux insulation in the low field region, so \textcolor{black}{a finite value of the} minimum field is \textcolor{black}{adopted}.
-
 \subsubsection{Performance curves for varying blow and magnetization fractions}
@@
 It is clear \textcolor{black}{that both the cooling capacity and the coefficient of performance exhibit a peak at} $F\ped{M} = F\ped{B}$.
-Moreover,  \textcolor{black}{to the right of the peak, i.e., for higher values of $F\ped{M}$, the}  reduction \textcolor{black}{of} both \textcolor{black}{performance} metrics \textcolor{black}{is} slower, meaning it is better to have a magnetization plateau wider than the fluid flow plateau, thus confirming the conclusions \textcolor{black}{of} \autoref{cha:exper-invest-fluid}.
+Moreover,  \textcolor{black}{to the right of the peak, i.e., for higher values of $F\ped{M}$, the}  reduction \textcolor{black}{of} both \textcolor{black}{performance} metrics \textcolor{black}{is} slower, meaning it is better to have a magnetization plateau wider than the fluid flow plateau
 
 The reduction in performance for $F\ped{M} > F\ped{B}$ \textcolor{black}{can be explained by an increase in} heat leakage through the casing, as the solid begins to lose energy to the environment \textcolor{black}{when} the fluid is not flowing.
-For $F\ped{M} < F\ped{B}$, the effect \textcolor{black}{discussed in} \autoref{sec:results-discussions} is present: the fluid begins to flow when the solid is not totally warmed up, losing effectiveness.
+For $F\ped{M} < F\ped{B}$,  the fluid begins to flow when the solid is not totally warmed up, losing effectiveness.
 
@@
 
-The influence of \textcolor{black}{the} utilization is demonstrated in \autoref{fig:Qc_curves_ramp_phi}, where the cooling capacity \textcolor{black}{is} plotted for different utilization factors.
+The influence of utilization is demonstrated in \autoref{fig:Qc_curves_ramp_phi}, where the cooling capacity \textcolor{black}{is} plotted for different utilization factors.
 For increasing $\Phi$ in this range, not only do the overall values of cooling capacity increase, but also the importance of choosing the blow fraction becomes clearer.
@@
 \textcolor{black}{All} previous results assumed a fixed regenerator geometry, with the goal of identifying the optimal fluid and magnetic profile parameters.
-\textcolor{black}{It became clear that the} magnetization fraction should be as large as possible, but that makes it more difficult to design a magnetic circuit \textcolor{black}{based on} permanent magnets.
+\textcolor{black}{It became clear that the} magnetization fraction should be as large as possible, but that raises some challenges in realizing abrupt changes in the magnetic field.
 The value of $F\ped{M} = \SI{70}{\percent}$ is then chosen as a compromise, with \textcolor{black}{a corresponding} $F\ped{B} = F\ped{M}$.
 The mean value of \textcolor{black}{the} utilization factor of $\Phi = 0.4$ is also chosen as reference in the next results.
-
-In this section, the \textcolor{black}{effect of the} regenerator height is \textcolor{black}{evaluated.
-The results will complement those for the} air gap height that will be shown in \autoref{cha:design-optim-magn} concerning the design of the magnetic circuit.
-The importance of the air gap height as a coupling \textcolor{black}{parameter} between the geometric design of the regenerators and the magnetic circuit was explored using a simplified model in \autoref{sec:performance-an-amr} and using the instantaneous magnetic profile in \autoref{sec:deta-analys-inst}.
-The results \textcolor{black}{to be} shown \textcolor{black}{here} use the magnetic \textcolor{black}{ramp} profile \textcolor{black}{studied in depth in} this present chapter.
 

### 2019-09-17 PaperMagneticProfiles_JBSMSE.tex
Expand section on final considerations.

@@
 To the authors' knowledge, this is the first study where magnetic profiles for AMR model are mathematically modeled and the model parameters are changed in a systematic way.
+The instantaneous, rectified cosine and ramp magnetic profiles were implemented in an AMR model, and the profile parameters were varied simultaneously with regenerator geometric parameters.
+These waveforms can be found in existing MR devices published in the literature.
 
-The instantaneous profile yields higher cooling capacity, even by
-reducing the blow fraction on rectified cosine, up to levels achieved by pumping and valving systems, mainly restricted by valve opening times
+Using a simplified model, the instantaneous profile yields higher cooling capacity, even by reducing the blow fraction on rectified cosine, at least up to levels achieved by pumping and valving systems; further reductions of the blow fraction is mainly restricted by valve opening times.
+This means that, even if sinusoidal profiles can be obtained with more compact magnetic circuit systems, the performance of MR systems can be maximized by using instantaneous variations of the magnetic field, and then optimizing the regenerator height and blow duration.
 
 The ramp profile is a feasible approximation for the instantaneous
-profile, and can be optimized for increasing cooling capacity.
-In particular, by synchronizing the plateau durations between fluid
-and magnetic profiles.
+profile without abrupt changes in the magnetic field plateaus.
+This waveform can be optimized for increasing cooling capacity, in particular by synchronizing the plateau durations between fluid and magnetic profiles.
 

### 2019-09-18 figures.py
Change power contributions figure.
The power figures are now plotted for one
pair (f, Phi), and show all contributions
for IT and RC profiles.

@@ -35,6 +35,7 @@ DENSITY_GD = 7900 # kg/m3, from Trevizoli et al (2016), IJR volume 72
 B_LABEL = r'${B}_\mathrm{high}\,[\mathrm{T}]$'
 Q_LABEL = r'$\dot{Q}_{\mathrm{C}}\,[\mathrm{W}]$'
 COP_LABEL = r'$\mathrm{COP}$'
+W_LABEL = r'$\dot{W}\,[\mathrm{W}]$'
 W_PUMP_LABEL = r'$\dot{W}_\mathrm{pump}\,[\mathrm{W}]$'
 W_MAG_LABEL = r'$\dot{W}_\mathrm{mag}\,[\mathrm{W}]$'
 W_VALVE_LABEL = r'$\dot{W}_\mathrm{valve}\,[\mathrm{W}]$'
@@ -295,7 +296,7 @@ def plot_W_Inst_vs_CCH(table_inst,table_cch,F_inst,F_CCH, figure_suffix=""):
     selecting points with blow fractions 'F_inst' and 'F_CCH',
     and adding 'figure_suffix' to the end of the filename for each figure
     
-    Creates one figure for each value of f, with curves for constant Phi for each profile
+    Creates one figure for each value of f and Phi, with all contributions plotted
     """ 
 
     regsim_utilizations = {0.1988: 0.2,
@@ -328,27 +329,11 @@ def plot_W_Inst_vs_CCH(table_inst,table_cch,F_inst,F_CCH, figure_suffix=""):
             
         if  table_inst_f_F[ld.MINIMUM_PROFILE_COLUMN].max() > 0.1:
             table_inst_f_F_Hmin = table_inst_f_F   
-                       
-                     
-        fig, axis = create_plot(ylabel=W_PUMP_LABEL,
-                                               xlabel=B_LABEL)
-
-        fig_mag, axis_mag = create_plot(ylabel=W_MAG_LABEL,
-                                               xlabel=B_LABEL)
-
-        fig_valve, axis_valve = create_plot(ylabel=W_MAG_LABEL,
-                                               xlabel=B_LABEL)
-        
-                
-        y_max = 0
-        y_COP_max = 0
-        y_mag_max = 0
-        y_valve_max = 0
-                             
                   
         for (i,phi) in enumerate(phi_vector):
 
-            label_text = r'$\Phi = ' + '%.1f' %(regsim_utilizations[phi]) + r'$'
[…]

### 2019-09-18 figures.py
Set limits for the Qc x Phi figures.

@@ -421,6 +421,11 @@ def plot_Qc_phi_Inst(table):
     
     markers=['s','o','x','v','^','h','<']
     colors=["black", "firebrick","darkcyan","indigo","sienna"]
+    
+    # tweak for better visuals
+    Qc_max = 600 
+    COP_max = 3.0
+
     for f in f_vector:    
         table_f = filter_table_from_column(table,ld.FREQUENCY_COLUMN,f)
         
@@ -466,7 +471,15 @@ def plot_Qc_phi_Inst(table):
                     ax.set_xlim(0.2,1)
                     ax.grid(True)
                     refine_yticks(ax,5)
-              
+                
+
+                axis_Qc.set_ylim((-Qc_max,Qc_max))
+                refine_yticks(axis_Qc,5)
+
+                axis_COP.set_ylim((-COP_max,COP_max))
+                refine_yticks(axis_COP,5)
+
+
                 fig_list.append((fig_Qc,fig_COP))
                 
                 

### 2019-09-19 PaperMagneticProfiles_JBSMSE.tex
Comment on evaluation of stainless steel and air thermophysical properties.
Update power figure with different colors and correct filename.

@@
 
-The same analysis, but in terms of the coeficient of performance, is shown in \autoref{fig:cos_ins_cop}, with the same trends as for the cooling capacity; however, in this case  the rectified cosine profile yields better results for small to medium values of utilization.
-This is due to \textcolor{black}{a} lower pumping power, as the mass flow rate for the cosine profile is slightly higher, but also flows for a shorter period of time.
-\textcolor{black}{Since} in this region the cooling capacity for the RC profile can be close to or higher than the \textcolor{black}{IT} profile (cf.
-Fig.~\autoref{fig:comp_min}), the coefficient of performance becomes higher for the rectified cosine profile.
+The same analysis, but in terms of the coeficient of performance, is shown in \autoref{fig:cos_ins_cop}, where it can be seen that the instantaneous profile yields better results for medium to high levels of utilization.
+This is due to some phenomena shown in \autoref{fig:cos_ins_w} for a fixed utilization of 0.6: the magnetic power only change between profiles due to variations in cooling capacity; the valve power is higher for the IT profile since the valves must remain open for longer periods; but the proportional increase in pumping power, due to larger flow rate, is even higher (than the change in valve power).
 
@@
  \label{fig:cos_ins_cop}
+\end{figure}
+
+\begin{figure}[!ht]
+  \centering
+  \includegraphics[width=10cm]{W_B_comp_f_1_Phi_60_same_minimum}
+  \caption{Power contributions as functions of the average high magnetic field, for a utilization of 0.6.
+\textcolor{black}{``IT''}: instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}).}
+  \label{fig:cos_ins_w}
 \end{figure}
@@
 This value \textcolor{black}{gave rise to a} peak in cooling capacity due to the compromise between minimizing losses and maximizing the magnetocaloric mass.
+The thermophysical properties of stainless steel and air were also obtained with interpolation of tables exported by the EES software \cite{bib:klein13-ees}.
 

### 2019-09-19 figures.py

@@ -314,7 +314,7 @@ def plot_W_Inst_vs_CCH(table_inst,table_cch,F_inst,F_CCH, figure_suffix=""):
 
     fig_list = []
     markers=['s','o','x','v','^','h','<']
-    colors=["black", "firebrick","darkcyan","indigo","sienna"]
+    colors=["indigo","sienna","darkgreen"]
     for f in f_vector:    
         table_inst_f = filter_table_from_column(table_inst,ld.FREQUENCY_COLUMN,f)
         table_cch_f = filter_table_from_column(table_cch,ld.FREQUENCY_COLUMN,f)
@@ -393,7 +393,7 @@ def plot_W_Inst_vs_CCH(table_inst,table_cch,F_inst,F_CCH, figure_suffix=""):
             refine_xticks(axis,4)
             refine_yticks(axis,4)
 
-            fig_name = "Wpump_B_comp_f_%d_Phi_%d%s" %(f,1e2*regsim_utilizations[phi],figure_suffix)
+            fig_name = "W_B_comp_f_%d_Phi_%d%s" %(f,1e2*regsim_utilizations[phi],figure_suffix)
             save_figure(fig,fig_name)
             plt.close(fig)
 

### 2019-10-22 PaperMagneticProfiles_JBSMSE.tex
Include revised manuscript from JRB.

@@
 
+\usepackage[numbers]{natbib}
 \usepackage{graphicx}
@@
 
-\title{Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators}
+\title{Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators
+\thanks{
+An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}).
+}}
 
 \author{
-Fábio P. Fortkamp \and
+F\'{a}bio P. Fortkamp \and
 Gusttav B. Lang \and
@@
 \institute{
-Fábio P. Fortkamp \\
+F\'{a}bio P. Fortkamp \\
 \email{fabio@polo.ufsc.br} \\
@@
 \begin{abstract}
-Magnetic cooling is an alternative to vapor compression with no use of hazarduous gases.
-The refrigerant is a solid material which reacts to oscillations in magnetic field with changes in temperature.
-In active magnetic regenerators, this magnetocaloric material and its effect are coupled with an oscillating fluid flow to yield a thermodynamic cooling cycle between cold and hot source temperatures.
-The literature is abundant with studies on the influence of the fluid flow waveform on magnetic refrigeration devices, but the influence of the magnetic field waveform is less investigated.
-In this work, we simulate a previously developed active magnetic regenerator numerical model with different mathematically-defined waveforms, and determine which operating parameters yield the highest values for cooling capacity and coefficient of performance.
-Results show that the highests performance levels are achieved when the magnetic field is kept constant for the same duration of the fluid flow through the magnetized material, and that the transition times between high and low levels of the magnetic field should be as fast as possible.
+Magnetic cooling is an alternative to vapor compression that does not rely on the use of hazardous substances.
+The refrigerant is a solid material which reacts to oscillations in magnetic field by changing its temperature (the magnetocaloric effect).
+In active magnetic regenerators, the magnetocaloric material arranged as a porous medium is subjected to an oscillating fluid flow to allow heat transfer from a cold source to a hot sink in a thermodynamic cooling cycle.
+Although the  literature is abundant with studies on the influence of the fluid flow waveform on magnetic refrigeration devices, the influence of the magnetic field waveform has been much less investigated.
+In this work, we make use of an active magnetic regenerator numerical model with different mathematically-defined waveforms to determine which operating parameters yield the highest values of cooling capacity and coefficient of performance for a specific set of operating conditions.
+The results show that the best performance is achieved when the magnetic field is kept constant for the same time duration of the fluid flow through the magnetized material, and that the transition times between the high and low levels of the magnetic field should be as short as possible.
 
-\keywords{ magnetic refrigeration \and active magnetic regenerator \and numerical modeling \and magnetocaloric effect}
+\keywords{magnetic refrigeration \and active magnetic regenerator \and numerical modeling \and magnetocaloric effect}
 \end{abstract}
@@
 
-Mechanical vapor compression has been the dominant cooling technology for the past century \cite{bib:nik} but, despite its dominance, it still faces an increasing number of challenges related to the its environmental footprint.
-In particular, the phase-out of refrigerants \textcolor{black}{with} ozone depleting \textcolor{black}{and global warming potentials has} introduced the use of flammable substances, with their own set of risks for consumer applications \cite{bib:iir-flammable} and technological challenges \cite{bib:lionte18-adapt}.
+Although mechanical vapor compression has been the dominant cooling technology for the past century \cite{bib:nik}, it still faces a number of challenges related to its environmental footprint.
+For instance, the phase-out of refrigerants with ozone depleting and global warming potentials brought about a more widespread use of flammable substances, which pose a new set of concerns, restrictions and new technological challenges for consumer applications \cite{bib:iir-flammable, bib:lionte18-adapt}.
 
-Magnetic refrigeration (MR) is an advanced cooling technology with no use of hazarduous gases, where a \emph{magnetocaloric material} (MCM) \textcolor{black}{is subjected to a cyclical change of the applied} magnetic field, and its temperature \textcolor{black}{changes as a result} of the \emph{magnetocaloric effect} (MCE).
-The magnitude of the MCE  \textcolor{black}{depends} on  material parameters, magnetic field variation and temperature, and its maximal at the Curie temperature of the material.
-For a thorough introduction to the magnetocaloric effect and magnetocaloric materials, the reader is referred to \cite{bib:smith-magneto}.
+Magnetic refrigeration (MR) is an emerging cooling technology which does not rely on hazardous fluids.
+In MR, the temperature of a  \emph{magnetocaloric material} (MCM) changes as a result of cyclical changes in the applied magnetic field due to the so-called \emph{magnetocaloric effect} (MCE).
+The magnitude of the MCE depends on  material properties, magnetic field variation and temperature, and it is maximum at the Curie temperature of the material \cite{bib:smith-magneto, bib:kitanovski}.
+Applications of the MCE at near room-temperature are not restricted to cooling applications; it can also be applied to the development of thermomagnetic motors \cite{bib:kaneko}.
 
@@
 
-For operating conditions typical of a low-temperature span magnetic refrigerator, the MCE is typically \textcolor{black}{on} the order of \num{2}-\SI{5}{\kelvin}.
-\textcolor{black}{T}o amplify this \textcolor{black}{temperature change}, heat regeneration is usually employed \cite{bib:kitanovski}.
-Active magnetic regenerators (AMR) are thermal devices where the magnetocaloric material constitutes a solid matrix through which flows an aqueous heat transfer fluid, and which is cyclically magnetized and demagnetized to activate the magnetocaloric effect.
-\textcolor{black}{Such a regenerator is essentially a cascade of infinitesimal ``layers'' of MCM that are activated simultaneously} to build up a temperature profile \textcolor{black}{along its length}.
-These layers can be made of the same material, yielding an homogeneous regenerator; however, given the  dependence  of the MCE with temperature, it is an interesting strategy to build \emph{multilayer} regenerators, where each layer is composed of a different material \textcolor{black}{that} will work around its \textcolor{black}{own} Curie temperature, maximizing the magnetocaloric effect of each portion.
+For operating temperatures typical of household cooling applications, the MCE is of the order of \num{2}-\SI{5} K/T.
+To amplify this temperature change, heat regeneration is usually employed \cite{bib:kitanovski}.
+Active magnetic regenerators (AMR) are thermal devices in which the magnetocaloric material is packed as a porous matrix subjected to periodic flow of an aqueous heat transfer fluid.
+The flow is put in sync with successive magnetization and demagnetization steps of the MCM in the porous bed to produce a refrigerating effect.
+Thus, the AMR is essentially a cascade of infinitesimal ``layers'' of MCM that are activated simultaneously to build up a longitudinal temperature profile in the matrix.
+The layers can be made of the same material, resulting in a homogeneous regenerator.
+However, given the dependence of the MCE on temperature, it is desirable to build \emph{multilayer} regenerators, where each adjacent layer has a slightly different composition that will function around its own Curie temperature, maximizing the magnetocaloric effect of each portion.
 
@@
 
-Magnetic refrigerators can operate according to different thermodynamic cycles, but the stages are roughly as follows.
-The magnetic circuit magnetizes the MCM, increasing its temperature due to the MCE.
-During the so-called \emph{cold blow}, cold fluid from the cold source flows through the warm bed and absorbs its energy, releasing it to the external heat exchanger.
-On the return of the fluid, the solid is demagnetized and cooled down, and in the \emph{hot blow} the fluid relases energy to the bed, decreasing its temperature so it can absorb the thermal load at the cold source.
-The cycle then repeats; different cycles can be configured by different durations and synchronization steps between these two \emph{characteristic waveforms}:
+A typical AMR cycle is comprised of the following steps: (i) The magnetic circuit magnetizes the MCM, thereby increasing its temperature due to the MCE; (ii) During the \emph{cold blow}, cold fluid previously in thermal contact with the low-temperature source flows through the warm bed, absorbs its energy and releases it as heat to the high-temperature sink through the hot heat exchanger; (iii) The MCM is demagnetized and coold down as a result; (iv) As the fluid flow is reversed (\emph{hot blow}), it releases energy to the bed, decreases its temperature so it can absorb the thermal load at the cold heat exchanger in contact with the low-temperature source.
+Different cycles can be devised by changing the duration and synchronization  between the two cycle \emph{characteristic waveforms}:
 
 \begin{enumerate}
-\item The \emph{magnetic profile}, which describes the oscillating magnetic field over one regenerator;
+\item The \emph{applied magnetic field profile}, which describes the oscillating magnetic field over one regenerator;
 \item The \emph{fluid flow profile}, which describes the time-variation of flow rate through one bed.
@@
 
-Fluid flow profiles are more easily investigated with experimental methods, since they can be altered with modifications in the fluid flow system.
-In particular, the \emph{duration} of blows have been extensively investigated \cite{bib:teyber17_exper,bib:nakashima18-influen-exp,FORTKAMP2018}, and the literature shows that the cooling capacity of magnetic refrigerators can be increased by focusing fluid flows during periods where the magnetic field is at its extrema values.
+Fluid flow profiles can be more easily investigated  experimentally, as no changes in the fluid flow hardware are required.
+In particular, the effect of the \emph{duration} of the fluid blows has been extensively investigated \cite{bib:teyber17_exper,bib:nakashima18-influen-exp,FORTKAMP2018}.
+There appears to be a consensus in the literature that the cooling capacity of magnetic refrigerators can be increased by displacing the fluid during periods where the magnetic field is at its extreme values.
 
-In this work, we focus on magnetic profiles, which are less studied in the literature.
-These waveforms are usually investigated in terms of their synchronization with the fluid flow profile \cite{TUSEK20111507,bib:bjoerk11_amr}.
-This paper uses the AMR model developed by \cite{bib:trevizoli16_perfor_model}, and the same authors had studied magnetic profiles waveforms in an earlier work \cite{bib:asme-mce}.
-However, their amplitudes was not varied, nor were they investigated with different geometries.
+In contrast, because of the complexities involved in designing and fabricating magnetic circuits, the applied magnetic field profiles (or simply the magnetic waveforms) are much less studied.
+Magnetic waveforms are usually investigated in terms of their synchronization with the fluid flow profile \cite{TUSEK20111507,bib:bjoerk11_amr}.
+\colorbox{yellow}{acho q cabe explicar brevemente o que os trabalhos de \cite{TUSEK20111507} e \cite{bib:bjoerk11_amr} fizeram...}.
+Trevizoli et al.~\cite{bib:trevizoli16_perfor_model} carried out a numerical comparison of the square wave (step change), sinusoidal and rectified cosine magnetic profiles.
+However, no systematic assessment of the effect of amplitude was performed nor did they investigate different geometries \colorbox{yellow}{nao estah claro o que vc quer dizer por geometries}.
 
-The present work combines the gaps from the above cited papers in investigating the performance of a magnetic refrigerator under different magnetic profile waveforms.
+\colorbox{yellow}{Fabio, acho que revisao bibliografica tem que ser expandida, trazendo trabalhos mais recentes em refrigeracao magnetica.}
+
+\colorbox{yellow}{Tambem tem que trazer aqui para a revisao os nossos artigos que mediram/testaram/modelaram as valvulas.}
+
+The present work bridges the gaps left in previous studies by investigating the performance of a magnetic refrigerator under different magnetic profile waveforms.
 These waveforms are mathematically modeled, and the cooling capacity and coefficient of performance are calculated based on the profiles parameters, while also investigated how the AMR geometry affect the performance in combinations with the magnetic profile.
@@
 
-As previuosly explained, we perform numerical simulations of a previously developed AMR model, varying the profile-specific and geometric parameters.
-We also couple a model for calculating  the power comsumption of a proposed fluid management system, a topic understudied in the literature.
-The output of this integrated model are cooling capacity, power contributions and the coefficient of performance (COP).
+As previuosly explained, we performed numerical simulations using a previously developed AMR model, varying the profile-specific and geometric parameters.
+We also implemented a model to calculate the power consumption of a novel fluid management system, which is a topic not yet extensively studied in the literature.
+The output variables from this integrated model are the cooling capacity, the several power contributions (\colorbox{yellow}{specify}) and the coefficient of performance (COP).
 
@@
 
-Simulations were performed using a one-dimensional AMR mathematical model, implemented using the Finite Volumes Method \cite{bib:trevizoli16_perfor_model}.
-Here we will show a summarized version focusing on the governing equations.
-This model solves momentum and energy balance equations for the solid and fluid phases, represented by indices `s' and `f', respectively.
-The model geometry is depicted in \autoref{fig:amrmodel}, and assumes regenerators composed of monodisperse packed spheres with porosity $\varepsilon$.
+Simulations were performed using a one-dimensional AMR mathematical model, implemented using the Finite Volume Method \cite{bib:trevizoli16_perfor_model}.
+The model solves momentum and energy balance equations for the solid and fluid phases, represented by indices `s' and `f', respectively.
+The model geometry is shown in \autoref{fig:amrmodel}, and assumes that the regenerator is composed of monodisperse packed spheres with porosity $\varepsilon$.
 
@@
 
-The momentum equation for the fluid domain is:
+The momentum equation for the fluid domain is given by:
 
@@
 
-Initial and boundary conditions, solution methods, convergence analyses, and closure relations for the porous media terms are described in \cite{bib:trevizoli16_perfor_model}.
+\colorbox{yellow}{Fabio, talvez valha a pena explicar quem eh quem nos termos das equacoes da Q movimento e energias...}
+
+Initial and boundary conditions, closure relations for the porous media terms, solution methods and convergence criteria and analyses are discussed in detail in \cite{bib:trevizoli16_perfor_model}.
 This AMR model solves the above equations for one regenerator operating between given sources temperatures (assuming ideal heat exchangers in contact with the thermal reservoirs), during one full cycle (hot and cold blows and  magnetization and demagnetization periods), given specified operating conditions (to be discussed later).
 
-The casing heat transfer term $\rate{q}\ped{csg}$ in \autoref{eq:78} is calculated solving the heat conduction in the regenerators casing \cite{bib:trevizoli16_perfor_model}, and can be neglected to simplify some analyses.
-More details are provided in \autoref{sec:results-discussions}.
+The casing heat transfer term $\rate{q}\ped{csg}$ in \autoref{eq:78} is calculated solving the heat conduction equation in the regenerator casing \cite{bib:trevizoli16_perfor_model}.
+It can be neglected in some circumstances if an insulating casing material is assumed, which greatly simplifies the analysis.
+%More details are provided in \autoref{sec:results-discussions}.
 
-\subsubsection{How the fluid flow profile is used}
+\subsubsection{Fluid flow profile modeling}
 \label{sec:how-fluid-flow}
@@
 
-\noindent where \(g(t)\) is a dimensionless function that expresses the mathematical waveform of the pressure gradient, and  \(A\ped{t}\) is its amplitude,  adjusted in a convergence loop; the mass flow rate calculated from the Darcy velocity from \autoref{eq:75} is compared with the input value of mass flow rate until these values converge.
-The waveform $g(t)$ represents the fluid flow profile used.
+\noindent where \(g(t)\) is a dimensionless function that expresses the mathematical waveform of the pressure gradient, and  \(A\ped{t}\) is its amplitude,  adjusted in a convergence loop.
+In this loop, the mass flow rate calculated in term of the Darcy velocity from \autoref{eq:75} is compared with the input   mass flow rate until convergence is obtained.
+%The waveform $g(t)$ represents the fluid flow profile used.
 
@@
 
-The canonical fluid flow profile considered in this work \textcolor{black}{ is the square wave or \emph{instantaneous profile}}, because of the instantaneous change in flow rate, as shown in \autoref{fig:mprofile}.
+The canonical fluid flow profile considered in this work is the square wave or \emph{instantaneous profile}, because of the instantaneous change in flow rate, as shown in \autoref{fig:mprofile}.
 
@@
 
-The \textcolor{black}{instantaneous mass flow rate}, \(\rate{m}\ped{f}(t)\), is defined over a cycle with \textcolor{black}{a} period \(\tau\), and represents the fluid flow \textcolor{black}{through} a given regenerator bed.
-The so-called \emph{hot cycle}, \textcolor{black}{during which} the MCM is magnetized, occupies the \textcolor{black}{time interval} \(0 \le t < \nicefrac{\tau}{2}\), while the \emph{cold cycle}
-lies \textcolor{black}{between} \(\nicefrac{\tau}{2} \le t \le \tau\). The flow profile oscillates between two plateaus of equal magnitude
-\(\rate{m}\ped{f,max}\) \textcolor{black}{and} opposite directions, \textcolor{black}{which} are centered in each half-cycle. During the hot cycle, the cold
-blow period is \(\tau\ped{CB}\), and during the cold cycle the hot blow period is \(\tau\ped{HB}\). If the flow is balanced, then \(\tau\ped{CB} = \tau\ped{HB}\).
+The instantaneous mass flow rate, \(\rate{m}\ped{f}(t)\), is defined over a cycle with a period \(\tau\), and represents the fluid flow through a given regenerator bed.
+The so-called \emph{hot cycle}, during which the MCM is magnetized, occupies the time interval \(0 \le t < \nicefrac{\tau}{2}\), while the \emph{cold cycle} lies between \(\nicefrac{\tau}{2} \le t \le \tau\).
+The flow profile oscillates between two plateaus of equal magnitude
+\(\rate{m}\ped{f,max}\) and opposite directions, which are centered in each half-cycle. During the hot cycle, the cold
+blow period is \(\tau\ped{CB}\), and during the cold cycle the hot blow period is \(\tau\ped{HB}\). If balanced flow exists, then \(\tau\ped{CB} = \tau\ped{HB}\).
 
-During each half cycle, there are periods \textcolor{black}{without}  fluid flow, defined as:
+During each half cycle, there are periods without  fluid flow defined as:
 
@@
 
-where HC and CC stand for hot \textcolor{black}{cycle} and cold cycle, respectively.
+where HC and CC stand for hot cycle and cold cycle, respectively.
 
@@
 
-When the blows have different time durations, the AMR cycle is considered unbalanced, and this \textcolor{black}{is known to have} a negative effect on performance \cite{bib:eriksen16_effec,bib:nakashima18-influen-exp}.
-In this work, the blows are always balanced, hence the blow fraction, the ratio of blow durations to cycle period \cite{bib:nakashima18-influen-exp}, can be evaluated as:
+When the blows have different time durations, the AMR cycle is considered unbalanced, and that is known to have a negative effect on performance \cite{bib:eriksen16_effec,bib:nakashima18-influen-exp}.
+In this work, the blows are always balanced, hence the blow fraction, i.e., the ratio of blow durations to cycle period \cite{bib:nakashima18-influen-exp}, can be evaluated as:
 
@@
 
-\subsubsection{How the magnetic profile is used}
+\subsubsection{Magnetic profile modeling}
 \label{sec:how-magnetic-profile}
 
-The magnetic profile is modeled by a waveform of magnetic field strength $H(t)$ applied perpendicular to the regenerators, as shown in \autoref{fig:amrmodel}.
+The magnetic profile is modeled by a waveform of magnetic field strength, $H(t)$, applied perpendicular to the regenerators, as shown in \autoref{fig:amrmodel}.
 The magnetic field is assumed uniform throughout the beds.
@@
 
-\noindent where the adiabatic temperature variation $\dtad$, a standard measure of the MCE, is calculated from \textcolor{black}{tabulated} experimental \textcolor{black}{data} for magnetocaloric materials as function of temperature and effective field.
+\noindent where the adiabatic temperature variation, $\dtad$, a standard measure of the MCE, is calculated from tabulated experimental data for magnetocaloric materials as function of temperature and effective field.
 \cite{bib:trevizoli16_perfor_model}.
@@
 
-The instantaneous profile (represented by the subscript ``IT'') and the rectified cosine profile (represented by ``RC'') are defined solely in terms of the \textcolor{black}{extreme} values $B\ped{min}$ and $B\ped{min}$, and are shown in \autoref{fig:itrc}.
+The instantaneous (square wave) profile (represented by the subscript ``IT'') and the rectified cosine profile (represented by ``RC'') are defined solely in terms of the extreme values $B\ped{min}$ and $B\ped{min}$, and are shown in \autoref{fig:itrc}.
 
@@
 
-A suitable approximation of the instantaneous profile is the \textcolor{black}{\emph{magnetic ramp profile}, shown} in \autoref{fig:ramp}, with finite transition times between the levels of constant magnetization.
-The magnetic profile oscillates  between a low value \({B}\ped{min}\) and a high value \({B}\ped{max}\), and \textcolor{black}{remains} at each plateau for a period of \(\tau\ped{M}\).
+A suitable approximation of the instantaneous profile is the \emph{magnetic ramp profile}, shown in \autoref{fig:ramp}, with finite transition times between the levels of constant magnetization.
+The magnetic profile oscillates  between a low value \({B}\ped{min}\) and a high value \({B}\ped{max}\), and remains at each plateau for a period of \(\tau\ped{M}\).
 The plateaus are balanced and centered at each half-cycle.
@@
 
-The \emph{ramp period} \(\tau\ped{R}\) \textcolor{black}{is} defined as:
+The \emph{ramp period} \(\tau\ped{R}\) is defined as:
 
@@
 
-\nomenclature[azt]{$\tau\ped{R}$}{ramp period in the \textcolor{black}{magnetic} ramp profile [\si{\second}]}
-\nomenclature[azt]{$\tau\ped{M}$}{magnetization period in the \textcolor{black}{magnetic} ramp  profile [\si{\second}]}
-\nomenclature[azo]{$\theta\ped{R}$}{ramp rate in the \textcolor{black}{magnetic} ramp profile}
+\nomenclature[azt]{$\tau\ped{R}$}{ramp period in the magnetic ramp profile [\si{\second}]}
+\nomenclature[azt]{$\tau\ped{M}$}{magnetization period in the magnetic ramp  profile [\si{\second}]}
+\nomenclature[azo]{$\theta\ped{R}$}{ramp rate in the magnetic ramp profile}
 
-The magnetization fraction, \(F\ped{M}\), is the fraction of the cycle \textcolor{black}{during which} the magnetocaloric material is \textcolor{black}{subjected to a} constant magnetic field:
+The magnetization fraction, \(F\ped{M}\), is the fraction of the cycle during which the magnetocaloric material is subjected to a constant magnetic field:
 
@@
 Additionally, the average values of the magnetic field during each half-AMR cycle are considered for comparison between profiles.
-The average magnetic profile during the hot cycle ($0 \le t < \nicefrac{\tau}{2}$) is denoted $\average{B}\ped{high}$ and the average during the cold cycle  ($ \nicefrac{\tau}{2} \le t < \tau$) is denoted $\average{B}\ped{low}$.
-For the instantaneous waveform, these average values are identical to the extrema values.
+The average magnetic profile during the hot cycle ($0 \le t < \nicefrac{\tau}{2}$) is denoted by $\average{B}\ped{high}$ and the average during the cold cycle  ($ \nicefrac{\tau}{2} \le t < \tau$) is denoted by $\average{B}\ped{low}$.
+For the instantaneous waveform, these average values are identical to the extreme values.
 
@@
 
-The fluid properties are considered constant in the momentum equation to decouple the solution \textcolor{black}{procedures to determine} the velocity and temperature fields.
-The properties are computed at the average temperature between the hot and cold sources temperatures, and are evaluated from interpolated tables exported from the EES software \cite{bib:klein13-ees}.
-In all simulations shown in this work, the heat transfer fluid is a mixture of water/ethylene-glycol with concentration \num{80}/\SI{20}{\percent} vol.
+The fluid properties are considered constant in the momentum equation to decouple the solution procedures to determine the velocity and temperature fields.
+The properties are computed at the average temperature between the hot and cold sources, and are evaluated from interpolation of tables imported from the EES software \cite{bib:klein13-ees}.
+In all simulations shown in this work, the heat transfer fluid is a \num{80}/\SI{20}{\percent} vol.~mixture of water/ethylene-glycol.
 For the energy equations, the fluid properties are also calculated from tabulated data, but the temperature dependence is considered.
 
-In this work, both single- and multilayer regenerators are considered.
+Both single- and multilayer regenerators are considered in this study.
 Single-layer regenerators are composed of gadolinium,  a benchmark material with a Curie temperature of \SI{290}{\kelvin}.
-\textcolor{black}{For simplicity, the solid} density is assumed constant at $\rho\ped{s} = \SI{7900}{\kg\per\cubic\meter}$ and the solid \textcolor{black}{thermal} conductivity is set to $k\ped{s} = \SI{10.5}{\watt\per\meter\per\kelvin}$.
-The specific heat \textcolor{black}{capacity} of \ce{Gd} is calculated as a function of temperature and magnetic field based on experimental \textcolor{black}{data}, using a bi-linear interpolation scheme; more details on the experimental dataset \textcolor{black}{are available} in \cite{bib:trevizoli16_perfor_model}.
+For simplicity, the solid density is assumed constant at $\rho\ped{s} = \SI{7900}{\kg\per\cubic\meter}$ and the solid thermal conductivity is set to $k\ped{s} = \SI{10.5}{\watt\per\meter\per\kelvin}$.
+The specific heat capacity of \ce{Gd} is calculated as a function of temperature and magnetic field based on experimental data, using a bi-linear interpolation scheme; more details on the experimental dataset are available in \cite{bib:trevizoli16_perfor_model}.
 
 For the multilayer simulations, alloys of gadolinium and yttrium are used in the form \ce{Gd_{1-x}Y_x}, where $x$ is the yttrium fraction.
-\textcolor{black}{This fraction} decreases the Curie temperature  \textcolor{black}{of the} alloy relative to that of pure gadolinium.
-Due to the lack of experimental  \textcolor{black}{data on the magnetocaloric properties of} \ce{Gd_{1-x}Y_x} alloys at the time \textcolor{black}{this analysis was made}, a simpler approach was used \textcolor{black}{in which} the properties of alloys with {a} low yttrium fraction are \textcolor{black}{identical to those} of pure gadolinium, except for the Curie temperature \textcolor{black}{(which is shifted to lower values)}.
+This fraction reduces the Curie temperature of the alloy relative to that of pure gadolinium.
+Due to the lack of experimental  data on the magnetocaloric properties of \ce{Gd_{1-x}Y_x} alloys at the time this analysis was made, a simpler approach was used in which the \textcolor{blue}{dependence of magnetization, specific heat capacity and entropy with respect to the magnetic field for} alloys with a low yttrium fraction are identical to those of pure gadolinium, \textcolor{blue}{but are shifted to a lower} Curie temperature (corresponding to the yttrium fraction).
+
+\colorbox{yellow}{Fabio, veja se o texto acima estah ok...}
 
@@
 
-The AMR model considers only one bed and assumes $N\ped{r}$ identical beds experience the same cycle, multiplying the performance metrics below by this factor.
+The AMR model is solved for only one bed, but  assumes that the $N\ped{r}$ identical beds experience the same cycle. Thus, the extensive performance parameters are multiplied by that factor.
 
@@
 
-The magnetic power to operate the AMR cycle is modeled as the ideal Carnot power, ignoring most thermal irreversibilities:
+\textcolor{blue}{As pointed out in \colorbox{yellow}{citar o paper da ATE - Design trade-offs}, since external sources of irreversibility (e.g., heat transfer with a finite temperature difference in the heat exchangers) are ignored and no eddy currents and hysteresis losses are present,} the magnetic power required to \textcolor{blue}{magnetize the solid refrigerant and produce the MCE} in the AMR cycle is given by the product of the Carnot efficiency and the cooling capacity as follows:
 
@@
 
-\noindent while the fluid friction irreversibility is accounted for in the calculation of the pumping power:
+Irreversibility due to fluid friction is accounted for in the calculation of the pumping power:
 
@@
 
-The hydraulic system to modulate the fluid flow through different regenerators at different time instants is composed of a pump and a set of electronic valves which can be precisely controlled to yield the desired blow durations.
+The hydraulic system designed to modulate the fluid flow through different regenerators at different time instants is composed of a pump and a set of electronic valves which can be precisely controlled to yield the desired blow durations.
 The electrical power consumed by the valve array is computed separately from other work contributions.
@@
 
-Due to evolving developments in our group, two types of valves are considered, as will be elaborated in \autoref{sec:results-discussions}.
+\colorbox{yellow}{Fabio, a ultima frase do paragrafo acima nao  cabe aqui... quero dizer que a aplicacao deveria ter sido discutida na revisao bibliografica, a qual precisa ser expandida}
 
-The first approach, called \emph{Type B valves}, uses the  model \textcolor{black}{of} \cite{bib:cardoso16_trans}, assuming that the individual consumption of each valve is independent of frequency and blow fraction.
+%Due to evolving developments in our group, two types of valves are considered, as will be elaborated in \autoref{sec:results-discussions}.
+
+In the present analysis, two types of valves are considered.
+In the first approach, called \emph{Type B valves}, the  model proposed in Ref.~\cite{bib:cardoso16_trans} is used, assuming that the individual consumption of each valve is independent of frequency and blow fraction.
 The valve power  $\wvalve$ can be computed as:
+
+\colorbox{yellow}{da mesma forma, o trabalho \cite{bib:cardoso16_trans} tem que constar da revisao bibliografica...}
+
+\colorbox{yellow}{fica estranho o \textbf{primeiro} approach ser Type B e o \textbf{segundo} ser Type A...}
 
@@
 
-Equation~\eqref{eq:198} was correlated for blow fractions of \num{50} and \SI{100}{\percent} and for frequencies in the range \textcolor{black}{of} \num{0.2}--\SI{1.6}{\hertz}, with an uncertainty \textcolor{black}{on} the order of \SI{0.4}{\watt} for a single valve.
+\colorbox{yellow}{A equacao acima precisa ser melhor contextualizada.
+Talvez os revisores pecam para dar uma descricao minima do experimento.
+Uma saida para nao ter que fazer isso seria revisar na introducao o trabalho nosso que mediu e propos a correlacao (foi o do Pedroca)  }
+
+Equation~\eqref{eq:198} was correlated for blow fractions of \num{50} and \SI{100}{\percent} and frequencies in the range of \num{0.2}--\SI{1.6}{\hertz}, with an uncertainty on the order of \SI{0.4}{\watt} for a single valve.
 The use of different valve types will be discussed among the presented results.
 
-Indepedent of the valve type used, it is also assumed that this valve system can produce the fluid flow profile \textcolor{black}{shown in} \autoref{fig:mprofile}, where the displaced fluid mass during one blow in one regenerator bed is $\rate{m}\ped{f,max} F\ped{B} \nicefrac{\tau}{2}$.
+Independent of the valve type used, it is also assumed that each valve system can produce the fluid flow profile shown in \autoref{fig:mprofile}, where the displaced fluid mass during one blow in one regenerator bed is $\rate{m}\ped{f,max} F\ped{B} \nicefrac{\tau}{2}$.
 The \emph{utilization factor} can then be calculated as:
@@
 \nomenclature[bf]{$\Phi$}{utilization factor}
-\noindent and in all results shown in this work, the number of valves is \textcolor{black}{calculated as}:
+\noindent and in all results shown in this work, the number of valves is calculated as:
 
@@
 
-The coefficient of performance \textcolor{black}{takes} the cooling capacity as \textcolor{black}{the main} output \textcolor{black}{parameter from} the AMR model, \textcolor{black}{in addition to} all previously cited power contributions:
+The coefficient of performance takes the cooling capacity as the main output parameter from the AMR model, in addition to all previously cited power contributions:
 
@@
 
-The analysis of magnetic profiles was performed in two different stages in the research of our group, as discussed below.
+The analysis of magnetic profiles was performed at two different stages.
+Initially, the instantaneous (square-wave) and the rectified cosine profiles are compared using a simpler approach (i.e., neglecting casing losses).
+Later, based on the selection of the most promising magnetic profile, a more in-depth analysis is carried out to determine the optimal geometric and operating parameters of the AMR system.
 
@@
 
-In the first stage, the instantaneous and rectified cosine profiles are compared in the AMR model, considering monolayer regenerators without casing losses, and using Type B valves.
+At the first stage of the present analysis, the instantaneous and rectified cosine profiles are compared considering a single-layer regenerator  without casing losses, using Type B valves.
 The parameters used in all simulations are presented in \autoref{tab:params-cobem}.
@@
   \centering
-  \caption{AMR parameters kept fixed in the simulations with different magnetic profiles}
+  \caption{AMR parameters kept fixed in the simulations with different magnetic profiles \colorbox{yellow}{Fabio, acho que as variaveis nao foram apresentadas na lista de simbolos}}
   \begin{tabular}{c|c}
@@
 
-When comparing the \textcolor{black}{performances resulting from the application of the different} magnetic profiles, the average magnetic field during the hot cycle \textcolor{black}{will be considered} the same; this implies a higher peak for the rectified cosine.
-For the cold cycle,  the minimum values for both profiles is the same, as shown in \autoref{fig:comparison-methods-profiles}.
-\textcolor{black}{For} reference, in all simulations,  the minimum value for the rectified cosine was fixed at ${B}\ped{min} = \SI{0.1}{\tesla}$.
+When comparing the performances resulting from the application of the different magnetic profiles, the same average magnetic field during the hot cycle will be considered; this implies a higher peak for the rectified cosine.
+For the cold cycle, the minimum values for both profiles are the same, as shown in \autoref{fig:comparison-methods-profiles}.
+For reference, in all simulations,  the minimum value for the rectified cosine was fixed at ${B}\ped{min} = \SI{0.1}{\tesla}$.
 
@@
 \includegraphics[width=8cm]{profiles_it_and_rc_same_minimum}
-  \caption{Configuration of average and extrema values of the instantaneous and rectified cosine profiles }
+  \caption{Configuration of average and extreme values of the instantaneous and rectified cosine profiles }
   \label{fig:comparison-methods-profiles}
@@
 
-Simulations were \textcolor{black}{carried out} for various values of blow fraction; the rectified cosine profile can benefit from a smaller blow fraction because this can concentrate the flow during the periods of very high or low fields.
+Simulations were carried out for various values of blow fraction.
+The rectified cosine profile can benefit from a smaller blow fractions that concentrate the flow during the periods of very high and very low fields.
 In this section, all results use the critical value of blow fraction that maximized the cooling capacity: fluid flowing during the entire period for the instantaneous profile, and only during \SI{60}{\percent} of the period (the smallest blow fraction tested) for the cosine profile; this latter case is shown in \autoref{fig:cos-inst-60}.
@@
 Figure~\ref{fig:cos_ins} shows the cooling capacity attained by the device at a frequency of \SI{1}{\hertz} and different utilizations.
-The horizontal axis shows the average value during the high field region.
-The instantaneous profile almost always yields a higher performance, and cince the average \textcolor{black}{field} during the hot cycle (high field stage) is the same, the main difference is due to the low magnetic field levels.
-For the ``same minimum'' comparison, the instantaneous profile is capable of keeping the magnetic field at low levels for the whole half-cycle, which is beneficial for performance;  for $\Phi=1.0$ and $B\ped{high} = \SI{1.40}{\tesla}$, the cooling capacity for the instantaneous profile is $\SI{196.3}{\percent}$ higher than for the cosine profile.
+The horizontal axis shows the average field value during the high field region.
+The instantaneous profile almost always yields a higher performance, and since the average field during the hot cycle (high field stage) is the same, the main difference is due to the low magnetic field levels.
+For the ``same minimum'' comparison, the instantaneous profile is capable of keeping a low magnetic field over the entire half-cycle, which is beneficial for performance;  for $\Phi=1.0$ and $B\ped{high} = \SI{1.40}{\tesla}$, the cooling capacity for the instantaneous profile is $\SI{196.3}{\percent}$ higher than for the cosine profile.
 As demonstrated by \cite{bib:asme-mce}, a higher average magnetic field during the low-field stage increases the solid temperature and consequently results in  warmer fluid entering the cold heat exchanger, representing a thermal loss.
@@
 
-The only exception in this comparison  is seen for the lowest utilization of $\Phi = 0.2$, where the performance is slightly better for the RC profile.
-Since the blow fraction for the cosine is lower, the mass flow rate \textcolor{black}{is} higher \textcolor{black}{in the latter for} the same utilization (cf.
+The only exception in this comparison is observed for the lowest utilization of $\Phi = 0.2$, where the performance is slightly better for the RC profile.
+Since the blow fraction for the cosine is smaller, the mass flow rate is higher in the latter for the same utilization (cf.
 Eq.~\eqref{eq:200}).
-\textcolor{black}{This} increases \textcolor{black}{the} heat transfer rate, as previously explained ---  outweighing the effects of the magnetic field.
+This increases the heat transfer rate, as previously explained ---  outweighing the effects of the magnetic field.
 
-The same analysis, but in terms of the coeficient of performance, is shown in \autoref{fig:cos_ins_cop}, where it can be seen that the instantaneous profile yields better results for medium to high levels of utilization.
-This is due to some phenomena shown in \autoref{fig:cos_ins_w} for a fixed utilization of 0.6: the magnetic power only change between profiles due to variations in cooling capacity; the valve power is higher for the IT profile since the valves must remain open for longer periods; but the proportional increase in pumping power, due to larger flow rate, is even higher (than the change in valve power).
+The same analysis, but in terms of the coefficient of performance, is shown in \autoref{fig:cos_ins_cop}, where  the instantaneous profile yields better results for medium to high levels of utilization.
+This is explained by the behavior of the magnetic, valve and pumping power shown in   \autoref{fig:cos_ins_w} for a fixed utilization of 0.6.
+As can be seen, the magnetic power only differs between the profiles due to changes in cooling capacity.
+Also, the valve power is higher for the instantaneous profile since the valves must remain open for longer periods.
+However, the proportional increase in pumping power, due to arger larger flow rates, is even higher (than the change in valve power).
 
@@
 \includegraphics[width=7cm]{COP_B_comp_f_1_same_minimum}
-  \caption{Coefficient of performance as a function of the  average high magnetic field, for different utilizations.
-\textcolor{black}{``IT''}: instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}).}
+  \caption{Coefficient of performance as a function of the  average high magnetic field, for different values of utilization.
+``IT'': instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}).}
  \label{fig:cos_ins_cop}
@@
   \caption{Power contributions as functions of the average high magnetic field, for a utilization of 0.6.
-\textcolor{black}{``IT''}: instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}).}
+``IT'': instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}).}
   \label{fig:cos_ins_w}
@@
 
-In general, considering the goal of achieving target requirements for the cooling capacity, AMRs operating with the instantaneous magnetic profile \textcolor{black}{generate} better \textcolor{black}{performance} results.
-As can be seen \textcolor{black}{in} Fig.~\ref{fig:cos_ins}, an instantaneous profile with the lowest possible value of $B\ped{min}$ and the highest possible value of $B\ped{max}$, with a flow profile occupying the whole cycle with average values of utilization, results in the highest values of cooling capacity among all simulations.
+In general, considering target values for the cooling capacity, AMRs operating with the instantaneous magnetic profile lead to better performance results.
+As can be seen in Fig.~\ref{fig:cos_ins}, an instantaneous profile with the lowest possible value of $B\ped{min}$ and the highest possible value of $B\ped{max}$, with a flow profile occupying the whole cycle with average values of utilization, results in the highest values of cooling capacity among all simulations.
 
-The rectified cosine profile, found in compact systems using Halbach arrays, can \textcolor{black}{surely} benefit from reducing the blow fraction, both in terms of cooling capacity and temperature span.
-However, for the typical parameters \textcolor{black}{evaluated} in this Thesis, even if the blow fraction is optimized for the ``RC'' profile, the ``IT'' profile still yields better results.
+The rectified cosine profile, found in compact systems using Halbach arrays, can surely benefit from reducing the blow fraction, both in terms of cooling capacity and temperature span.
+However, for the typical parameters evaluated in this paper, even if the blow fraction is optimized for the ``RC'' profile, the ``IT'' profile still gives better results.
 
@@
 
-As shown in the previous section, the instantaneous profile \textcolor{black}{generally} yields the highest values \textcolor{black}{of} cooling capacity.
-Therefore, in this section, a more detailed analysis of \textcolor{black}{this} profile has been carried out, \textcolor{black}{where the} maximum field  \textcolor{black}{is} varied, while the minimum value is kept at \SI{0.05}{\tesla}.
-Figure~\ref{fig:qc_phi_inst} shows the cooling capacity as a function of \textcolor{black}{the} utilization, for several levels of the maximum magnetic field \textcolor{black}{and} two different operating frequencies.
-Because of the conflict between a low heat transfer rate for flow rates \textcolor{black}{that are} too low and losses in regenerator effectiveness in flow rates \textcolor{black}{that are} too high, there are critical values of utilization that maximize \textcolor{black}{the} cooling capacity, and this critical values increase with the magnetic field.
-\textcolor{black}{For} higher magnetic fields, the increase in the MCE surpasses the loss of effectiveness, and one can go to higher flow rates without losing performance.
-It can also be seen in Fig.~\ref{fig:qc_phi_inst} that at  higher frequencies the values of cooling power are higher, and also the critical values of utilization are lower; however, this \textcolor{black}{is} usually achieved at the \textcolor{black}{expense} of \textcolor{black}{a} higher power consumption in AMR devices at higher frequencies \cite{bib:lei15_study,NIKNIA2016601}.
+As shown in the previous section, the instantaneous profile generally yields the highest values of cooling capacity.
+Therefore, in this section, a more detailed analysis of this profile is carried out, where the maximum field is varied, but the minimum value is kept at \SI{0.05}{\tesla}.
+Figure~\ref{fig:qc_phi_inst} shows the cooling capacity as a function of the utilization, for several levels of the maximum magnetic field and two different operating frequencies.
+Because of the conflict between a low heat transfer rate for flow rates that are too low and losses in regenerator effectiveness in flow rates that are too high, there are critical values of utilization that maximize the cooling capacity, and these critical values increase with the magnetic field.
+For higher magnetic fields, the increase in the MCE surpasses the loss of effectiveness, and one can go to higher flow rates without losing performance.
+It can also be seen in Fig.~\ref{fig:qc_phi_inst} that at  higher frequencies the values of cooling power are higher, and also the critical values of utilization are lower.
+However, this is usually achieved at the expense of a higher power consumption in AMR devices at higher frequencies \cite{bib:lei15_study,NIKNIA2016601}.
 
@@
   \subfloat[$f = \SI{2}{\hertz}$]{\includegraphics[width=8cm]{Qc_Phi_inst_f_2_Hmin_005_FB_100}\label{fig:Qc_phi_inst_2}}
-  \caption{Cooling capacity as a function of utilization, for various values of the high magnetic field  \textcolor{black}{for} the instantaneous profile}
+  \caption{Cooling capacity as a function of utilization, for various values of the high magnetic field  for the instantaneous profile}
   \label{fig:qc_phi_inst}
@@
   \subfloat[Coefficient of performance]{\includegraphics[width=9cm]{COP_H_inst_f_1_Phi_40}\label{fig:COP_H_inst_f_1_Phi_40}}
-  \caption{Performance metrics as a function of \textcolor{black}{the} regenerator height (all other parameters \textcolor{black}{were set as in} Table~\ref{tab:params-cobem}, \textcolor{black}{for}  utilization factor of 0.4) for various values of the high magnetic field of the instantaneous profile}
+  \caption{Performance metrics as a function of the regenerator height (all other parameters were set as in Table~\ref{tab:params-cobem}, for utilization factor of 0.4) for various values of the high magnetic field of the instantaneous profile}
 \label{fig:Qc_H_inst}
@@
 
-The geometric parameters in \autoref{tab:params-cobem} were chosen from preliminary simulations, \textcolor{black}{so} they are not  optimal.
-To understand the impact of \textcolor{black}{the} regenerator geometry on the performance with the instantaneous profile, the regenerator height was varied in Fig.~\ref{fig:Qc_H_inst}, and all other parameters from \autoref{tab:params-cobem} were kept fixed and with $\phi=0.4$.
-As expected, higher magnetic fields allow for smaller regenerators (hence more compact systems) to achieve a \textcolor{black}{desired} cooling capacity.
-For instance, to achieve a capacity of \SI{100}{\watt}, increasing the field from \num{1.0} to \SI{1.2}{\tesla} \textcolor{black}{results} in regenerators \textcolor{black}{that are} \SI{36}{\percent} smaller.
-Comparing results \textcolor{black}{for} cooling capacity and coefficient of performance, the trends are largely the same, as the former is more sensitive to variations in the magnetic field and regenerator height than the components of power.
+The geometric parameters in \autoref{tab:params-cobem} were chosen from preliminary simulations, so they are not  optimal.
+To understand the impact of the regenerator geometry on the system performance with the instantaneous profile, the regenerator height was varied in Fig.~\ref{fig:Qc_H_inst}, and all other parameters from \autoref{tab:params-cobem} were kept fixed and with $\phi=0.4$.
+As expected, higher magnetic fields allow for smaller regenerators (hence more compact systems) to achieve a desired cooling capacity.
+For instance, to achieve a capacity of \SI{100}{\watt}, increasing the field from \num{1.0} to \SI{1.2}{\tesla} results in regenerators that are \SI{36}{\percent} smaller.
+Comparing the results for the cooling capacity and coefficient of performance, the trends are largely the same, as the former is more sensitive to variations in the magnetic field and regenerator height than the components of power.
 
@@
 
-Based on the better performance of the instantaneous profile, the ramp profile is assumed as a suitable target profile for the design of magnetic refrigerators, and will be analyzed in this section, representing the second stage in the analysis of magnetic profiles.
+Based on the better performance of the instantaneous profile, the ramp profile is a naturally suitable target profile for the design of magnetic refrigerators, and will be analyzed in this section, representing the second stage in the analysis of magnetic profiles.
 
 Moving towards a more realistic model, casing losses are included, using the model from \cite{bib:trevizoli16_perfor_model}.
-The bed is enclosed in a solid casing of thickness $h\ped{csg}$, and two air layers of thickness $h\ped{air}$ separate \textcolor{black}{the AMR and its casing} from the inner and outer \textcolor{black}{magnet} cylinders, as shown in \autoref{fig:amr-casing}.
-These magnetic cylinders can be designed to yield the desired magnetic profiles, as will be shown in future studies by our group.
+The bed is enclosed in a solid casing of thickness $h\ped{csg}$, and two air layers of thickness $h\ped{air}$ separate the AMR and its casing from the inner and outer magnet cylinders, as shown in \autoref{fig:amr-casing}.
+The optimal design of such magnetic cylinders aiming at a particular magnetic profile  will be the subject of future publications.
 
@@
 
-Preliminary analyses \textcolor{black}{carried out by} \cite{bib:peixer17-perfor-amrs} showed that a stainless steel casing \textcolor{black}{with a} thickness \textcolor{black}{of} $h\ped{csg} = \SI{0.5}{\mm}$ is thick enough to ensure mechanical integrity and easy manufacturing, while being thin enough to accommodate the material \textcolor{black}{with a low} thermal conductivity.
+Preliminary analyses carried out by \cite{bib:peixer17-perfor-amrs} showed that a stainless steel casing with a thickness of $h\ped{csg} = \SI{0.5}{\mm}$ is thick enough to ensure mechanical integrity and easy manufacturing, while being thin enough to accommodate the material with a low thermal conductivity.
 
-In addition, \textcolor{black}{in the present study}, an air gap clearance thickness was set at $h\ped{air} = \SI{1}{\mm}$.
-This value \textcolor{black}{gave rise to a} peak in cooling capacity due to the compromise between minimizing losses and maximizing the magnetocaloric mass.
+In addition, in the present study, an air gap clearance thickness was set at $h\ped{air} = \SI{1}{\mm}$.
+This value gave rise to a peak in cooling capacity due to the compromise between minimizing losses and maximizing the magnetocaloric mass.
 The thermophysical properties of stainless steel and air were also obtained with interpolation of tables exported by the EES software \cite{bib:klein13-ees}.
@@
  Figure~\ref{fig:ramp-inst} shows the two profiles that will be used in this section and how they are synchronized.
-Regarding the magnetic profile, the \textcolor{black}{magnitude of the} high value will be varied to investigate the performance of the AMR system, while the minimum will be kept at $\bmin = \SI{0.05}{\tesla}$.
+Regarding the magnetic profile, the magnitude of the high value will be varied to investigate the performance of the AMR system, while the minimum will be kept at $\bmin = \SI{0.05}{\tesla}$.
 
@@
 
-\subsubsection{Performance curves for varying blow and magnetization fractions}
+\subsubsection{Performance curves for variable blow and magnetization fractions}
 \label{sec:perf-curv-vary}
 
-Figure~\ref{fig:Qc_COP_curves_phi40} shows the cooling capacity and coefficient of performance of the AMR system for a fixed utilization factor of \num{0.4} and for a magnetic profile with \textcolor{black}{a} maximum at \SI{1.3}{\tesla}, for \textcolor{black}{variable} blow and magnetization fractions.
-\textcolor{black}{To facilitate the analysis, the} results are plotted in terms of the ratio $\nicefrac{F\ped{M}}{F\ped{B}}$, with curves for different \textcolor{black}{values of} $F\ped{B}$.
-It is clear \textcolor{black}{that both the cooling capacity and the coefficient of performance exhibit a peak at} $F\ped{M} = F\ped{B}$.
-Moreover,  \textcolor{black}{to the right of the peak, i.e., for higher values of $F\ped{M}$, the}  reduction \textcolor{black}{of} both \textcolor{black}{performance} metrics \textcolor{black}{is} slower, meaning it is better to have a magnetization plateau wider than the fluid flow plateau
+Figure~\ref{fig:Qc_COP_curves_phi40} shows the cooling capacity and coefficient of performance of the AMR system for a fixed utilization factor of \num{0.4} and for a magnetic profile with a maximum at \SI{1.3}{\tesla}, for variable blow and magnetization fractions.
+To facilitate the analysis, the results are plotted in terms of the ratio $\nicefrac{F\ped{M}}{F\ped{B}}$, with curves for different values of $F\ped{B}$.
+It is clear that both the cooling capacity and the coefficient of performance exhibit a peak at $F\ped{M} = F\ped{B}$.
+Moreover, to the right of the peak, i.e., for higher values of $F\ped{M}$, the reduction of both performance metrics is slower, meaning it is better to have a magnetization plateau that is wider than the fluid flow plateau.
 
-The reduction in performance for $F\ped{M} > F\ped{B}$ \textcolor{black}{can be explained by an increase in} heat leakage through the casing, as the solid begins to lose energy to the environment \textcolor{black}{when} the fluid is not flowing.
+The reduction in performance for $F\ped{M} > F\ped{B}$ can be explained by an increase in heat leakage through the casing, as the solid begins to lose energy to the environment when the fluid is not flowing.
 For $F\ped{M} < F\ped{B}$,  the fluid begins to flow when the solid is not totally warmed up, losing effectiveness.
@@
 
-The influence of utilization is demonstrated in \autoref{fig:Qc_curves_ramp_phi}, where the cooling capacity \textcolor{black}{is} plotted for different utilization factors.
+The influence of the utilization is demonstrated in \autoref{fig:Qc_curves_ramp_phi}, where the cooling capacity is plotted for different utilization factors.
 For increasing $\Phi$ in this range, not only do the overall values of cooling capacity increase, but also the importance of choosing the blow fraction becomes clearer.
-In \textcolor{black}{these ranges} of utilization and blow fraction,  the cooling capacity increases because the higher transfer rate associated with higher flow rates \textcolor{black}{dominates} over the loss of regenerator effectiveness.
+In these ranges of utilization and blow fraction,  the cooling capacity increases because the higher transfer rate associated with higher flow rates dominates over the loss of regenerator effectiveness.
 
@@
 
-The \textcolor{black}{above} results can be \textcolor{black}{evaluated from} another point of view with \autoref{fig:COP_maps_ramp_FM}, where the coefficient of performance is plotted as contour levels.
-This type of map is useful because, since $\bmin$ and $\tau$ are fixed, each point in this graph completely characterizes a magnetic \textcolor{black}{ramp} profile, and each subplot with fixed $\Phi$ and $F\ped{B}$ characterizes the fluid flow profile.
-As expected, the performance increases for the higher values both $\bmax$ and $F\ped{M}$, where the  magnetic \textcolor{black}{ramp} profile tends to the instantaneous magnetic profile with a large amplitude.
+The above results can be evaluated from another point of view with \autoref{fig:COP_maps_ramp_FM}, where the coefficient of performance is plotted as contour levels.
+This type of map is useful because, since $\bmin$ and $\tau$ are fixed, each point in this graph completely characterizes a magnetic ramp profile, and each subplot with fixed $\Phi$ and $F\ped{B}$ characterizes the fluid flow profile.
+As expected, the performance increases for the higher values both $\bmax$ and $F\ped{M}$, where the  magnetic ramp profile tends to the instantaneous magnetic profile with a large amplitude.
 Confirming the previous trends, the results are less sensitive to the magnetization fraction when $F\ped{M} \ge F\ped{B}$.
@@
 
-\subsubsection{Geometric analysis of the regenerators using the ramp magnetic profile}
+\subsubsection{Geometric analysis of the regenerators using the magnetic ramp profile}
 \label{sec:geom-analys-regen}
 
-\textcolor{black}{All} previous results assumed a fixed regenerator geometry, with the goal of identifying the optimal fluid and magnetic profile parameters.
-\textcolor{black}{It became clear that the} magnetization fraction should be as large as possible, but that raises some challenges in realizing abrupt changes in the magnetic field.
-The value of $F\ped{M} = \SI{70}{\percent}$ is then chosen as a compromise, with \textcolor{black}{a corresponding} $F\ped{B} = F\ped{M}$.
-The mean value of \textcolor{black}{the} utilization factor of $\Phi = 0.4$ is also chosen as reference in the next results.
+All previous results assumed a fixed regenerator geometry, with the goal of identifying the optimal fluid and magnetic profile parameters.
+It became clear that the magnetization fraction should be as large as possible, but that raises some challenges in realizing abrupt changes in the magnetic field.
+The value of $F\ped{M} = \SI{70}{\percent}$ is then chosen as a compromise, with a corresponding $F\ped{B} = F\ped{M}$.
+The mean value of the utilization factor of $\Phi = 0.4$ is also chosen as reference in the next results.
 
 Figure~\ref{fig:qc-cop-eta-amr-height} shows the cooling capacity, coefficient of performance and second-law efficiency for varying magnetic field and regenerator height.
-\textcolor{black}{As} expected, larger regenerators can \textcolor{black}{produce} the desired performance with lower magnetic fields.
+As expected, larger regenerators can produce the desired performance with lower magnetic fields.
 It can also be seen that this configuration for an AMR system can achieve values of $\etasec$ compatible with conventional vapor compression systems \cite{HERMES20081341,NEGRAO20113051}, although these numerical results do not include mechanical losses.
@@
 
-\section{Final considerations}
+\section{Conclusions}
 \label{sec:final-considerations}
@@
 To the authors' knowledge, this is the first study where magnetic profiles for AMR model are mathematically modeled and the model parameters are changed in a systematic way.
-The instantaneous, rectified cosine and ramp magnetic profiles were implemented in an AMR model, and the profile parameters were varied simultaneously with regenerator geometric parameters.
+The instantaneous (square wave), rectified cosine and ramp magnetic profiles were implemented in an AMR model, and the profile parameters were varied simultaneously with the regenerator geometric parameters.
 These waveforms can be found in existing MR devices published in the literature.
 
-Using a simplified model, the instantaneous profile yields higher cooling capacity, even by reducing the blow fraction on rectified cosine, at least up to levels achieved by pumping and valving systems; further reductions of the blow fraction is mainly restricted by valve opening times.
-This means that, even if sinusoidal profiles can be obtained with more compact magnetic circuit systems, the performance of MR systems can be maximized by using instantaneous variations of the magnetic field, and then optimizing the regenerator height and blow duration.
+Using a simplified model, the instantaneous profile resulted in a higher cooling capacity, even by reducing the blow fraction on rectified cosine, at least up to levels achieved by pumping and valving systems; further reductions of the blow fraction is mainly restricted by valve opening times.
+This means that, even if sinusoidal profiles can be obtained with more compact magnetic circuit systems, the performance of magnetic refrigeration systems can be maximized by using instantaneous variations of the magnetic field, and then optimizing the regenerator height and blow duration.
+\colorbox{yellow}{Fabio, tive dificuldade em entender o que voce quis concluir neste paragrafo...
+talvez seja uma boa tentar expandir seu conteudo}
 
-The ramp profile is a feasible approximation for the instantaneous
-profile without abrupt changes in the magnetic field plateaus.
+The ramp profile is a feasible approximation for the instantaneous profile without abrupt changes in the magnetic field plateaus.
 This waveform can be optimized for increasing cooling capacity, in particular by synchronizing the plateau durations between fluid and magnetic profiles.
+\colorbox{yellow}{Fabio, acho que seria bom trazer alguns dados quantitativos para ca, tipo ganhos percentuais etc.}
 
-\begin{acknowledgements}
-The authors duly acknowledge the financial support from CNPq (Grant no. 443696/2014-4), Capes (PTI program, Process no. 88887.194773/2018-00), Embraco and the EMBRAPII Unit Polo/UFSC.
-\end{acknowledgements}
+\section*{Conflict of Interest Statement}
+
+There is no actual or potential conflict of interest including any financial, personal or other relationships with other people or organizations that could inappropriately influence, or be perceived to influence, the present work.
+
+\acknowledgement{This work was funded by the Brazilian Federal Government (CAPES PTI program, Process no.
+88887.194773/2018-00, CNPq Grant no.
+443696/2014-4 and EMBRAPII) and by the State of Santa Catarina (FAPESC/INCT).
+The authors acknowledge the continuous support from Embraco.
+}
 
@@
 %\bibliographystyle{spmpsci}      % mathematics and physical sciences
-\bibliographystyle{spphys}       % APS-like style for physics
+\bibliographystyle{unsrtnat}
+%\renewcommand{\refname}{}
+%\bibliographystyle{spphys}       % APS-like style for physics
 

### 2019-10-22 PaperMagneticProfiles_JBSMSE.tex
Begin developing literature review.

@@
 \thanks{
-An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}).
+An abridged version of this manuscript was presented at the 24th ABCM International Congress of Mechanical Engineering (COBEM 2017), held in Curitiba, PR, Brazil, in December 2017.
 }}
@@
 
-A typical AMR cycle is comprised of the following steps: (i) The magnetic circuit magnetizes the MCM, thereby increasing its temperature due to the MCE; (ii) During the \emph{cold blow}, cold fluid previously in thermal contact with the low-temperature source flows through the warm bed, absorbs its energy and releases it as heat to the high-temperature sink through the hot heat exchanger; (iii) The MCM is demagnetized and coold down as a result; (iv) As the fluid flow is reversed (\emph{hot blow}), it releases energy to the bed, decreases its temperature so it can absorb the thermal load at the cold heat exchanger in contact with the low-temperature source.
+A typical AMR cycle is comprised of the following steps: (i) The magnetic circuit magnetizes the MCM, thereby increasing its temperature due to the MCE; (ii) During the \emph{cold blow}, cold fluid previously in thermal contact with the low-temperature source flows through the warm bed, absorbs its energy and releases it as heat to the high-temperature sink through the hot heat exchanger; (iii) The MCM is demagnetized and cooled down as a result; (iv) As the fluid flow is reversed (\emph{hot blow}), it releases energy to the bed, and decreases its temperature so it can absorb the thermal load at the cold heat exchanger in contact with the low-temperature source.
 Different cycles can be devised by changing the duration and synchronization  between the two cycle \emph{characteristic waveforms}:
@@
 
-In contrast, because of the complexities involved in designing and fabricating magnetic circuits, the applied magnetic field profiles (or simply the magnetic waveforms) are much less studied.
-Magnetic waveforms are usually investigated in terms of their synchronization with the fluid flow profile \cite{TUSEK20111507,bib:bjoerk11_amr}.
+In contrast, because of the complexities involved in designing and fabricating magnetic circuits, the applied magnetic field profiles (or simply the magnetic waveforms) are much less studied, and are usually investigated in terms of their synchronization with the fluid flow profile.
+Considering a trapezoidal magnetic profile and a square fluid flow waveform, a numerical analysis showed that small delays between the increase of the magnetic field and the start of the fluid flow is beneficial for the cooling capacity, to assure the solid is fully magnetized before the fluid starts transfering energy from it \citet{bib:bjoerk11_amr}.
+If this delay is further increased so that the fluid flow period can coincide with diferent stages of the magnetic profile, different thermodynamic cycles can be obtained with different performance trends; the Brayton AMR cycle (explained previously) yields the highest cooling capacities, while the Ericsson AMR cycle (with isothermal (de)magnetization steps) yield the highest values of the coefficient of performance \cite{bib:plaznik13-numer}.
+This conclusion was confirmed by the more extensive numerical analysis of \cite{bib:kitanovski}, which also varied the amplitude of the trapezoidal magnetic profile and proposed magnetic circuit designs which could generate these profiles.
+
 \colorbox{yellow}{acho q cabe explicar brevemente o que os trabalhos de \cite{TUSEK20111507} e \cite{bib:bjoerk11_amr} fizeram...}.

### 2019-11-01 PaperMagneticProfiles_JBSMSE.tex
Conclude reivision of introduction.

@@
 The magnitude of the MCE depends on  material properties, magnetic field variation and temperature, and it is maximum at the Curie temperature of the material \cite{bib:smith-magneto, bib:kitanovski}.
-Applications of the MCE at near room-temperature are not restricted to cooling applications; it can also be applied to the development of thermomagnetic motors \cite{bib:kaneko}.
+Applications of the MCE at near room-temperature are not restricted to cooling applications \cite{bib:gimaev19-review-htsc,bib:greco19}; it can also be applied to the development of thermomagnetic motors \cite{bib:kaneko19-desig}.
 
@@
 
-For operating temperatures typical of household cooling applications, the MCE is of the order of \num{2}-\SI{5} K/T.
+For operating temperatures typical of household cooling applications, the MCE is of the order of \num{2}-\SI{5}{\kelvin\per\tesla}.
 To amplify this temperature change, heat regeneration is usually employed \cite{bib:kitanovski}.
@@
 
-Fluid flow profiles can be more easily investigated  experimentally, as no changes in the fluid flow hardware are required.
+Fluid flow profiles can be more easily investigated  experimentally, as no changes in the fluid flow hardware are required, provided a reliable and flexible valving system is in place.
 In particular, the effect of the \emph{duration} of the fluid blows has been extensively investigated \cite{bib:teyber17_exper,bib:nakashima18-influen-exp,FORTKAMP2018}.
@@
 
-In contrast, because of the complexities involved in designing and fabricating magnetic circuits, the applied magnetic field profiles (or simply the magnetic waveforms) are much less studied, and are usually investigated in terms of their synchronization with the fluid flow profile.
-Considering a trapezoidal magnetic profile and a square fluid flow waveform, a numerical analysis showed that small delays between the increase of the magnetic field and the start of the fluid flow is beneficial for the cooling capacity, to assure the solid is fully magnetized before the fluid starts transfering energy from it \citet{bib:bjoerk11_amr}.
+The control of these blow durations can be achieved with the use of solenoid valves; a model for a digital hydraulic system and a calculation of valve power has been presented by  \cite{bib:cardoso16_trans}, who showed that, if the opening and closing times are fast enough compared to the cycle period, then valve power is indepedent of frequency and proportional to the blow duration.
+An application of  electronic valves in AMR devices has been presented by \cite{bib:nakashima18-perfor-asses-solen-valves-flow}, using the control logic (for synchronizing the valve operation with the magnetic profile) described by \cite{bib:hoffmann17-actuat}.
+
+In contrast, because of the complexities involved in designing and fabricating magnetic circuits, the applied magnetic field profiles (or simply the magnetic waveforms) are much less studied, and are usually investigated in terms of their synchronization with the fluid flow profile with numerical investigations.
+Considering a trapezoidal magnetic profile and a square fluid flow waveform, a numerical analysis showed that small delays between the increase of the magnetic field and the start of the fluid flow is beneficial for the cooling capacity, to assure the solid is fully magnetized before the fluid starts transfering energy from it \cite{bib:bjoerk11_amr}.
+To the authors' knowledge, the only work that experimentally varied the magnetic profile, by controlling the rotation of magnetic cylinders, is the work by \cite{bib:benedict16_desig}, which also showed that cooling capacity of an AMR device is dependent on this lag between magnetization and fluid flow.
+
 If this delay is further increased so that the fluid flow period can coincide with diferent stages of the magnetic profile, different thermodynamic cycles can be obtained with different performance trends; the Brayton AMR cycle (explained previously) yields the highest cooling capacities, while the Ericsson AMR cycle (with isothermal (de)magnetization steps) yield the highest values of the coefficient of performance \cite{bib:plaznik13-numer}.
 This conclusion was confirmed by the more extensive numerical analysis of \cite{bib:kitanovski}, which also varied the amplitude of the trapezoidal magnetic profile and proposed magnetic circuit designs which could generate these profiles.
+Trevizoli et al.~\cite{bib:asme-mce} carried out a numerical comparison of the square wave (step change), sinusoidal and rectified cosine magnetic profiles for a sinusoidal fluid profile and concluded that the cooling capacity and maximum temperature spans are maximal for the instantaneous magnetic profile.
 
-\colorbox{yellow}{acho q cabe explicar brevemente o que os trabalhos de \cite{TUSEK20111507} e \cite{bib:bjoerk11_amr} fizeram...}.
-Trevizoli et al.~\cite{bib:trevizoli16_perfor_model} carried out a numerical comparison of the square wave (step change), sinusoidal and rectified cosine magnetic profiles.
-However, no systematic assessment of the effect of amplitude was performed nor did they investigate different geometries \colorbox{yellow}{nao estah claro o que vc quer dizer por geometries}.
-
-\colorbox{yellow}{Fabio, acho que revisao bibliografica tem que ser expandida, trazendo trabalhos mais recentes em refrigeracao magnetica.}
-
-\colorbox{yellow}{Tambem tem que trazer aqui para a revisao os nossos artigos que mediram/testaram/modelaram as valvulas.}
+As previously noted, the fluid flow profile is implemented with proper design of the fluid flow system, while the magnetic profile is an important input when designing a magnetic circuit \cite{bib:oh13-air}.
+With the goal of AMR design, none of works reviewed in this section considered different \emph{shapes} and \emph{amplitudes} of the magnetic field waveform.
+Regarding shape, the combination of a trapezoidal magnetic profile and an instantaneous fluid flow profile is prevalent in the literature \cite{bib:bjoerk11_amr,bib:benedict16_desig,bib:park17-devel-k-k}, and this case is also investigated in the present paper.
+However, sinusoidal magnetic profiles can be achieved with more compact systems \cite{bib:trevizoli16_pump}, and their generation and impact of AMR devices have been investigated by  our group [PAPERS JMMM E TRADEOFF], but no work has investigated how these waveforms, when synchronized with optimized fluid flow profiles, can compare with the instantaneous magnetic profile, which the literature identifies as the optimal one when the fluid flow profile is fixed.
 
@@
 The electrical power consumed by the valve array is computed separately from other work contributions.
-An application of electronic valves in AMR devices has been presented by \cite{bib:nakashima18-perfor-asses-solen-valves-flow}.
-
-\colorbox{yellow}{Fabio, a ultima frase do paragrafo acima nao  cabe aqui... quero dizer que a aplicacao deveria ter sido discutida na revisao bibliografica, a qual precisa ser expandida}
 

### 2019-11-03 PaperMagneticProfiles_JBSMSE.tex
Add reference to my previous papers.

@@
 Regarding shape, the combination of a trapezoidal magnetic profile and an instantaneous fluid flow profile is prevalent in the literature \cite{bib:bjoerk11_amr,bib:benedict16_desig,bib:park17-devel-k-k}, and this case is also investigated in the present paper.
-However, sinusoidal magnetic profiles can be achieved with more compact systems \cite{bib:trevizoli16_pump}, and their generation and impact of AMR devices have been investigated by  our group [PAPERS JMMM E TRADEOFF], but no work has investigated how these waveforms, when synchronized with optimized fluid flow profiles, can compare with the instantaneous magnetic profile, which the literature identifies as the optimal one when the fluid flow profile is fixed.
+However, sinusoidal magnetic profiles can be achieved with more compact systems \cite{bib:trevizoli16_pump}, and their generation and impact of AMR devices have been investigated by  our group \cite{FORTKAMP201787,bib:fortkamp20-desig}, but no work has investigated how these waveforms, when synchronized with optimized fluid flow profiles, can compare with the instantaneous magnetic profile, which the literature identifies as the optimal one when the fluid flow profile is fixed.
 

### 2019-11-03 PaperMagneticProfiles_JBSMSE.tex
Add specific comments on which power contributions are accounted for.

@@
 We also implemented a model to calculate the power consumption of a novel fluid management system, which is a topic not yet extensively studied in the literature.
-The output variables from this integrated model are the cooling capacity, the several power contributions (\colorbox{yellow}{specify}) and the coefficient of performance (COP).
+The output variables from this integrated model are the cooling capacity, the several power contributions (the magnetic power to magnetize the material, the pumping power to overcome pressure drop in the regenerator, and the power to actuate the electronic valves) and the coefficient of performance (COP).
 

### 2019-11-03 PaperMagneticProfiles_JBSMSE.tex
Include explanation of terms in momentum and energy equations.

@@
 
-\noindent and is solved for the time-dependent uniform fluid velocity $V_z$ through the bed.
+\noindent where the macroscopic inertial term on the left-hand side is balanced with the pressure gradient, Darcy stress and Forchheimer drag \cite{bib:nield06_convec_porous_media}.
+The momentum equation is solved for the time-dependent uniform fluid velocity $V_z$ through the bed.
 
@@
 \end{equation}
+
+\noindent where the left-hand side includes the inertial and advection terms, and the right-hand side includes terms for the solid-fluid heat transfer, viscous dissipation, heat conduction, porous-media dispersion, and casing losses.
 
@@
 
-\noindent while the energy equation for the solid phase is written as:
+The energy equation for the solid phase is written as:
 
@@
 
-\colorbox{yellow}{Fabio, talvez valha a pena explicar quem eh quem nos termos das equacoes da Q movimento e energias...}
+\noindent where the terms represent respectively inertia, solid-fluid heat transfer and heat conduction.
 

### 2019-11-03 PaperMagneticProfiles_JBSMSE.tex
Confirm JRB explanation on the multilayer materials.

@@
 It can be neglected in some circumstances if an insulating casing material is assumed, which greatly simplifies the analysis.
-%More details are provided in \autoref{sec:results-discussions}.
 
@@
 In this loop, the mass flow rate calculated in term of the Darcy velocity from \autoref{eq:75} is compared with the input   mass flow rate until convergence is obtained.
-%The waveform $g(t)$ represents the fluid flow profile used.
 
@@
   \includegraphics[width=8cm]{mprofile}
-  \caption{Instantaneous fluid flow profile}
+  \caption{Instantaneous fluid flow profile. Adapated from \cite{bib:fortkamp20-desig}.}
   \label{fig:mprofile}
@@
 This fraction reduces the Curie temperature of the alloy relative to that of pure gadolinium.
-Due to the lack of experimental  data on the magnetocaloric properties of \ce{Gd_{1-x}Y_x} alloys at the time this analysis was made, a simpler approach was used in which the \textcolor{blue}{dependence of magnetization, specific heat capacity and entropy with respect to the magnetic field for} alloys with a low yttrium fraction are identical to those of pure gadolinium, \textcolor{blue}{but are shifted to a lower} Curie temperature (corresponding to the yttrium fraction).
+Due to the lack of experimental  data on the magnetocaloric properties of \ce{Gd_{1-x}Y_x} alloys at the time this analysis was made, a simpler approach was used in which the dependence of magnetization, specific heat capacity and entropy with respect to the magnetic field for alloys with a low yttrium fraction are identical to those of pure gadolinium, but are shifted to a lower Curie temperature (corresponding to the yttrium fraction).
 
-\colorbox{yellow}{Fabio, veja se o texto acima estah ok...}
+\nomenclature[ix]{$x$}{yttrium fraction}
 

### 2019-11-03 PaperMagneticProfiles_JBSMSE.tex
Cite our Trade-offs paper to justify accounting of irreversibilities.

@@
 
-\textcolor{blue}{As pointed out in \colorbox{yellow}{citar o paper da ATE - Design trade-offs}, since external sources of irreversibility (e.g., heat transfer with a finite temperature difference in the heat exchangers) are ignored and no eddy currents and hysteresis losses are present,} the magnetic power required to \textcolor{blue}{magnetize the solid refrigerant and produce the MCE} in the AMR cycle is given by the product of the Carnot efficiency and the cooling capacity as follows:
+As pointed out in \cite{bib:fortkamp20-desig}, since external sources of irreversibility (e.g., heat transfer with a finite temperature difference in the heat exchangers) are ignored and no eddy currents and hysteresis losses are present, the magnetic power required to magnetize the solid refrigerant and produce the MCE in the AMR cycle is given by the product of the Carnot efficiency and the cooling capacity as follows:
 

### 2019-11-03 PaperMagneticProfiles_JBSMSE.tex
Change nomenclature of valve types.

@@
 
-%Due to evolving developments in our group, two types of valves are considered, as will be elaborated in \autoref{sec:results-discussions}.
+% Type R = Type B (BuRkert)
+% Type S = Type A (ASco)
 
 In the present analysis, two types of valves are considered.
-In the first approach, called \emph{Type B valves}, the  model proposed in Ref.~\cite{bib:cardoso16_trans} is used, assuming that the individual consumption of each valve is independent of frequency and blow fraction.
+In the first approach, called \emph{Type R valves}, the  model proposed in \cite{bib:cardoso16_trans} is used, assuming that the individual consumption of each valve is independent of frequency and blow fraction.
 The valve power  $\wvalve$ can be computed as:
-
-\colorbox{yellow}{da mesma forma, o trabalho \cite{bib:cardoso16_trans} tem que constar da revisao bibliografica...}
-
-\colorbox{yellow}{fica estranho o \textbf{primeiro} approach ser Type B e o \textbf{segundo} ser Type A...}
 
@@
 
-In the second approach, \emph{Type A} valves are used, with  nominal power lower in magnitude but which depends on frequency and blow fraction.
+In the second approach, \emph{Type S} valves are used, with  nominal power lower in magnitude but which depends on frequency and blow fraction.
 For these valves, the valve power was experimentally correlated as:
@@
 
-At the first stage of the present analysis, the instantaneous and rectified cosine profiles are compared considering a single-layer regenerator  without casing losses, using Type B valves.
+At the first stage of the present analysis, the instantaneous and rectified cosine profiles are compared considering a single-layer regenerator  without casing losses, using Type R valves.
 The parameters used in all simulations are presented in \autoref{tab:params-cobem}.
@@
 A summary of all parameters adopted in this section, including the Curie temperatures and volumetric fractions (relative to the length of the bed) of each layer is presented in \autoref{tab:params-ramp}.
+In addition, in the following results, Type S valves are used, with valve power calculated by \autoref{eq:198}.
 

### 2019-11-03 PaperMagneticProfiles_JBSMSE.tex
Implement minor fixes.

@@
 \nomenclature[af]{$f$}{cycle frequency [\si{\hertz}]}
-\nomenclature[bf]{$\Phi$}{utilization}
 \nomenclature[am]{$m$}{mass [\si{\kg}]}
@@
 
+\nomenclature[ad]{$D\ped{p}$}{particle diameter [\si{meter}]}
+
 When comparing the performances resulting from the application of the different magnetic profiles, the same average magnetic field during the hot cycle will be considered; this implies a higher peak for the rectified cosine.
@@
 The instantaneous profile almost always yields a higher performance, and since the average field during the hot cycle (high field stage) is the same, the main difference is due to the low magnetic field levels.
-For the ``same minimum'' comparison, the instantaneous profile is capable of keeping a low magnetic field over the entire half-cycle, which is beneficial for performance;  for $\Phi=1.0$ and $B\ped{high} = \SI{1.40}{\tesla}$, the cooling capacity for the instantaneous profile is $\SI{196.3}{\percent}$ higher than for the cosine profile.
+In this comparison, the instantaneous profile is capable of keeping a low magnetic field over the entire half-cycle, which is beneficial for performance;  for $\Phi=1.0$ and $B\ped{high} = \SI{1.40}{\tesla}$, the cooling capacity for the instantaneous profile is $\SI{196.3}{\percent}$ higher than for the cosine profile.
 As demonstrated by \cite{bib:asme-mce}, a higher average magnetic field during the low-field stage increases the solid temperature and consequently results in  warmer fluid entering the cold heat exchanger, representing a thermal loss.

### 2019-11-04 PaperMagneticProfiles_JBSMSE.tex
Complete list of symbols.

@@
 
+\nomenclature[ah]{$H\ped{reg}$}{regenerator height [\si{\meter}]}
+\nomenclature[aw]{$W\ped{reg}$}{regenerator width [\si{\meter}]}
+\nomenclature[al]{$L\ped{reg}$}{regenerator length [\si{\meter}]}
+\nomenclature[ah]{$H$}{magnetic field [\si{\henry}]}
+
 The momentum equation for the fluid domain is given by:
@@
 
-\nomenclature[ak]{$K$}{permeability of the porous medium [\si{\meter\square}]}
+\nomenclature[ak]{$K$}{permeability of the porous medium [\si{\meter\squared}]}
 \nomenclature[ac]{$c\ped{E}$}{Ergun constant of the porous medium}
@@
 \nomenclature[ap]{$P$}{pressure [\si{\pascal}]}
-\nomenclature[bu]{$\mu$}{dynamic viscosity [\si{\pascal\second}]}
+\nomenclature[bu]{$\mu\ped{f}$}{fluid dynamic viscosity [\si{\pascal\second}]}
 
@@
 \nomenclature[at]{$t$}{time [\si{\second}]}
-\nomenclature[az]{$z$}{axial coordinate [\si{\meter}]}
+\nomenclature[ax]{$x,y,z$}{coordinate system variables [\si{\meter}]}
+\nomenclature[ip]{$p$}{constant-pressure}
 
@@
 \nomenclature[is]{sf}{relative to the heat transfer between solid and fluid phases in the regenerator}
-\nomenclature[bb]{$\beta$}{surface area density [\si{\squared\meter\per\cubic\meter}]}
-\nomenclature[ak]{$k\ap{eff}$}{effective thermal conductivity [\si{\watt\per\meter\per\kelvin}]}
+\nomenclature[bb]{$\beta$}{surface area density [\si{\square\meter\per\cubic\meter}]}
+\nomenclature[ak]{$k$}{thermal conductivity [\si{\watt\per\meter\per\kelvin}]}
 \nomenclature[ad]{$D\ped{ld}$}{dispersion term in the AMR model [\si{\meter\square\per\second}]}
@@
 \nomenclature[ag]{$g(t)$}{dimensional waveform of the pressure gradient term in the fluid momentum equation}
-\nomenclature[aA]{$A\ped{t}$}{amplitude of the pressure gradient waveform in the fluid momentum equation [\si{\meter\per\second\square}]}
+\nomenclature[aA]{$A\ped{t}$}{amplitude of the pressure gradient waveform in the fluid momentum equation [\si{\meter\per\second\squared}]}
 
@@
 \nomenclature[vc]{CC}{cold cycle}
+\nomenclature[vc]{CB}{cold blow}
+\nomenclature[bt]{$\tau\ped{0,CC}, \tau\ped{0,HC}$  }{time periods without fluid flow in the respective half-cycle (see list of Abbreviations) [\si{\second}]}
 
@@
 \nomenclature[bt]{$\tau\ped{B}$}{blow duration [\si{\second}]}
+\nomenclature[af]{$F\ped{B}$}{blow fraction}
 
@@
 
-\nomenclature[am]{$M$}{magnetization field [\si{\ampere\per\meter}]}
+\nomenclature[am]{$M$}{magnetization field [\si{\henry}]}
 \nomenclature[an]{$N\ped{D}$}{demagnetization tensor}
+\nomenclature[ie]{eff}{effective}
 
@@
 
-\nomenclature[bt]{$\dtad$}{adiabatic temperature variation [\si{\kelvin}]}
+\nomenclature[at]{$\dtad$}{adiabatic temperature variation [\si{\kelvin}]}
 
@@
 Sec.~\ref{sec:how-magnetic-profile}).
+
+\nomenclature[ab]{$B$}{magnetic flux density [\si{\tesla}]}
+\nomenclature[bu]{$\mu_0$}{magnetic permeability of free space [\si{\henry\per\meter}]}
 
@@
 
-\noindent such that there are four ramp periods in one full cycle. The ramp rate, \(\theta\ped{R}\), is:
+\noindent such that there are four ramp periods in one full cycle. The ramp rate, \(\tan \theta\ped{R}\), is:
 
@@
 
-\nomenclature[azt]{$\tau\ped{R}$}{ramp period in the magnetic ramp profile [\si{\second}]}
-\nomenclature[azt]{$\tau\ped{M}$}{magnetization period in the magnetic ramp  profile [\si{\second}]}
-\nomenclature[azo]{$\theta\ped{R}$}{ramp rate in the magnetic ramp profile}
+\nomenclature[bt]{$\tau\ped{R}$}{ramp period in the magnetic ramp profile [\si{\second}]}
+\nomenclature[bt]{$\tau\ped{M}$}{magnetization period in the magnetic ramp  profile [\si{\second}]}
+\nomenclature[bo]{$\tan \theta\ped{R}$}{ramp rate in the magnetic ramp profile [\si{\tesla\per\second}]}
 
@@
 
-\nomenclature[vr]{RM}{rectified cosine magnetic profile}
+\nomenclature[vr]{RM}{ramp magnetic profile}
 
@@
 
-The AMR model is solved for only one bed, but  assumes that the $N\ped{r}$ identical beds experience the same cycle. Thus, the extensive performance parameters are multiplied by that factor.
+The AMR model is solved for only one bed, but  assumes that the $N\ped{reg}$ identical beds experience the same cycle. Thus, the extensive performance parameters are multiplied by that factor.
 
-\nomenclature[an]{$N\ped{r}$}{number of regenerators}
+\nomenclature[an]{$N\ped{reg}$}{number of regenerators}
 
@@
 \label{eq:99}
-\qc = N\ped{r}\frac{1}{\tau} \int_{\tau\ped{HB}} \mrate\ped{f}(t) c_{p,\mathrm{f}} \left( T\ped{C} -T\ped{f,CE} \right) \diffd{t}
+\qc = N\ped{reg}\frac{1}{\tau} \int_{\tau\ped{HB}} \mrate\ped{f}(t) c_{p,\mathrm{f}} \left( T\ped{C} -T\ped{f,CE} \right) \diffd{t}
 \end{equation}
@@
 \nomenclature[vc]{H}{hot source}
+\nomenclature[aq]{$\qc$}{cooling capacity [\si{\watt}]}
 
@@
 \label{eq:103}
-\wpump = N\ped{r}\frac{1}{\tau}\int_0^{\tau}\frac{\rate{m}\ped{f}}{\rho\ped{f}} \Delta P \diffd{t}
+\wpump = N\ped{reg}\frac{1}{\tau}\int_0^{\tau}\frac{\rate{m}\ped{f}}{\rho\ped{f}} \Delta P \diffd{t}
 \end{equation}
 
-\noindent where $\Delta P$ is the total pressure drop through the regenerator.
+\noindent where $\Delta P$ is the total pressure drop through the regenerator (including one hot and one cold blow).
 
@@
 \nomenclature[awm]{$\wmag$}{magnetic power [\si{\watt}]}
-\nomenclature[ap]{$\Delta P$}{pressure drop across one region [\si{\pascal}]}
+\nomenclature[ap]{$\Delta P$}{total pressure drop across one regenerator [\si{\pascal}]}
 
@@
 
-\noindent where $N\ped{v}$ is the number of valves, $\wvalven$ is the measured average nominal power for one normally-closed electronic valve and $\wrelayn$ is the nominal power for one controlling relay.
+\noindent where $N\ped{valve}$ is the number of valves, $\wvalven$ is the measured average nominal power for one normally-closed electronic valve and $\wrelayn$ is the nominal power for one controlling relay.
 The factor $\nicefrac{1}{2}$ is due to two valves being controlled by one relay.
 
-\nomenclature[an]{$N\ped{v}$}{number of valves}
+\nomenclature[an]{$N\ped{valve}$}{number of valves}
 \nomenclature[aw]{$\wvalve$}{valve power [\si{\watt}]}
@@
   \label{eq:198}
-  \wvalve\,[\si{\watt}]= N\ped{v}\left(0.927 f\,[\si{\hertz}] + 1.023 F\ped{B} + 0.226 f\,[\si{\hertz}] F\ped{B} - 0.037\right)
+  \wvalve\,[\si{\watt}]= N\ped{valve}\left(0.927 f\,[\si{\hertz}] + 1.023 F\ped{B} + 0.226 f\,[\si{\hertz}] F\ped{B} - 0.037\right)
 \end{equation}
@@
   \label{eq:111}
-  N\ped{v} = 2 N\ped{r}
+  N\ped{valve} = 2 N\ped{reg}
 \end{equation}
@@
   \centering
-  \caption{AMR parameters kept fixed in the simulations with different magnetic profiles \colorbox{yellow}{Fabio, acho que as variaveis nao foram apresentadas na lista de simbolos}}
+  \caption{AMR parameters kept fixed in the simulations with different magnetic profiles}
   \begin{tabular}{c|c}
@@
    $D\ped{p}$ & \SI{0.5}{\mm}\\
-$H\ped{r}$ & \SI{20}{\mm}\\
-$W\ped{r}$ & \SI{25}{\mm}\\
-$L\ped{r}$ & \SI{100}{\mm}\\
-$N\ped{r}$ & 11 \\
-$N\ped{v}$ & 22 \\
+$H\ped{reg}$ & \SI{20}{\mm}\\
+$W\ped{reg}$ & \SI{25}{\mm}\\
+$L\ped{reg}$ & \SI{100}{\mm}\\
+$N\ped{reg}$ & 11 \\
+$N\ped{valve}$ & 22 \\
 $T\ped{H}$ & \SI{298}{\kelvin}\\
 $\tc$ & \SI{278}{\kelvin}\\
-$\w\ped{NV}$ & \SI{4}{\watt}\\
-$\w\ped{R}$ & \SI{0.36}{\watt}\\
+$\wvalven$ & \SI{4}{\watt}\\
+$\wrelayn$ & \SI{0.36}{\watt}\\
 \hline
@@
 
-\nomenclature[ad]{$D\ped{p}$}{particle diameter [\si{meter}]}
+\nomenclature[ad]{$D\ped{p}$}{particle diameter [\si{\meter}]}
 
@@
 \nomenclature[ia]{air}{air layer between magnets and regenerators}
+\nomenclature[ah]{$h$}{thickness [\si{\meter}]}
 
@@
 \hline
-$R\ped{o}$ & \SI{40}{\mm} \\
-$W\ped{r}$ & \SI{30}{\mm} \\
-$L\ped{r}$ & \SI{85}{\mm} \\
-$N\ped{r}$ & \num{8} \\
-$N\ped{v}$ & \num{16} \\
+$W\ped{reg}$ & \SI{30}{\mm} \\
+$L\ped{reg}$ & \SI{85}{\mm} \\
+$N\ped{reg}$ & \num{8} \\
+$N\ped{valve}$ & \num{16} \\
 $f$ & \SI{1}{\hertz} \\

### 2019-11-05 PaperMagneticProfiles_JBSMSE.tex
Improved conclusions.
The paragraphs were made more clear, and some numerical results are cited.

@@
 
-To the authors' knowledge, this is the first study where magnetic profiles for AMR model are mathematically modeled and the model parameters are changed in a systematic way.
-The instantaneous (square wave), rectified cosine and ramp magnetic profiles were implemented in an AMR model, and the profile parameters were varied simultaneously with the regenerator geometric parameters.
+To the authors' knowledge, this is the first study where magnetic and fluid flow profiles for an AMR model are mathematically modeled and the model parameters are changed in an integrated and systematic  way.
+The instantaneous (square wave), rectified cosine and ramp magnetic profiles were implemented in an AMR model, together with an instantaneous fluid flow profile, and the profile parameters were varied simultaneously with the regenerator geometric parameters.
 These waveforms can be found in existing MR devices published in the literature.
+A valve model was also incorporated into a more realistic computation of the coefficient of performance.
 
-Using a simplified model, the instantaneous profile resulted in a higher cooling capacity, even by reducing the blow fraction on rectified cosine, at least up to levels achieved by pumping and valving systems; further reductions of the blow fraction is mainly restricted by valve opening times.
-This means that, even if sinusoidal profiles can be obtained with more compact magnetic circuit systems, the performance of magnetic refrigeration systems can be maximized by using instantaneous variations of the magnetic field, and then optimizing the regenerator height and blow duration.
-\colorbox{yellow}{Fabio, tive dificuldade em entender o que voce quis concluir neste paragrafo...
-talvez seja uma boa tentar expandir seu conteudo}
+When comparing the instantaneous  and the rectified cosing magnetic profiles, the cooling capacity associated with the former can be almost \SI{200}{\percent} higher than with the latter, for the same utilization and average high magnetic field and considering optimal blow fractions.
+The rectified cosing profile suffers from high values of the low magnetic field, and reduction of blow fraction up to the minimum tested value of \SI{60}{\percent} is not enough to overcome the loss in cooling capacity resulting from this effect.
 
-The ramp profile is a feasible approximation for the instantaneous profile without abrupt changes in the magnetic field plateaus.
-This waveform can be optimized for increasing cooling capacity, in particular by synchronizing the plateau durations between fluid and magnetic profiles.
-\colorbox{yellow}{Fabio, acho que seria bom trazer alguns dados quantitativos para ca, tipo ganhos percentuais etc.}
+An analysis of power contributions showed that the cost of the higher cooling capacity for the instantaneous profile is a higher valve power associated with the longer blow duration, dominating the other contributions.
+However, the coefficient of performance is still higher for the square wave.
+Hence, even though sinusoidal waveforms can be obtained with more compact systems, step-like variations of high amplitude of the magnetic field are preferred if performance is more critical.
+
+The ramp magnetic profile is a feasible approximation for the instantaneous profile without abrupt changes in the magnetic field plateaus.
+For an AMR device operating with this  profile and the instantaneous fluid flow profile, both cooling capacity and coefficient of performance are maximized if the blow duration is equal to the period of constant magnetic field; if this exact synchronization is not possible, making the magnetization plateau wider than the flow plateau results in smaller reduction of the performance metrics than if it is narrower.
+
+With this strategy and using average values of utilization, it is possible to achieve second-law efficiency levels compatible with vapor-compression systems.
+Hence the ramp magnetic profile is identified as a suitable target profile in the design of magnetic circuits for AMR devices.
 

### 2019-11-05 PaperMagneticProfiles_JBSMSE.tex
Improved explanation of Type S valves.

@@
 
-The control of these blow durations can be achieved with the use of solenoid valves; a model for a digital hydraulic system and a calculation of valve power has been presented by  \cite{bib:cardoso16_trans}, who showed that, if the opening and closing times are fast enough compared to the cycle period, then valve power is indepedent of frequency and proportional to the blow duration.
+The control of these blow durations can be achieved with the use of solenoid valves; a model for a digital hydraulic system and a calculation of valve power has been presented by  \cite{bib:cardoso16_trans} and \cite{bib:cardoso18}.
 An application of  electronic valves in AMR devices has been presented by \cite{bib:nakashima18-perfor-asses-solen-valves-flow}, using the control logic (for synchronizing the valve operation with the magnetic profile) described by \cite{bib:hoffmann17-actuat}.
@@
 In the second approach, \emph{Type S} valves are used, with  nominal power lower in magnitude but which depends on frequency and blow fraction.
-For these valves, the valve power was experimentally correlated as:
+These valves were experimentally characterized by \cite{bib:cardoso18}, where a single valve was attached to a measurement circuit and set to operate for varying values of blow fraction and frequency; the valve power was calculated from the averaged values of voltage and current after periodic steady state was reached.
+From these experiments, the valve power was experimentally correlated as:
 
@@
 \end{equation}
-
-\colorbox{yellow}{A equacao acima precisa ser melhor contextualizada.
-Talvez os revisores pecam para dar uma descricao minima do experimento.
-Uma saida para nao ter que fazer isso seria revisar na introducao o trabalho nosso que mediu e propos a correlacao (foi o do Pedroca)  }
 
@@
 
-\bibliography{thermo-ref/Thermo-Foam-Ref,thermo-ref/thesis}
+\bibliography{thermo-ref/Thermo-Foam-Ref,thesis}
 

### 2019-11-05 PaperMagneticProfiles_JBSMSE.tex
Rename figures sequentially.

@@
   \centering
-  \includegraphics[width=8cm]{reg3d}
+  \includegraphics[width=8cm]{Fig1-reg3d}
   \caption{AMR model geometry}
@@
   \centering
-  \includegraphics[width=8cm]{mprofile}
+  \includegraphics[width=8cm]{Fig2-mprofile}
   \caption{Instantaneous fluid flow profile. Adapated from \cite{bib:fortkamp20-desig}.}
@@
   \centering
-  \includegraphics[width=8cm]{profiles_it_and_rc}
+  \includegraphics[width=8cm]{Fig3-profiles_it_and_rc}
   \caption{Instantaneous ("IT") and rectified cosine ("RC") magnetic profiles}
@@
   \centering
-  \includegraphics[width=7cm]{profile_rm}
+  \includegraphics[width=7cm]{Fig4-profile_rm}
   \caption{\textcolor{black}{Magnetic ramp}  profile}
@@
   \centering
-\includegraphics[width=8cm]{profiles_it_and_rc_same_minimum}
+\includegraphics[width=8cm]{Fig5-profiles_it_and_rc_same_minimum}
   \caption{Configuration of average and extreme values of the instantaneous and rectified cosine profiles }
@@
   \centering
-  \includegraphics[width=7cm]{profiles_rc_and_flow_instantaneous}
+  \includegraphics[width=7cm]{Fig6-profiles_rc_and_flow_instantaneous}
   \caption{Rectified cosine magnetic profile and the instantaneous flow profile with blow fraction of \SI{60}{\percent}}
@@
   \centering
-\includegraphics[width=8cm]{Qc_B_comp_f_1_same_minimum}
+\includegraphics[width=8cm]{Fig7-Qc_B_comp_f_1_same_minimum}
   \caption{Cooling capacity as a function of the  average high magnetic field, for different utilizations.
@@
   \centering
-\includegraphics[width=7cm]{COP_B_comp_f_1_same_minimum}
+\includegraphics[width=7cm]{Fig8-COP_B_comp_f_1_same_minimum}
   \caption{Coefficient of performance as a function of the  average high magnetic field, for different values of utilization.
@@
   \centering
-  \includegraphics[width=10cm]{W_B_comp_f_1_Phi_60_same_minimum}
+  \includegraphics[width=10cm]{Fig9-W_B_comp_f_1_Phi_60_same_minimum}
   \caption{Power contributions as functions of the average high magnetic field, for a utilization of 0.6.
@@
   \centering
-\subfloat[$f = \SI{1}{\hertz}$]{\includegraphics[width=8cm]{Qc_Phi_inst_f_1_Hmin_005_FB_100}\label{fig:Qc_phi_inst_1}}
+\subfloat[$f = \SI{1}{\hertz}$]{\includegraphics[width=8cm]{Fig10a-Qc_Phi_inst_f_1_Hmin_005_FB_100}\label{fig:Qc_phi_inst_1}}
 \,
-  \subfloat[$f = \SI{2}{\hertz}$]{\includegraphics[width=8cm]{Qc_Phi_inst_f_2_Hmin_005_FB_100}\label{fig:Qc_phi_inst_2}}
+  \subfloat[$f = \SI{2}{\hertz}$]{\includegraphics[width=8cm]{Fig10b-Qc_Phi_inst_f_2_Hmin_005_FB_100}\label{fig:Qc_phi_inst_2}}
   \caption{Cooling capacity as a function of utilization, for various values of the high magnetic field  for the instantaneous profile}
@@
   \centering
-  \subfloat[Cooling capacity]{\includegraphics[width=9cm]{Qc_H_inst_f_1_Phi_40}\label{fig:Qc_H_inst_f_1_Phi_40}}
+  \subfloat[Cooling capacity]{\includegraphics[width=9cm]{Fig11a-Qc_H_inst_f_1_Phi_40}\label{fig:Qc_H_inst_f_1_Phi_40}}
 \quad
-  \subfloat[Coefficient of performance]{\includegraphics[width=9cm]{COP_H_inst_f_1_Phi_40}\label{fig:COP_H_inst_f_1_Phi_40}}
+  \subfloat[Coefficient of performance]{\includegraphics[width=9cm]{Fig11b-COP_H_inst_f_1_Phi_40}\label{fig:COP_H_inst_f_1_Phi_40}}
   \caption{Performance metrics as a function of the regenerator height (all other parameters were set as in Table~\ref{tab:params-cobem}, for utilization factor of 0.4) for various values of the high magnetic field of the instantaneous profile}
@@
   \centering
-  \includegraphics[width=7cm]{amr-casing}
+  \includegraphics[width=7cm]{Fig12-amr-casing}
   \caption{Model for the casing losses in regenerators}
@@
   \centering
-  \includegraphics[width=7cm]{profiles_rm_and_flow_instantaneous}
+  \includegraphics[width=7cm]{Fig13-profiles_rm_and_flow_instantaneous}
   \caption{Comparison between the magnetic \textcolor{black}{ramp} profile (solid line) and the instantaneous fluid flow profile (dashed line)}
@@
   \centering
-  \subfloat[Cooling capacity]{\includegraphics[width=5cm]{Qc_FM_ramp_f_1_Phi_40_35K_1300mT}\label{fig:Qc_FM_ramp_f_1_Phi_40_35K_1.3T}}
+  \subfloat[Cooling capacity]{\includegraphics[width=5cm]{Fig14a-Qc_FM_ramp_f_1_Phi_40_35K_1300mT}\label{fig:Qc_FM_ramp_f_1_Phi_40_35K_1.3T}}
 \quad
- \subfloat[Coefficient of performance]{\includegraphics[width=5cm]{COP_FM_ramp_f_1_Phi_40_35K_1300mT}\label{fig:COP_FM_ramp_f_1_Phi_40_35K_1.3T}}
+ \subfloat[Coefficient of performance]{\includegraphics[width=5cm]{Fig14b-COP_FM_ramp_f_1_Phi_40_35K_1300mT}\label{fig:COP_FM_ramp_f_1_Phi_40_35K_1.3T}}
   \caption{Performance of the AMR system for various blow and magnetization fractions, utilization of 0.4 and and high magnetic field of \SI{1.3}{\tesla}}
@@
   \centering
-  \subfloat[$\Phi = \num{0.2}$]{\includegraphics[width=5cm]{Qc_FM_ramp_f_1_Phi_20_35K_1300mT}\label{fig:Qc_FM_ramp_f_1_Phi_20_35K_1.3T}}
+  \subfloat[$\Phi = \num{0.2}$]{\includegraphics[width=5cm]{Fig15a-Qc_FM_ramp_f_1_Phi_20_35K_1300mT}\label{fig:Qc_FM_ramp_f_1_Phi_20_35K_1.3T}}
 \quad
  \subfloat[$\Phi = \num{
-0.5}$]{\includegraphics[width=5cm]{Qc_FM_ramp_f_1_Phi_50_35K_1300mT}\label{fig:COP_FM_ramp_f_1_Phi_50_35K_1.3T}}
+0.5}$]{\includegraphics[width=5cm]{Fig15b-Qc_FM_ramp_f_1_Phi_50_35K_1300mT}\label{fig:COP_FM_ramp_f_1_Phi_50_35K_1.3T}}
   \caption{Influence of utilization on the cooling capacity of the AMR system for  various blow and magnetization fractions, with high magnetic field of \SI{1.3}{\tesla}}
@@
   \centering
-  \subfloat[$\Phi = 0.2, F\ped{B} = \SI{60}{\percent}$]{\includegraphics[width=5cm]{COP_ramp_map_f_1_Phi_20_FB_60_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_20_FB_70_35K_Valv_ASCO}}
+  \subfloat[$\Phi = 0.2, F\ped{B} = \SI{60}{\percent}$]{\includegraphics[width=5cm]{Fig16a-COP_ramp_map_f_1_Phi_20_FB_60_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_20_FB_70_35K_Valv_ASCO}}
 \quad
- \subfloat[$\Phi= 0.2, F\ped{B} = \SI{90}{\percent}$]{\includegraphics[width=5cm]{COP_ramp_map_f_1_Phi_20_FB_90_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_20_FB_90_35K_Valv_ASCO}} \\
-  \subfloat[$\Phi = 0.4, F\ped{B} = \SI{60}{\percent}$]{\includegraphics[width=5cm]{COP_ramp_map_f_1_Phi_40_FB_60_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_60_FB_90_35K_Valv_ASCO}}
+ \subfloat[$\Phi= 0.2, F\ped{B} = \SI{90}{\percent}$]{\includegraphics[width=5cm]{Fig16b-COP_ramp_map_f_1_Phi_20_FB_90_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_20_FB_90_35K_Valv_ASCO}} \\
+  \subfloat[$\Phi = 0.4, F\ped{B} = \SI{60}{\percent}$]{\includegraphics[width=5cm]{Fig16c-COP_ramp_map_f_1_Phi_40_FB_60_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_60_FB_90_35K_Valv_ASCO}}
 \quad
- \subfloat[$\Phi = 0.4, F\ped{B} = \SI{90}{\percent}$]{\includegraphics[width=5cm]{COP_ramp_map_f_1_Phi_40_FB_90_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_40_FB_90_35K_Valv_ASCO}}
+ \subfloat[$\Phi = 0.4, F\ped{B} = \SI{90}{\percent}$]{\includegraphics[width=5cm]{Fig16d-COP_ramp_map_f_1_Phi_40_FB_90_35K_Valv_ASCO}\label{fig:COP_ramp_map_f_1_Phi_40_FB_90_35K_Valv_ASCO}}
   \caption{Influence of utilization and blow fraction on the coefficient of performance of the AMR system for varying high magnetic field and magnetization fraction}
@@
   \centering
-\subfloat[Cooling capacity (solid lines) and coefficient of performance (dashed lines)]{  \includegraphics[width=5cm]{Qc_COP_combined_H_regW30}\label{fig:Qc_COP_Hreg}}
+\subfloat[Cooling capacity (solid lines) and coefficient of performance (dashed lines)]{  \includegraphics[width=5cm]{Fig17a-Qc_COP_combined_H_regW30}\label{fig:Qc_COP_Hreg}}
 \,
-\subfloat[Second-law efficiency]{\includegraphics[width=5cm]{eta_H_regW30}\label{fig:eta_Hreg}}
+\subfloat[Second-law efficiency]{\includegraphics[width=5cm]{Fig17b-eta_H_regW30}\label{fig:eta_Hreg}}
   \caption{Performance of the AMR with varying regenerator height and high magnetic field, with fixed $F\ped{M} = F\ped{B} = \SI{70}{\percent}$ and $\Phi = 0.4$}

### 2019-11-11 figures.py
Perform major reorganization.
This is a large commit. Scripts, figures, and datasets were moved to
subdirectories. The README was updated to explain the repo structure.

@@ -1,990 +1,0 @@
-#!/usr/bin/env python
-# coding: utf-8
-
-import math
-import re
-import os.path
-from pathlib import Path
-
-import numpy as np
-import numpy.ma as ma
-import pandas as pd
-from pandas import DataFrame, Series
-from scipy.interpolate import griddata
-from scipy.constants import mu_0
-from scipy.integrate import simps
-import matplotlib.pyplot as plt
-
-import loaddatasets as ld
-
-FIG_FILE_PATH = Path('.')
-PLOT_EXTENSION = ".eps"
-
-FIGSIZE_IN = (7,5)
-DPI = 600
-
-# stolen from https://stackoverflow.com/questions/3899980/how-to-change-the-font-size-on-a-matplotlib-plot
-SMALL_SIZE = 14
-MEDIUM_SIZE = 20
-BIGGER_SIZE = 22
-
-N_POINTS_LINEPLOT = 2000
-
-DENSITY_GD = 7900 # kg/m3, from Trevizoli et al (2016), IJR volume 72
-
-B_LABEL = r'${B}_\mathrm{high}\,[\mathrm{T}]$'
-Q_LABEL = r'$\dot{Q}_{\mathrm{C}}\,[\mathrm{W}]$'
-COP_LABEL = r'$\mathrm{COP}$'
-W_LABEL = r'$\dot{W}\,[\mathrm{W}]$'
-W_PUMP_LABEL = r'$\dot{W}_\mathrm{pump}\,[\mathrm{W}]$'
-W_MAG_LABEL = r'$\dot{W}_\mathrm{mag}\,[\mathrm{W}]$'
-W_VALVE_LABEL = r'$\dot{W}_\mathrm{valve}\,[\mathrm{W}]$'
-PHI_LABEL = r'$\Phi$'
-H_REG_LABEL = r'$H_\mathrm{r}\,[\mathrm{mm}]$'
-F_B_LABEL = r'$F_\mathrm{B}\,[\%]$'
-RATIO_F_LABEL = r'$\frac{F_\mathrm{M}}{F_\mathrm{B}}$'
-F_M_LABEL = r'$F_\mathrm{M}\,[\%]$'
-H_MAX_LABEL = r'${B}_\mathrm{max}\,[\mathrm{T}]$'
-Q_RATIO_LABEL = r'$\frac{\dot{Q}_{\mathrm{C,RC}}}{\dot{Q}_{\mathrm{C,IT}}}\,[\%]$'
[…]

### 2019-11-11 loaddatasets.py

@@ -1,53 +1,0 @@
-#!/usr/bin/env python
-# coding: utf-8
-
-import pandas as pd
-from pandas import DataFrame, Series
-
-INSTANTANEOUS_DATASET = "Instantaneous.csv"
-INSTANTANEOUS_DATASET_VARYING_HEIGHT = "Instantaneous-varH.csv"
-RAMP_DATASET = "Ramp.csv"
-RAMP_DATASET_VARYING_HEIGHT = "Ramp-varH.csv"
-RECTIFIED_COSINE_DATASET = "RectifiedCosine.csv"
-
-
-# These dataset are formated as tab-separed values (TSV), with column names in the format:
-# 
-#     <column_name>[<unit>]
-
-# These files are formatted in such a way that they can be easily loaded with pandas DataFrames.
-# 
-# We adopt the convention of naming these data sets as '<profile_identifier>df', where the profile identifier can be 'it' (instantaneous), 'rc' (rectified cosine) or 'rm' (ramp)
-
-itdf = pd.read_csv(INSTANTANEOUS_DATASET)
-it_varH_df = pd.read_csv(INSTANTANEOUS_DATASET_VARYING_HEIGHT)
-rcdf = pd.read_csv(RECTIFIED_COSINE_DATASET)
-rmdf = pd.read_csv(RAMP_DATASET)
-rm_varH_df = pd.read_csv(RAMP_DATASET_VARYING_HEIGHT)
-
-
-# The columns of interest can be nicely identified as:
-
-FREQUENCY_COLUMN = 'f[Hz]'
-REGENERATOR_HEIGHT_COLUMN = 'H[mm]'
-MAXIMUM_PROFILE_COLUMN = 'H_max[T]'
-MINIMUM_PROFILE_COLUMN = 'H_min[T]'
-BLOW_FRACTION_COLUMN  = 'F_B[%]'
-UTILIZATION_HOT_BLOW_COLUMN = 'U_HB[-]'
-UTILIZATION_COLD_BLOW_COLUMN = 'U_CB[-]'
-PRESSURE_DROP_COLD_BLOW_COLUMN =  'dPCB[kPa]'
-PRESSURE_DROP_HOT_BLOW_COLUMN =  'dPHB[kPa]'
[…]

### 2019-11-11 plotprofiles.py

@@ -1,584 +1,0 @@
-import numpy as np
-
-import matplotlib
-from matplotlib import patches
-import matplotlib.pyplot as plt
-
-N_POINTS_LINEPLOT = 2000
-
-FIGSIZE_IN = (8,6)
-DPI = 800
-
-# stolen from https://stackoverflow.com/questions/3899980/how-to-change-the-font-size-on-a-matplotlib-plot
-
-SMALL_SIZE = 16
-MEDIUM_SIZE = 20
-BIGGER_SIZE = 24
-
-plt.rc('text', usetex=True)
-plt.rc(
-    'font', 
-    size=MEDIUM_SIZE,
-    family='serif',
-    serif='Helvetica')          # controls default text sizes
-plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
-plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
-plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
-plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
-plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
-plt.rc('figure', titlesize=BIGGER_SIZE,figsize=FIGSIZE_IN)  # fontsize of the figure title
-
-def calculate_instantaneous_profile(phi, B_low, B_high):
-    """
-    Calculate the value of the two-pole instantaneous magnetic profile at angular position 'phi' (in degrees),
-    where the profile oscillates from 'B_low' to 'B_high'
-    
-    """
-    
-    high_region = (phi < 180)
-                 
-    return np.where(high_region,B_high,B_low)
-
-def calculate_rectified_cosine_profile(phi, B_low, B_high):
-    """
-    Calculate the value of the two-pole rectified cosine magnetic profile at angular position 'phi' (in degrees),
-    where the profile oscillates from 'B_low' to 'B_high'
-    
-    """
-    
-    return B_low + (B_high-B_low)*np.abs(np.cos((np.deg2rad(phi)-np.pi/2)/2))
-
-def calculate_ramp_profile(phi, B_low, B_high, field_fraction):
-    """
-    Calculate the value of the two-pole ramp magnetic profile at angular position 'phi' (in degrees),
[…]

### 2019-11-11 src/figures.py

@@ -1,0 +1,1005 @@
+#!/usr/bin/env python
+# coding: utf-8
+"""
+figures.py
+
+Create all plots for the analysis of magnetic profiles.
+
+The figures are saved in the 'figures'  directory, sister to the
+directory of this script.
+"""
+
+import math
+import re
+import os.path
+from pathlib import Path
+
+import numpy as np
+import numpy.ma as ma
+import pandas as pd
+from pandas import DataFrame, Series
+from scipy.interpolate import griddata
+from scipy.constants import mu_0
+from scipy.integrate import simps
+import matplotlib.pyplot as plt
+
+import loaddatasets as ld
+from plotprofiles import FIGURES_DIR
+
+FIG_FILE_PATH = FIGURES_DIR
+PLOT_EXTENSION = ".eps"
+
+FIGSIZE_IN = (7,5)
+DPI = 600
+
+# stolen from https://stackoverflow.com/questions/3899980/how-to-change-the-font-size-on-a-matplotlib-plot
+SMALL_SIZE = 14
+MEDIUM_SIZE = 20
+BIGGER_SIZE = 22
+
+N_POINTS_LINEPLOT = 2000
+
+DENSITY_GD = 7900 # kg/m3, from Trevizoli et al (2016), IJR volume 72
+
+B_LABEL = r'${B}_\mathrm{high}\,[\mathrm{T}]$'
+Q_LABEL = r'$\dot{Q}_{\mathrm{C}}\,[\mathrm{W}]$'
+COP_LABEL = r'$\mathrm{COP}$'
+W_LABEL = r'$\dot{W}\,[\mathrm{W}]$'
+W_PUMP_LABEL = r'$\dot{W}_\mathrm{pump}\,[\mathrm{W}]$'
+W_MAG_LABEL = r'$\dot{W}_\mathrm{mag}\,[\mathrm{W}]$'
+W_VALVE_LABEL = r'$\dot{W}_\mathrm{valve}\,[\mathrm{W}]$'
+PHI_LABEL = r'$\Phi$'
+H_REG_LABEL = r'$H_\mathrm{r}\,[\mathrm{mm}]$'
+F_B_LABEL = r'$F_\mathrm{B}\,[\%]$'
+RATIO_F_LABEL = r'$\frac{F_\mathrm{M}}{F_\mathrm{B}}$'
[…]

### 2019-11-11 src/loaddatasets.py

@@ -1,0 +1,67 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+"""
+loaddatasets.py
+
+Read the csv files and load them as pandas DataFrames.
+"""
+
+from pathlib import Path
+
+import pandas as pd
+from pandas import DataFrame, Series
+
+SRC_DIR = Path(__file__).resolve().parent
+
+ROOT_DIR = SRC_DIR.parent.resolve()
+
+DATA_DIR = ROOT_DIR/ "data"
+
+INSTANTANEOUS_DATASET = "Instantaneous.csv"
+INSTANTANEOUS_DATASET_VARYING_HEIGHT = "Instantaneous-varH.csv"
+RAMP_DATASET = "Ramp.csv"
+RAMP_DATASET_VARYING_HEIGHT = "Ramp-varH.csv"
+RECTIFIED_COSINE_DATASET = "RectifiedCosine.csv"
+
+
+# These dataset are formated as tab-separed values (TSV), with column names in the format:
+# 
+#     <column_name>[<unit>]
+
+# These files are formatted in such a way that they can be easily loaded with pandas DataFrames.
+# 
+# We adopt the convention of naming these data sets as '<profile_identifier>df', where the profile identifier can be 'it' (instantaneous), 'rc' (rectified cosine) or 'rm' (ramp)
+
+itdf = pd.read_csv(DATA_DIR / INSTANTANEOUS_DATASET)
+it_varH_df = pd.read_csv(DATA_DIR / INSTANTANEOUS_DATASET_VARYING_HEIGHT)
+rcdf = pd.read_csv(DATA_DIR / RECTIFIED_COSINE_DATASET)
+rmdf = pd.read_csv(DATA_DIR / RAMP_DATASET)
+rm_varH_df = pd.read_csv(DATA_DIR / RAMP_DATASET_VARYING_HEIGHT)
+
+
+# The columns of interest can be nicely identified as:
+
+FREQUENCY_COLUMN = 'f[Hz]'
+REGENERATOR_HEIGHT_COLUMN = 'H[mm]'
[…]

### 2019-11-11 src/plotprofiles.py

@@ -1,0 +1,604 @@
+"""
+plotprofiles.py
+
+Create schematic figures for various magnetic and fluid profiles.
+
+The figures are saved in the 'figures'  directory, 
+sister to the directory where this script is placed.
+"""
+
+import numpy as np
+
+import matplotlib
+from matplotlib import patches
+import matplotlib.pyplot as plt
+
+from loaddatasets import ROOT_DIR
+
+N_POINTS_LINEPLOT = 2000
+
+FIGSIZE_IN = (8,6)
+DPI = 800
+
+FIGURES_DIR = (ROOT_DIR / "figures").resolve()
+
+# stolen from https://stackoverflow.com/questions/3899980/how-to-change-the-font-size-on-a-matplotlib-plot
+
+SMALL_SIZE = 16
+MEDIUM_SIZE = 20
+BIGGER_SIZE = 24
+
+plt.rc('text', usetex=True)
+plt.rc(
+    'font', 
+    size=MEDIUM_SIZE,
+    family='serif',
+    serif='Helvetica')          # controls default text sizes
+plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
+plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
+plt.rc('xtick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('ytick', labelsize=SMALL_SIZE)    # fontsize of the tick labels
+plt.rc('legend', fontsize=SMALL_SIZE)    # legend fontsize
+plt.rc('figure', titlesize=BIGGER_SIZE,figsize=FIGSIZE_IN)  # fontsize of the figure title
+
+def calculate_instantaneous_profile(phi, B_low, B_high):
+    """
+    Calculate the value of the two-pole instantaneous magnetic profile at angular position 'phi' (in degrees),
+    where the profile oscillates from 'B_low' to 'B_high'
+    
+    """
+    
+    high_region = (phi < 180)
+                 
+    return np.where(high_region,B_high,B_low)
+
+def calculate_rectified_cosine_profile(phi, B_low, B_high):
+    """
+    Calculate the value of the two-pole rectified cosine magnetic profile at angular position 'phi' (in degrees),
[…]

### 2019-11-11 src/renamefigures.py

@@ -1,0 +1,72 @@
+"""
+renamefigures.py
+
+Rename figures that will appear in the manuscript, with a 
+"FigX-" prefix, and move these copies to the root dir.
+"""
+from pathlib import Path
+from shutil import copy2
+from string import ascii_lowercase
+
+from plotprofiles import FIGURES_DIR, ROOT_DIR
+
+def main():
+    figures_list = [
+        "reg3d.eps",
+        "mprofile.eps",
+        "profiles_it_and_rc.eps",
+        "profile_rm.eps",
+        "profiles_it_and_rc_same_minimum.eps",
+        "profiles_rc_and_flow_instantaneous.eps",
+        "Qc_B_comp_f_1_same_minimum.eps",
+        "COP_B_comp_f_1_same_minimum.eps",
+        "W_B_comp_f_1_Phi_60_same_minimum.eps",
+        (
+            "Qc_Phi_inst_f_1_Hmin_005_FB_100.eps",
+            "Qc_Phi_inst_f_2_Hmin_005_FB_100.eps",
+        ),
+        (
+            "Qc_H_inst_f_1_Phi_40.eps",
+            "COP_H_inst_f_1_Phi_40.eps"
+        ),
+        "amr-casing.eps",
+        "profiles_rm_and_flow_instantaneous.eps",
+        (
+            "Qc_FM_ramp_f_1_Phi_40_35K_1300mT.eps",
+            "COP_FM_ramp_f_1_Phi_40_35K_1300mT.eps"
+        ),
+        (
+            "Qc_FM_ramp_f_1_Phi_20_35K_1300mT.eps",
+            "Qc_FM_ramp_f_1_Phi_50_35K_1300mT.eps"
+        ),
+        (
+            "COP_ramp_map_f_1_Phi_20_FB_60_35K_Valv_ASCO.eps",
+            "COP_ramp_map_f_1_Phi_20_FB_90_35K_Valv_ASCO.eps",
+            "COP_ramp_map_f_1_Phi_40_FB_60_35K_Valv_ASCO.eps",
+            "COP_ramp_map_f_1_Phi_40_FB_90_35K_Valv_ASCO.eps"
+        ),
+        (
+            "Qc_COP_combined_H_regW30.eps",
+            "eta_H_regW30.eps"
+        )
+    ]
+
+    for i, f in enumerate(figures_list):
+
+        if not isinstance(f,tuple):
+            p = Path(FIGURES_DIR / f)
[…]

### 2019-11-11 src/runall.py

@@ -1,0 +1,7 @@
+import plotprofiles
+import figures
+import renamefigures
+
+plotprofiles.main()
+figures.main()
+renamefigures.main()

### 2020-05-04 PaperMagneticProfiles_JBSMSE.tex
Perform major reorganization.
This is a large commit. Scripts, figures, and datasets were moved to
subdirectories. The README was updated to explain the repo structure.
Include reference to GitHub release in manuscript.
Correct spacing in appendix.
Add reference with curves for dtad.
Correct equation of utilization.
The equation for utilization used the solid specific heat in the numerator,
where the correct is to use the fluid specific heat.
Improve explanation of reduction of blow fraction.

@@
 \cite{bib:trevizoli16_perfor_model}.
+Experimental curves of $\dtad$ can be found in \cite{bib:bahl09}.
 
@@
   \label{eq:110}
-  \Phi = \frac{\rate{m}\ped{f,max} F\ped{B} c\ped{s}}{2 f m\ped{s} c\ped{s}}
+  \Phi = \frac{\rate{m}\ped{f,max} F\ped{B} c\ped{f}}{2 f m\ped{s} c\ped{s}}
 \end{equation}
@@
 Simulations were carried out for various values of blow fraction.
-The rectified cosine profile can benefit from a smaller blow fractions that concentrate the flow during the periods of very high and very low fields.
+The rectified cosine profile can benefit from a smaller blow fractions that concentrate the flow during the periods of very high and very low fields, thereby increasing the average variation in magnetic field \cite{bib:nakashima18-influen-exp}; this does not happen with the instantaneous profile, since the field is constant and reducing the blow fraction will only reduce the period where the fluid is in contact with the warmed up solid, decreasing the regenerator effectiveness.
 In this section, all results use the critical value of blow fraction that maximized the cooling capacity: fluid flowing during the entire period for the instantaneous profile, and only during \SI{60}{\percent} of the period (the smallest blow fraction tested) for the cosine profile; this latter case is shown in \autoref{fig:cos-inst-60}.
@@
 
+\section*{Supplementary Material}
+\label{sec:suppl-mater}
+
+The datasets for the results shown in this paper, the source code used to produce the figures and the \LaTeX{} manuscript for this work are available at \cite{bib:fortkamp19-repo-pprof}.
+
 \section*{Conflict of Interest Statement}
@@
 
-\bibliography{thermo-ref/Thermo-Foam-Ref,thesis}
+\bibliography{Thermo-Foam-Ref,thesis}
 

### 2020-05-04 PaperMagneticProfiles_JBSMSE.tex
Clarify description of figure of comparison between profiles.
Explain why cooling capacity is non-linear with utilization.

@@
   \includegraphics[width=7cm]{Fig6-profiles_rc_and_flow_instantaneous}
-  \caption{Rectified cosine magnetic profile and the instantaneous flow profile with blow fraction of \SI{60}{\percent}}
+  \caption{Rectified cosine magnetic profile (solid lines) and the instantaneous flow profile  with blow fraction of \SI{60}{\percent} (dashed lines)}
   \label{fig:cos-inst-60}
@@
 The instantaneous profile almost always yields a higher performance, and since the average field during the hot cycle (high field stage) is the same, the main difference is due to the low magnetic field levels.
-In this comparison, the instantaneous profile is capable of keeping a low magnetic field over the entire half-cycle, which is beneficial for performance;  for $\Phi=1.0$ and $B\ped{high} = \SI{1.40}{\tesla}$, the cooling capacity for the instantaneous profile is $\SI{196.3}{\percent}$ higher than for the cosine profile.
-As demonstrated by \cite{bib:asme-mce}, a higher average magnetic field during the low-field stage increases the solid temperature and consequently results in  warmer fluid entering the cold heat exchanger, representing a thermal loss.
+In this comparison, the instantaneous profile is capable of keeping a low magnetic field over the entire half-cycle, which is beneficial for performance; as demonstrated by \cite{bib:asme-mce}, a higher average magnetic field during the low-field stage increases the solid temperature and consequently results in  warmer fluid entering the cold heat exchanger, representing a thermal loss.
+Analyzing points of different profiles of constant utilization (which should result in the same regenerator effectiveness),
+ for $\Phi=1.0$ and $B\ped{high} = \SI{1.40}{\tesla}$, the cooling capacity for the instantaneous profile is $\SI{196.3}{\percent}$ higher than for the cosine profile.
+This is the result of the fluid being able to cool down to lower temperatures during the low-field cycle, since the cosine profile cannot maintain the field as low as the instantaneous profile (cf.
+\autoref{fig:comparison-methods-profiles}), even with the reduction of blow fraction.
 
@@
 This increases the heat transfer rate, as previously explained ---  outweighing the effects of the magnetic field.
+
+Also noticeable in \autoref{fig:cos_ins} is the non-linear relationship  between cooling capacity and utilization.
+For instance, for the ``RC'' profile at the highest magnetic field, the cooling capacity increases when the utilization grows from 0.2 to 0.6, but then return to the same levels with a further increase of utilization to 1.0.
+Since the frequency is constant for \autoref{fig:cos_ins}, increasing utilization means increasing the mass flow rate; initially, this results in higher heat transfer rates due to higher Nusselt numbers, but further increase reduce the effectiveness and amplify viscous dissipation, to the point where the cooling capacity is null for certain points with the highest utilization.
 

### 2020-05-18 src/plotprofiles.py
Increase font size of profile figures

@@ -24,9 +24,9 @@ FIGURES_DIR = (ROOT_DIR / "figures").resolve()
 
 # stolen from https://stackoverflow.com/questions/3899980/how-to-change-the-font-size-on-a-matplotlib-plot
 
-SMALL_SIZE = 16
-MEDIUM_SIZE = 20
-BIGGER_SIZE = 24
+SMALL_SIZE = 26
+MEDIUM_SIZE = 28
+BIGGER_SIZE = 30
 
 plt.rc('text', usetex=True)
 plt.rc(
@@ -140,12 +140,12 @@ def plot_all_profiles():
     profile_axes.set_xlim(0,np.max(time))
     profile_axes.set_xticks(np.linspace(0,np.max(time),5))
     profile_axes.xaxis.grid(True)
-    profile_axes.set_xticklabels([r'$0$', r'$\frac{\tau}{4}$', r'$\frac{\tau}{2}$',r'$\frac{3\tau}{4}$',r'$\tau$'])
+    profile_axes.set_xticklabels([r'$0$', r'$\frac{\tau}{4}$', r'$\frac{\tau}{2}$',r'$\frac{3\tau}{4}$',r'$\tau$'],fontsize=SMALL_SIZE)
 
     profile_axes.set_yticks([B_min,(B_max+B_min)/2,B_max])
     profile_axes.set_yticklabels([r'${B}_\mathrm{min}$',
                                   r'$\frac{\left({B}_\mathrm{max}+{B}_\mathrm{min}\right)}{2}$',
-                                  r'${B}_\mathrm{max}$'])
+                                  r'${B}_\mathrm{max}$'],fontsize=SMALL_SIZE)
     profile_axes.yaxis.grid(True)
 
     profile_axes.set_xlabel(r'$t$')
@@ -193,11 +193,11 @@ def plot_it_and_rc_profiles():
     profile_axes.set_xlim(0,np.max(time))
     profile_axes.set_xticks(np.linspace(0,np.max(time),5))
     profile_axes.xaxis.grid(True)
-    profile_axes.set_xticklabels([r'$0$', r'$\frac{\tau}{4}$', r'$\frac{\tau}{2}$',r'$\frac{3\tau}{4}$',r'$\tau$'])
[…]

### 2020-05-19 PaperMagneticProfiles_JBSMSE.tex
Merge local repo with Overleaf.
After corrections from JRB, with additions to BibTeX, I downloaded the manuscript from Overleaf into this repo.

I don't have yeat a premium account and cannot automatically sync.

Most figures only had the date metadata changed, but I'm merging everything for consistency.

--- 2019-11-05 PaperMagneticProfiles_JBSMSE.tex
@@
 \usepackage{mathptmx}
-\journalname{Journal of the Brazilian Society of Mechanical Sciences and Engineering}
+\journalname{J. Braz. Soc. Mech. Sci. Eng.}
 
@@
 Although mechanical vapor compression has been the dominant cooling technology for the past century \cite{bib:nik}, it still faces a number of challenges related to its environmental footprint.
-For instance, the phase-out of refrigerants with ozone depleting and global warming potentials brought about a more widespread use of flammable substances, which pose a new set of concerns, restrictions and new technological challenges for consumer applications \cite{bib:iir-flammable, bib:lionte18-adapt}.
+For instance, the phase-out of refrigerants with ozone depleting and global warming potentials brought about a more widespread use of flammable substances, which pose a new set of concerns, restrictions and \textcolor{blue}{additional} technological challenges for consumer applications \cite{bib:iir-flammable, bib:lionte18-adapt}.
 
@@
 The magnitude of the MCE depends on  material properties, magnetic field variation and temperature, and it is maximum at the Curie temperature of the material \cite{bib:smith-magneto, bib:kitanovski}.
-Applications of the MCE at near room-temperature are not restricted to cooling applications \cite{bib:gimaev19-review-htsc,bib:greco19}; it can also be applied to the development of thermomagnetic motors \cite{bib:kaneko19-desig}.
+Applications of the MCE at near room-temperature are not restricted to cooling applications \cite{bib:gimaev19-review-htsc,bib:greco19}; it can also be applied to the development of thermomagnetic motors \cite{bib:kit2020rev, bib:kaneko19-desig}.
 
@@
 To amplify this temperature change, heat regeneration is usually employed \cite{bib:kitanovski}.
-Active magnetic regenerators (AMR) are thermal devices in which the magnetocaloric material is packed as a porous matrix subjected to periodic flow of an aqueous heat transfer fluid.
-The flow is put in sync with successive magnetization and demagnetization steps of the MCM in the porous bed to produce a refrigerating effect.
+Active magnetic regenerators (AMR) are thermal devices in which the magnetocaloric material is packed as a porous matrix subjected to a  periodic flow of an aqueous heat transfer fluid.
+The flow is \textcolor{blue}{synchronized} with successive magnetization and demagnetization steps of the MCM in the porous bed to produce a refrigerating effect.
 Thus, the AMR is essentially a cascade of infinitesimal ``layers'' of MCM that are activated simultaneously to build up a longitudinal temperature profile in the matrix.
@@
 
-A typical AMR cycle is comprised of the following steps: (i) The magnetic circuit magnetizes the MCM, thereby increasing its temperature due to the MCE; (ii) During the \emph{cold blow}, cold fluid previously in thermal contact with the low-temperature source flows through the warm bed, absorbs its energy and releases it as heat to the high-temperature sink through the hot heat exchanger; (iii) The MCM is demagnetized and cooled down as a result; (iv) As the fluid flow is reversed (\emph{hot blow}), it releases energy to the bed, and decreases its temperature so it can absorb the thermal load at the cold heat exchanger in contact with the low-temperature source.
+A typical AMR cycle is comprised of the following steps: (i) The magnetic circuit magnetizes the MCM, thereby increasing its temperature due to the MCE; (ii) During the \emph{cold blow}, cold fluid previously in thermal contact with the low-temperature source flows through the warm bed, absorbs \textcolor{blue}{part of} its energy and releases it as heat to the high-temperature sink through the hot heat exchanger; (iii) The MCM is demagnetized and cooled down as a result; (iv) As the fluid flow is reversed (\emph{hot blow}), it releases energy to the bed, and decreases its temperature so it can absorb the thermal load at the cold heat exchanger in contact with the low-temperature source.
 Different cycles can be devised by changing the duration and synchronization  between the two cycle \emph{characteristic waveforms}:
@@
 
-Fluid flow profiles can be more easily investigated  experimentally, as no changes in the fluid flow hardware are required, provided a reliable and flexible valving system is in place.
+Fluid flow profiles can be more easily investigated experimentally, as no changes in the fluid flow hardware are \textcolor{blue}{generally} required, provided \textcolor{blue}{that} a reliable and flexible valving system is in place.
 In particular, the effect of the \emph{duration} of the fluid blows has been extensively investigated \cite{bib:teyber17_exper,bib:nakashima18-influen-exp,FORTKAMP2018}.
@@
 
-The control of these blow durations can be achieved with the use of solenoid valves; a model for a digital hydraulic system and a calculation of valve power has been presented by  \cite{bib:cardoso16_trans} and \cite{bib:cardoso18}.
-An application of  electronic valves in AMR devices has been presented by \cite{bib:nakashima18-perfor-asses-solen-valves-flow}, using the control logic (for synchronizing the valve operation with the magnetic profile) described by \cite{bib:hoffmann17-actuat}.
+\textcolor{blue}{Controlling the duration of the fluid blows} can be achieved with the use of solenoid valves; a model for a digital hydraulic system and a calculation of valve power has been presented in Refs.~\cite{bib:cardoso16_trans, bib:cardoso18}.
+An application of  electronic valves in AMR devices has been presented in Ref.~\cite{bib:nakashima18-perfor-asses-solen-valves-flow}, using the control logic (for synchronizing the valve operation with the magnetic profile) described in Ref.~\cite{bib:hoffmann17-actuat}.
 
-In contrast, because of the complexities involved in designing and fabricating magnetic circuits, the applied magnetic field profiles (or simply the magnetic waveforms) are much less studied, and are usually investigated in terms of their synchronization with the fluid flow profile with numerical investigations.
-Considering a trapezoidal magnetic profile and a square fluid flow waveform, a numerical analysis showed that small delays between the increase of the magnetic field and the start of the fluid flow is beneficial for the cooling capacity, to assure the solid is fully magnetized before the fluid starts transfering energy from it \cite{bib:bjoerk11_amr}.
-To the authors' knowledge, the only work that experimentally varied the magnetic profile, by controlling the rotation of magnetic cylinders, is the work by \cite{bib:benedict16_desig}, which also showed that cooling capacity of an AMR device is dependent on this lag between magnetization and fluid flow.
+In contrast, because of the complexities involved in designing and fabricating magnetic circuits, the applied magnetic field profiles (or simply the magnetic waveforms) are much less studied, and are usually investigated in \textcolor{blue}{the context} of their synchronization with the fluid flow profile \textcolor{blue}{using} numerical \textcolor{blue}{analysis}.
+Considering a trapezoidal magnetic profile and a square fluid flow waveform, \textcolor{blue}{one of such analyses} showed that small delays between the increase of the magnetic field and the start of the fluid flow \textcolor{blue}{are} beneficial for the cooling capacity, \textcolor{blue}{as they} assure \textcolor{blue}{that} the solid is fully magnetized before \textcolor{blue}{initiating its energy transfer with} the fluid \cite{bib:bjoerk11_amr}.
+To the authors' knowledge, \textcolor{blue}{Ref.~\cite{bib:benedict16_desig} was} the only work to experimentally vary the magnetic profile, by controlling the rotation of magnetic cylinders.
+\textcolor{blue}{They} also showed that \textcolor{blue}{the} cooling capacity of an AMR device \textcolor{blue}{depends on the time} lag between magnetization and fluid flow.
 
-If this delay is further increased so that the fluid flow period can coincide with diferent stages of the magnetic profile, different thermodynamic cycles can be obtained with different performance trends; the Brayton AMR cycle (explained previously) yields the highest cooling capacities, while the Ericsson AMR cycle (with isothermal (de)magnetization steps) yield the highest values of the coefficient of performance \cite{bib:plaznik13-numer}.
-This conclusion was confirmed by the more extensive numerical analysis of \cite{bib:kitanovski}, which also varied the amplitude of the trapezoidal magnetic profile and proposed magnetic circuit designs which could generate these profiles.
-Trevizoli et al.~\cite{bib:asme-mce} carried out a numerical comparison of the square wave (step change), sinusoidal and rectified cosine magnetic profiles for a sinusoidal fluid profile and concluded that the cooling capacity and maximum temperature spans are maximal for the instantaneous magnetic profile.
+If \textcolor{blue}{the time delay between magnetization and fluid displacement} is further increased so that the fluid flow period can coincide with \textcolor{blue}{different} stages of the magnetic profile, different thermodynamic cycles can be obtained with different performance trends; the Brayton AMR cycle (explained previously) yields the highest cooling capacities, while the Ericsson AMR cycle --- with isothermal (de)magnetization steps --- yields the highest values of the coefficient of performance \cite{bib:plaznik13-numer}.
+This conclusion was confirmed by \textcolor{blue}{a} more extensive numerical analysis in Ref.~\cite{bib:kitanovski}, which also varied the amplitude of the trapezoidal magnetic profile and proposed magnetic circuit designs \textcolor{blue}{capable of generating such} profiles.
+Ref.~\cite{bib:asme-mce} carried out a numerical comparison of the square wave (step change), sinusoidal and rectified cosine magnetic profiles for a sinusoidal fluid profile and concluded that the cooling capacity and maximum temperature spans are maximal for the instantaneous magnetic profile.
 
-As previously noted, the fluid flow profile is implemented with proper design of the fluid flow system, while the magnetic profile is an important input when designing a magnetic circuit \cite{bib:oh13-air}.
-With the goal of AMR design, none of works reviewed in this section considered different \emph{shapes} and \emph{amplitudes} of the magnetic field waveform.
-Regarding shape, the combination of a trapezoidal magnetic profile and an instantaneous fluid flow profile is prevalent in the literature \cite{bib:bjoerk11_amr,bib:benedict16_desig,bib:park17-devel-k-k}, and this case is also investigated in the present paper.
-However, sinusoidal magnetic profiles can be achieved with more compact systems \cite{bib:trevizoli16_pump}, and their generation and impact of AMR devices have been investigated by  our group \cite{FORTKAMP201787,bib:fortkamp20-desig}, but no work has investigated how these waveforms, when synchronized with optimized fluid flow profiles, can compare with the instantaneous magnetic profile, which the literature identifies as the optimal one when the fluid flow profile is fixed.
+As previously noted, the fluid flow profile is implemented with a proper design of the fluid flow system, while the magnetic profile is an important input when designing a magnetic circuit \cite{bib:oh13-air}.
+With the goal of AMR design \textcolor{blue}{in mind}, none of \textcolor{blue}{the} works \textcolor{blue}{revised} in this \textcolor{blue}{paper} considered different \emph{shapes} and \emph{amplitudes} of the magnetic field waveform.
+Regarding shape, the combination of a trapezoidal magnetic profile and an instantaneous fluid flow profile \textcolor{blue}{currently prevails} in the literature \cite{bib:bjoerk11_amr,bib:benedict16_desig,bib:park17-devel-k-k}, and this is also \textcolor{blue}{the situation} investigated in the present paper.
+However, sinusoidal magnetic profiles can be achieved with more compact systems \cite{bib:trevizoli16_pump}, and their generation and impact on AMR \textcolor{blue}{performance} have been investigated in  our group \cite{FORTKAMP201787,bib:fortkamp20-desig}.
+\textcolor{blue}{However,} no work has investigated how these waveforms, when synchronized with optimized fluid flow profiles, \textcolor{blue}{measure up against} the instantaneous magnetic profile, which \textcolor{blue}{is recognised in} the literature as the optimal \textcolor{blue}{waveform for} when the fluid flow profile is fixed.
 
-The present work bridges the gaps left in previous studies by investigating the performance of a magnetic refrigerator under different magnetic profile waveforms.
-These waveforms are mathematically modeled, and the cooling capacity and coefficient of performance are calculated based on the profiles parameters, while also investigated how the AMR geometry affect the performance in combinations with the magnetic profile.
-The fluid flow profile is assumed fixed in shape, although its parameters are also varied.
-To emulate constraints on an operating point of actual magnetic refrigeration devices, the temperature span is set fixed, and hence few comments are made on second-law efficiency.
+\textcolor{blue}{As far as the incorporation of the magnetic field waveform in the AMR performance optimization is concerned, the studies published in the open literature can be classified into three categories, namely \textit{segregated}, \textit{semi-segregated} and \textit{integrated} design.
+In the first category, the magnetic field waveform remains constant (i.e., fixed shape and amplitude) during the AMR optimization.
+In the semi-segregated approach, parameters associated with the magnetic field waveform are allowed to change, but no consideration is given to the configuration of the magnetic circuit (i.e., magnet materials, geometry, segmentation) needed to generate such waveforms.
+Finally, in the integrated design approach, the magnetic circuit that generates the waveform is mathematically incorporated in the analysis (through conservation equations and appropriate closure relationships involving the magnetic field), so objective functions may now be formulated involving the mass, size, geometry or material cost of the magnetic circuit.
+Refs.
+~\cite{bib:Momen2014,bib:ZhangSR2017} are examples of segregated AMR optimization.
+In Ref.~\cite{bib:Momen2014}, single-objective optimization coupled with a dimensionless parametric analysis enabled identifying the utilization factor that optimized the performance of Gd-based AMRs in terms of the temperature span and cooling capacity.
+Ref.~\cite{bib:ZhangSR2017} introduced a detailed numerical model of a sixteen-layer La-Fe-Mn-Si-H parallel-plate AMR, and  coupled it with a DoE-based (Design of Experiment)  optimization method.
+A square wave magnetic field waveform with a 1.5-T maximum magnetic flux density was applied.
+Examples of semi-segregated AMR optimization are given in Refs.~\cite{bib:Bouchekara2014,bib:Ganjehsarabi2016,bib:Roy2017}, where  multi-objective optimization techniques were employed to optimize the performance of parallel-plate \cite{bib:Roy2017} and sphere packed-bed AMRs \cite{bib:Ganjehsarabi2016} using methods such as weighted sum, weighted product and genetic algorithms, among others.
+A common finding to all of such studies is that no configuration exists which can simultaneously optimize all objectives (e.g., cooling capacity and temperature span), so a compromise is required according to specified design constraints.
+Finally, in their \textit{integrated} approach to AMR optimization, Ref.~\cite{bib:teyber17_perman} employed a topology-based optimization of the magnetic circuit (using genetic algorithms) to reduce to a minimum the cost of cooling.
+In this sense, not only the capital costs were considered (using simple prismatic magnet segments in the magnetic circuit), but also the operating costs associated with the AMR itself.
+More recently, in Ref.~\cite{bib:fortkamp20-desig}, a magnetic circuit consisting of concentric Halbach cylinders was analytically modelled and integrated with models for the power expenditure of the flow management system and for the fluid flow and heat transfer in the AMR to determine the geometric characteristics of the latter which maximized its performance.
+Designer maps, which embodied the existing trade-offs between the system variables, provided easy visual access to the regenerator dimensions which maximized the cooling capacity or the COP.}
+
+The present work \textcolor{blue}{complements the} previously mentioned studies by investigating the performance of a magnetic refrigerator \textcolor{blue}{subjected to} different magnetic profile waveforms.
+The cooling capacity and \textcolor{blue}{the COP} are calculated \textcolor{blue}{taking account of the magnetic profile} parameters, while also \textcolor{blue}{considering} how the AMR geometry affects the performance \textcolor{blue}{parameters in conjunction} with the magnetic profile.
+\textcolor{blue}{To simplify the analysis,} the \textcolor{blue}{shape of the} fluid flow \textcolor{blue}{waveform} is assumed fixed, \textcolor{blue}{but some of} its parameters are also varied.
+To emulate constraints on an operating point of actual magnetic refrigeration devices, the temperature span is kept fixed, so a few comments are made \textcolor{blue}{regarding the} second-law efficiency.
 
@@
 
-As previuosly explained, we performed numerical simulations using a previously developed AMR model, varying the profile-specific and geometric parameters.
+As explained \textcolor{blue}{before}, we performed numerical simulations using a previously developed AMR model, varying the profile-specific and geometric parameters.
 We also implemented a model to calculate the power consumption of a novel fluid management system, which is a topic not yet extensively studied in the literature.
@@
 Initial and boundary conditions, closure relations for the porous media terms, solution methods and convergence criteria and analyses are discussed in detail in \cite{bib:trevizoli16_perfor_model}.
-This AMR model solves the above equations for one regenerator operating between given sources temperatures (assuming ideal heat exchangers in contact with the thermal reservoirs), during one full cycle (hot and cold blows and  magnetization and demagnetization periods), given specified operating conditions (to be discussed later).
+This AMR model solves the above equations for one regenerator operating between given source temperatures (assuming ideal heat exchangers in contact with the thermal reservoirs), during one full cycle (hot and cold blows and  magnetization and demagnetization periods), given specified operating conditions (to be discussed later).
 
@@
 \noindent where \(g(t)\) is a dimensionless function that expresses the mathematical waveform of the pressure gradient, and  \(A\ped{t}\) is its amplitude,  adjusted in a convergence loop.
-In this loop, the mass flow rate calculated in term of the Darcy velocity from \autoref{eq:75} is compared with the input   mass flow rate until convergence is obtained.
+In this loop, the mass flow rate calculated in terms of the Darcy velocity from \autoref{eq:75} is compared with the input   mass flow rate until convergence is obtained.
 
@@
 
-The profile can be mathematically defined as:
+The \textcolor{blue}{fluid flow} profile can be mathematically defined as:
 
@@
 
-When the blows have different time durations, the AMR cycle is considered unbalanced, and that is known to have a negative effect on performance \cite{bib:eriksen16_effec,bib:nakashima18-influen-exp}.
+When the blows have different time durations, the AMR cycle is considered unbalanced, and that is known to have a negative effect on performance \cite{bib:nakashima18-influen-exp, bib:eriksen16_effec}.
 In this work, the blows are always balanced, hence the blow fraction, i.e., the ratio of blow durations to cycle period \cite{bib:nakashima18-influen-exp}, can be evaluated as:
@@
 
-The magnetocaloric effect is implemented in the so-called discrete approach \cite{bib:nielsen11_review}; every time the magnetic field changes, based on the input magnetic profile, the solid temperature is calculated according to:
+The magnetocaloric effect is implemented \textcolor{blue}{using} the so-called discrete approach \cite{bib:nielsen11_review}; every time the magnetic field changes, based on the input magnetic profile, the solid temperature is calculated according to:
 
@@
 
-\noindent where the adiabatic temperature variation, $\dtad$, a standard measure of the MCE, is calculated from tabulated experimental data for magnetocaloric materials as function of temperature and effective field.
-\cite{bib:trevizoli16_perfor_model}.
+\noindent where the adiabatic temperature variation, $\dtad$, a standard measure of the MCE, is calculated from tabulated experimental data for magnetocaloric materials as function of temperature and effective field \cite{bib:trevizoli16_perfor_model}.
+\textcolor{blue}{Experimental curves for  $\dtad$ as a function of temperature and magnetic field change can be found in Ref.~\cite{bib:bahl09}}.
 
-The magnetic profiles considered in this work are presented in terms of the flux density $B = \mu_0 H$, where $\mu_0$ is the permeability of free space; the magnetic field $H$ is used in the evaluation of the magnetocaloric effect (cf.
-Sec.~\ref{sec:how-magnetic-profile}).
+The magnetic profiles considered in this work are presented in terms of the flux density $B = \mu_0 H$, where $\mu_0$ is the permeability of free space; the magnetic field $H$ is used in the evaluation of the magnetocaloric effect.
 
@@
 
-\noindent such that there are four ramp periods in one full cycle. The ramp rate, \(\tan \theta\ped{R}\), is:
+\noindent such that there are four ramp periods in one full cycle. The ramp rate, \(\tan \theta\ped{R}\), is \textcolor{blue}{given by}:
 
@@
 The properties are computed at the average temperature between the hot and cold sources, and are evaluated from interpolation of tables imported from the EES software \cite{bib:klein13-ees}.
-In all simulations shown in this work, the heat transfer fluid is a \num{80}/\SI{20}{\percent} vol.~mixture of water/ethylene-glycol.
+In all simulations shown in this work, the heat transfer fluid is a \num{80}/\SI{20} vol.\% mixture of water/ethylene-glycol.
 For the energy equations, the fluid properties are also calculated from tabulated data, but the temperature dependence is considered.
@@
 
-For the multilayer simulations, alloys of gadolinium and yttrium are used in the form \ce{Gd_{1-x}Y_x}, where $x$ is the yttrium fraction.
+For the multilayer simulations, gadolinium-yttrium alloys are used,  \ce{Gd_{1-x}Y_x}, where $x$ is the yttrium fraction.
 This fraction reduces the Curie temperature of the alloy relative to that of pure gadolinium.
@@
 
-The AMR model is solved for only one bed, but  assumes that the $N\ped{reg}$ identical beds experience the same cycle. Thus, the extensive performance parameters are multiplied by that factor.
+The AMR model is solved for only one bed, but  assumes that the $N\ped{reg}$ identical beds experience the same cycle.
+Thus, the extensive performance parameters are multiplied by that factor.
+The cooling capacity is calculated as \cite{bib:trevizoli16_perfor_model}:
 
 \nomenclature[an]{$N\ped{reg}$}{number of regenerators}
-
-The cooling capacity is calculated as \cite{bib:trevizoli16_perfor_model}:
 
@@
 
-As pointed out in \cite{bib:fortkamp20-desig}, since external sources of irreversibility (e.g., heat transfer with a finite temperature difference in the heat exchangers) are ignored and no eddy currents and hysteresis losses are present, the magnetic power required to magnetize the solid refrigerant and produce the MCE in the AMR cycle is given by the product of the Carnot efficiency and the cooling capacity as follows:
+As pointed out in Ref.~\cite{bib:fortkamp20-desig}, since external sources of irreversibility (e.g., heat transfer with a finite temperature difference in the heat exchangers) are ignored and no eddy currents and hysteresis losses are present, the magnetic power required to magnetize the solid refrigerant and produce the MCE in the AMR cycle is given by the product of the Carnot efficiency and the cooling capacity as follows:
 
@@
 In the present analysis, two types of valves are considered.
-In the first approach, called \emph{Type R valves}, the  model proposed in \cite{bib:cardoso16_trans} is used, assuming that the individual consumption of each valve is independent of frequency and blow fraction.
-The valve power  $\wvalve$ can be computed as:
+In the first approach, called \emph{Type R valves}, the  model proposed in Ref.~\cite{bib:cardoso16_trans} is used, assuming that the individual \textcolor{blue}{power} consumption of each valve is independent of frequency and blow fraction.
+The valve power,  $\wvalve$, can be computed as:
 
@@
 
-In the second approach, \emph{Type S} valves are used, with  nominal power lower in magnitude but which depends on frequency and blow fraction.
-These valves were experimentally characterized by \cite{bib:cardoso18}, where a single valve was attached to a measurement circuit and set to operate for varying values of blow fraction and frequency; the valve power was calculated from the averaged values of voltage and current after periodic steady state was reached.
-From these experiments, the valve power was experimentally correlated as:
+In the second approach, \emph{Type S} valves are used, \textcolor{blue}{which have a} nominal power lower in magnitude, but which depends on the  frequency and blow fraction.
+These valves were experimentally characterized \textcolor{blue}{in Ref.~\cite{bib:cardoso18}}, where a single valve was attached to a measurement circuit and set to operate for \textcolor{blue}{a range of} values of blow fraction and frequency; the valve power was calculated from the averaged values of voltage and current after the periodic steady state was reached.
+From those experiments, the valve power was experimentally correlated as:
 
@@
 Equation~\eqref{eq:198} was correlated for blow fractions of \num{50} and \SI{100}{\percent} and frequencies in the range of \num{0.2}--\SI{1.6}{\hertz}, with an uncertainty on the order of \SI{0.4}{\watt} for a single valve.
-The use of different valve types will be discussed among the presented results.
+The use of different valve types will be discussed \textcolor{blue}{in the Results section}.
 
-Independent of the valve type used, it is also assumed that each valve system can produce the fluid flow profile shown in \autoref{fig:mprofile}, where the displaced fluid mass during one blow in one regenerator bed is $\rate{m}\ped{f,max} F\ped{B} \nicefrac{\tau}{2}$.
+Independent of the valve type used, it is also assumed that each valve system \textcolor{blue}{is capable of producing} the fluid flow profile shown in \autoref{fig:mprofile}, where the displaced fluid mass during one blow in one regenerator bed is $\rate{m}\ped{f,max} F\ped{B} \nicefrac{\tau}{2}$.
 The \emph{utilization factor} can then be calculated as:
@@
 
-\subsection{Calculation of the coefficient of performance}
+\subsection{Coefficient of performance and second-law efficiency}
 \label{sec:calc-coeff-perf}
 
-The coefficient of performance takes the cooling capacity as the main output parameter from the AMR model, in addition to all previously cited power contributions:
+The coefficient of performance \textcolor{blue}{is calculated as the ratio of} the cooling capacity --- the main output parameter from the AMR model --- \textcolor{blue}{and} all previously cited power contributions:
 
@@
 
+The maximum possible COP between the source temperatures is the Carnot COP, calculated as:
+
+\begin{equation}
+    \label{eq:copcarnot}
+    \cop\ped{Carnot} = \frac{T\ped{C}}{T\ped{H} - T\ped{C}}
+\end{equation}
+
+\noindent and the second-law efficiency is defined as:
+
+\begin{equation}
+    \label{eq:eta2}
+    \etasec = \frac{\cop}{\cop\ped{Carnot}}
+\end{equation}{}
+
+\nomenclature[azn]{$\etasec$}{second-law efficiency}
 \section{Results and Discussions}
@@
 
-The analysis of magnetic profiles was performed at two different stages.
+The analysis of the magnetic profiles was performed at two different stages.
 Initially, the instantaneous (square-wave) and the rectified cosine profiles are compared using a simpler approach (i.e., neglecting casing losses).
-Later, based on the selection of the most promising magnetic profile, a more in-depth analysis is carried out to determine the optimal geometric and operating parameters of the AMR system.
+Later, based on the selection of the most promising magnetic profile, a more in-depth analysis was carried out to determine the optimal geometric and operating parameters of the AMR system.
 
@@
 For the cold cycle, the minimum values for both profiles are the same, as shown in \autoref{fig:comparison-methods-profiles}.
-For reference, in all simulations,  the minimum value for the rectified cosine was fixed at ${B}\ped{min} = \SI{0.1}{\tesla}$.
+\textcolor{blue}{As a} reference, in all simulations,  the minimum value for the rectified cosine was fixed at ${B}\ped{min} = \SI{0.1}{\tesla}$.
 
@@
 Simulations were carried out for various values of blow fraction.
-The rectified cosine profile can benefit from a smaller blow fractions that concentrate the flow during the periods of very high and very low fields.
+The rectified cosine profile can benefit from smaller blow fractions that concentrate the flow during the periods of very high and very low fields, \textcolor{blue}{thereby increasing the average variation in magnetic field \cite{bib:nakashima18-influen-exp}; this is not observed with the instantaneous profile, since the field is constant and reducing the blow fraction will only reduce the period when the fluid is in contact with the warm  solid, decreasing the regenerator effectiveness}.
 In this section, all results use the critical value of blow fraction that maximized the cooling capacity: fluid flowing during the entire period for the instantaneous profile, and only during \SI{60}{\percent} of the period (the smallest blow fraction tested) for the cosine profile; this latter case is shown in \autoref{fig:cos-inst-60}.
@@
   \includegraphics[width=7cm]{Fig6-profiles_rc_and_flow_instantaneous}
-  \caption{Rectified cosine magnetic profile and the instantaneous flow profile with blow fraction of \SI{60}{\percent}}
+  \caption{\textcolor{blue}{Rectified cosine magnetic profile (solid lines) and the instantaneous flow profile  with blow fraction of \SI{60}{\percent} (dashed lines)}}
   \label{fig:cos-inst-60}
@@
 
-Figure~\ref{fig:cos_ins} shows the cooling capacity attained by the device at a frequency of \SI{1}{\hertz} and different utilizations.
+\textcolor{blue}{Figure~\ref{fig:cos_ins} shows the cooling capacity attained by the device at a frequency of \SI{1}{\hertz} for different utilizations.
 The horizontal axis shows the average field value during the high field region.
 The instantaneous profile almost always yields a higher performance, and since the average field during the hot cycle (high field stage) is the same, the main difference is due to the low magnetic field levels.
-In this comparison, the instantaneous profile is capable of keeping a low magnetic field over the entire half-cycle, which is beneficial for performance;  for $\Phi=1.0$ and $B\ped{high} = \SI{1.40}{\tesla}$, the cooling capacity for the instantaneous profile is $\SI{196.3}{\percent}$ higher than for the cosine profile.
-As demonstrated by \cite{bib:asme-mce}, a higher average magnetic field during the low-field stage increases the solid temperature and consequently results in  warmer fluid entering the cold heat exchanger, representing a thermal loss.
+In this comparison, the instantaneous profile is capable of keeping a low magnetic field over the entire half-cycle, which is beneficial for performance; as demonstrated in Ref.~\cite{bib:asme-mce}, a higher average magnetic field during the low-field stage increases the solid temperature and consequently results in  warmer fluid entering the cold heat exchanger, representing a thermal loss.
+Analyzing points of different profiles of constant utilization (which should result in the same regenerator effectiveness),
+ for $\Phi=1.0$ and $B\ped{high} = \SI{1.40}{\tesla}$, the cooling capacity for the instantaneous profile is $\SI{196.3}{\percent}$ higher than for the cosine profile.
+This results from the fluid being able to cool down to lower temperatures during the low-field cycle, since the cosine profile cannot maintain the field as low as the instantaneous profile (cf.
+\autoref{fig:comparison-methods-profiles}), even with the reduction of blow fraction.}
 
@@
 
+\textcolor{blue}{Also noticeable in \autoref{fig:cos_ins} is the non-linear relationship  between cooling capacity and utilization.
+For instance, for the ``RC'' profile at the highest magnetic field, the cooling capacity increases when the utilization is raised from 0.2 to 0.6, but then returns to the same levels with a further increase of the utilization to 1.0.
+Since the frequency is constant in \autoref{fig:cos_ins}, increasing the utilization means increasing the mass flow rate; initially, this results in higher heat transfer rates due to higher Nusselt numbers, but further increase reduces the effectiveness and amplifies viscous dissipation, to the point where the cooling capacity is null for certain points with the highest utilization.}
+
 The same analysis, but in terms of the coefficient of performance, is shown in \autoref{fig:cos_ins_cop}, where  the instantaneous profile yields better results for medium to high levels of utilization.
-This is explained by the behavior of the magnetic, valve and pumping power shown in   \autoref{fig:cos_ins_w} for a fixed utilization of 0.6.
+This can be explained based on the behavior of the magnetic, valve and pumping powers shown in   \autoref{fig:cos_ins_w} for a fixed utilization of 0.6.
 As can be seen, the magnetic power only differs between the profiles due to changes in cooling capacity.
 Also, the valve power is higher for the instantaneous profile since the valves must remain open for longer periods.
-However, the proportional increase in pumping power, due to arger larger flow rates, is even higher (than the change in valve power).
+However, the proportional increase in pumping power, due to larger larger flow rates \textcolor{blue}{when operating with the smaller blow fraction of the ``RC'' profile}, is even higher (than the change in valve power).
+\textcolor{blue}{Although not shown in \autoref{fig:cos_ins_w}, the effect of higher utilization levels is to make the pumping power even more relevant; as depicted in \autoref{fig:cos_ins_cop}, the lowest levels of the coefficient of performance are attained with the smallest blow fraction (for the rectified cosine profile) and higher utilization, corresponding to the highest flow rate levels.}
 
@@
   \includegraphics[width=10cm]{Fig9-W_B_comp_f_1_Phi_60_same_minimum}
-  \caption{Power contributions as functions of the average high magnetic field, for a utilization of 0.6.
+  \caption{Power contributions as a function of the average high magnetic field, for a utilization of 0.6.
 ``IT'': instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}).}
@@
 For higher magnetic fields, the increase in the MCE surpasses the loss of effectiveness, and one can go to higher flow rates without losing performance.
-It can also be seen in Fig.~\ref{fig:qc_phi_inst} that at  higher frequencies the values of cooling power are higher, and also the critical values of utilization are lower.
-However, this is usually achieved at the expense of a higher power consumption in AMR devices at higher frequencies \cite{bib:lei15_study,NIKNIA2016601}.
+It can also be seen in Fig.~\ref{fig:qc_phi_inst} that at  higher frequencies the values of cooling capacity are higher, and also the critical values of utilization are lower.
+However, this is usually achieved at the expense of \textcolor{blue}{an even} higher power consumption at higher frequencies \cite{bib:lei15_study,NIKNIA2016601}, resulting in a decrease of the coefficient of performance with frequency.
+\textcolor{blue}{Critical values of utilization that maximize the COP (all other parameters fixed) are also observed, but these tend to be smaller than the critical values for cooling capacity; at higher utilization levels, the pumping power increases more rapidly than the cooling capacity.}
 
@@
 To understand the impact of the regenerator geometry on the system performance with the instantaneous profile, the regenerator height was varied in Fig.~\ref{fig:Qc_H_inst}, and all other parameters from \autoref{tab:params-cobem} were kept fixed and with $\phi=0.4$.
+\textcolor{blue}{The height was chosen as the geometric parameter to be varied as it usually represents a design trade-off in magnetic refrigerators \cite{bib:fortkamp20-desig}: taller regenerator cross-sections allow for more magnetocaloric material while reducing the volume of the magnetic circuit (cf.
+\autoref{fig:amr-casing}).}
+
 As expected, higher magnetic fields allow for smaller regenerators (hence more compact systems) to achieve a desired cooling capacity.
 For instance, to achieve a capacity of \SI{100}{\watt}, increasing the field from \num{1.0} to \SI{1.2}{\tesla} results in regenerators that are \SI{36}{\percent} smaller.
-Comparing the results for the cooling capacity and coefficient of performance, the trends are largely the same, as the former is more sensitive to variations in the magnetic field and regenerator height than the components of power.
+Comparing the results for the cooling capacity and coefficient of performance, the trends are largely the same, as the former is more sensitive to variations in the magnetic field and regenerator height than the components of power; \textcolor{blue}{note that
+increasing the regenerator height increases the  mass of magnetocaloric material, hence increasing the cooling capacity, but it also changes the area available for the fluid flow (influencing pumping power) and the demagnetization factor (influencing the magnetic power).}
 
@@
 
-Moving towards a more realistic model, casing losses are included, using the model from \cite{bib:trevizoli16_perfor_model}.
+Moving towards a more realistic model, casing losses are included, using the model from Ref.~\cite{bib:trevizoli16_perfor_model}.
 The bed is enclosed in a solid casing of thickness $h\ped{csg}$, and two air layers of thickness $h\ped{air}$ separate the AMR and its casing from the inner and outer magnet cylinders, as shown in \autoref{fig:amr-casing}.
@@
 
-Preliminary analyses carried out by \cite{bib:peixer17-perfor-amrs} showed that a stainless steel casing with a thickness of $h\ped{csg} = \SI{0.5}{\mm}$ is thick enough to ensure mechanical integrity and easy manufacturing, while being thin enough to accommodate the material with a low thermal conductivity.
+Preliminary analyses carried out in Ref.~\cite{bib:peixer17-perfor-amrs} showed that a stainless steel casing with a thickness of $h\ped{csg} = \SI{0.5}{\mm}$ is thick enough to ensure mechanical integrity and easy manufacturing, while being thin enough to accommodate the material with a low thermal conductivity.
 
@@
 The simulations in this section also use multilayer regenerators.
-A summary of all parameters adopted in this section, including the Curie temperatures and volumetric fractions (relative to the length of the bed) of each layer is presented in \autoref{tab:params-ramp}.
+A summary of all parameters adopted in this section, including the Curie temperatures and volumetric fractions (relative to the length of the bed) of each layer is presented in \autoref{tab:params-ramp}; more details on the selection of these parameters are shown in Ref.~\cite{bib:neves18-numer-gd-y}.
 In addition, in the following results, Type S valves are used, with valve power calculated by \autoref{eq:198}.
@@
  Figure~\ref{fig:ramp-inst} shows the two profiles that will be used in this section and how they are synchronized.
-Regarding the magnetic profile, the magnitude of the high value will be varied to investigate the performance of the AMR system, while the minimum will be kept at $\bmin = \SI{0.05}{\tesla}$.
+Regarding the magnetic profile, the magnitude of the high value will be varied to investigate the performance of the AMR system, while the minimum will be kept \textcolor{blue}{fixed} at $\bmin = \SI{0.05}{\tesla}$.
 
@@
 The reduction in performance for $F\ped{M} > F\ped{B}$ can be explained by an increase in heat leakage through the casing, as the solid begins to lose energy to the environment when the fluid is not flowing.
-For $F\ped{M} < F\ped{B}$,  the fluid begins to flow when the solid is not totally warmed up, losing effectiveness.
+For $F\ped{M} < F\ped{B}$,  the fluid begins to flow when the solid is not totally warmed up, losing effectiveness, \textcolor{blue}{and this effect is amplified with larger blow fraction values; notice that, to the left of the peak, the performance parameters are the lowest for the highest value of $F\ped{B}$.}
 
@@
 
-When comparing the instantaneous  and the rectified cosing magnetic profiles, the cooling capacity associated with the former can be almost \SI{200}{\percent} higher than with the latter, for the same utilization and average high magnetic field and considering optimal blow fractions.
-The rectified cosing profile suffers from high values of the low magnetic field, and reduction of blow fraction up to the minimum tested value of \SI{60}{\percent} is not enough to overcome the loss in cooling capacity resulting from this effect.
+When comparing the instantaneous  and the rectified \textcolor{blue}{cosine} magnetic profiles, the cooling capacity associated with the former can be almost \SI{200}{\percent} higher than with the latter, for the same utilization and average high magnetic field and considering optimal blow fractions.
+The rectified \textcolor{blue}{cosine} profile suffers from high values of the low magnetic field, and reduction of blow fraction up to the minimum tested value of \SI{60}{\percent} is not enough to overcome the loss in cooling capacity resulting from this effect.
 
@@
 The ramp magnetic profile is a feasible approximation for the instantaneous profile without abrupt changes in the magnetic field plateaus.
-For an AMR device operating with this  profile and the instantaneous fluid flow profile, both cooling capacity and coefficient of performance are maximized if the blow duration is equal to the period of constant magnetic field; if this exact synchronization is not possible, making the magnetization plateau wider than the flow plateau results in smaller reduction of the performance metrics than if it is narrower.
+For an AMR device operating with this  profile and the instantaneous fluid flow profile, both cooling capacity and coefficient of performance are maximized if the blow duration is equal to the period of constant magnetic field; if this exact synchronization is not possible, making the magnetization plateau wider than the flow plateau results in a smaller reduction of the performance metrics than \textcolor{blue}{in the case where the magnetization plateau} is narrower.
 
-With this strategy and using average values of utilization, it is possible to achieve second-law efficiency levels compatible with vapor-compression systems.
+With this strategy and using average values of utilization, it is possible to achieve second-law efficiency levels compatible with \textcolor{blue}{those of} vapor-compression systems.
 Hence the ramp magnetic profile is identified as a suitable target profile in the design of magnetic circuits for AMR devices.
+
+% \section*{Supplementary Material}
+% \label{sec:suppl-mater}
+
+% The datasets for the results shown in this paper, the source code used to produce the figures and the \LaTeX{} manuscript for this work are available at \cite{bib:fortkamp19-repo-pprof}.
+
+% NA MINHA OPINIAO O SUPPLEMENTARY MATERIAL EH DESNECESSARIO
 
@@
 
-\acknowledgement{This work was funded by the Brazilian Federal Government (CAPES PTI program, Process no.
-88887.194773/2018-00, CNPq Grant no.
-443696/2014-4 and EMBRAPII) and by the State of Santa Catarina (FAPESC/INCT).
-The authors acknowledge the continuous support from Embraco.
-}
+\acknowledgement{This work was funded by the INCT (National Institutes of Science and Technology) Program (CNPq Grant no.
+443696/2014-4; FAPESC Grant no.2018TR1576).
+Additional funding was provided by CAPES (Talents for Innovation Program - Grant No.~88887.194773/2018-00) to F.
+Fortkamp and J.
+Lozano.
+Financial support from EMBRAPII, Embraco and CODEMGE is also acknowledged.}
 

### 2020-05-19 PaperMagneticProfiles_JBSMSE.tex
Remove reference to supplementary material per JRB request.
Review and complete list of symbols.

@@
 
-\nomenclature[vm]{AMR}{Active Magnetic Regenerator}
+\nomenclature[va]{AMR}{Active Magnetic Regenerator}
 
@@
 Designer maps, which embodied the existing trade-offs between the system variables, provided easy visual access to the regenerator dimensions which maximized the cooling capacity or the COP.}
+
+\nomenclature[vd]{DoE}{design of experiments}
 
@@
 \nomenclature[ah]{$\hheat$}{heat transfer coefficient [\si{\watt\per\meter\squared\per\kelvin}]}
-\nomenclature[aa]{$A\ped{sf}$}{contact surface area between solid and fluid phases in the regenerator [\si{\meter^2}]}
 \nomenclature[is]{sf}{relative to the heat transfer between solid and fluid phases in the regenerator}
@@
   \label{eq:58}
-  \wvalve = N\ped{v}F\ped{B}\left(\wvalven + \frac{1}{2}\wrelayn\right)
+  \wvalve = N\ped{valve}F\ped{B}\left(\wvalven + \frac{1}{2}\wrelayn\right)
 \end{equation}
@@
 \nomenclature[an]{$N\ped{valve}$}{number of valves}
-\nomenclature[aw]{$\wvalve$}{valve power [\si{\watt}]}
-\nomenclature[aw]{$\wvalven$}{nominal power comsumption of one valve [\si{\watt}]}
-\nomenclature[aw]{$\wrelayn$}{nominal power comsumption of one relay [\si{\watt}]}
+\nomenclature[awn]{$\wvalve$}{valve power [\si{\watt}]}
+\nomenclature[awn]{$\wvalven$}{nominal power comsumption of one valve [\si{\watt}]}
+\nomenclature[awn]{$\wrelayn$}{nominal power comsumption of one relay [\si{\watt}]}
 
@@
   \label{eq:110}
-  \Phi = \frac{\rate{m}\ped{f,max} F\ped{B} c\ped{f}}{2 f m\ped{s} c\ped{s}}
+  \Phi = \frac{\rate{m}\ped{f,max} F\ped{B} c_{p,\mathrm{f}}}{2 f m\ped{s} c\ped{s}}
 \end{equation}
@@
 
-\nomenclature[azn]{$\etasec$}{second-law efficiency}
+\nomenclature[bn]{$\etasec$}{second-law efficiency}
 \section{Results and Discussions}
@@
 
-% \section*{Supplementary Material}
-% \label{sec:suppl-mater}
-
-% The datasets for the results shown in this paper, the source code used to produce the figures and the \LaTeX{} manuscript for this work are available at \cite{bib:fortkamp19-repo-pprof}.
-
-% NA MINHA OPINIAO O SUPPLEMENTARY MATERIAL EH DESNECESSARIO
-
 \section*{Conflict of Interest Statement}

### 2020-05-20 src/figures.py
Remove negative y-axis in some figures.
All figures had their timestamps updated.

@@ -679,10 +679,6 @@ def plot_Qc_H_Inst(table):
                     
                 
             for ax in [axis_Qc, axis_COP]:
-                   
-                ax.plot(x_vector,np.zeros_like(x_vector),
-                        color='grey',
-                         linestyle='-')
                     
                 ax.legend(loc='upper left',
                          bbox_to_anchor=(0,1))    
@@ -691,6 +687,7 @@ def plot_Qc_H_Inst(table):
                 refine_yticks(ax,5)
                 ax.set_xlim(min(x_vector),max(x_vector))
                 ax.set_xticks(x_vector)
+                ax.set_ylim((0,None))
               
             fig_list.append((fig_Qc,fig_COP))
                 
